### 2019-07-02 paper/paper.tex
created paper directory for JuliaCon 2019

% JuliaCon proceedings template
\documentclass[]{article}
%\documentclass{juliacon}
\setcounter{page}{1}

%\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage[left=1.00in, right=1.00in, top=1.00in, bottom=1.00in]{geometry}

\input{mathsym}

% Theorems and Propositions
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem{example}{Example}
\newtheorem*{recall}{Recall}
\newtheorem*{note}{Note}
\newtheorem*{observe}{Observe}
\newtheorem*{question}{\underline{Question}}
\newtheorem*{fact}{Fact}
\newtheorem{corollary}{Corollary}
\newtheorem*{lemma}{Lemma}
\newtheorem{xca}{Exercise}

\usepackage{unicode-math}
\setmonofont[Scale=MatchLowercase]{DejaVu Sans Mono}
\usepackage{scalerel}
\DeclareMathOperator*{\bigboxtimes}{\scalerel*{\boxtimes}{\bigodot}}
\DeclareMathOperator*{\bigominus}{\scalerel*{\ominus}{\bigodot}}
\DeclareMathOperator*{\obackslash}{\text{\reflectbox{$\oslash$}}}

\author{Michael Reed (Crucial Flow Research)}
\title{Differential geometric algebra using Leibniz, Grassmann}

\begin{document}

%\input{header}

\maketitle

\begin{abstract}
	The \textit{Grassmann.jl}
	package provides tools for computations based on multi-linear algebra and spin groups using the extended geometric algebra known as Grassmann-Clifford-Hestenes-Leibniz algebra.
	The primary operations are
	outer, regressive, inner, geometric, and cross products along with the Hodge star, adjoint, and multivector reversal operations. 
	The kernelized operations are built on composite sparse tensor products and Hodge duality, with high dimensional support for up to 62 indices and staged caching / precompilation. Code generation enables making concise and extensible definitions.
	The \textit{DirectSum.jl}
	multivector parametric type polymorphism is based on various tangent vector spaces and conformal projective geometry.
	Additionally, interoperability between different sub-algebras is enabled by \textit{AbstractTensors.jl},
	on which the type system is built.
	%\headingtable
\end{abstract}

In this paper, the mathematical foundations and some of the nuances in the definitions specific to the \textit{Grassmann.jl} implementation are concisely described.
The \textit{Grassmann.jl} package and its accompanying support packages provide an extensible platform for computing with geometric algebra at high dimensions. 
The design is based on the \verb`TensorAlgebra` abstract type system interoperability from \textit{AbstractTensors.jl} with a \verb`VectorBundle` type parameter from \textit{DirectSum.jl}. Abstract vector space type operations happen at compile-time, resulting in a differential conformal geometric algebra of hyper-dual multivector forms.

\begin{itemize}
	\item \textbf{DirectSum.jl}: Abstract tangent bundle vector space types (unions, intersections, sums, etc.)
	\item \textbf{AbstractTensors.jl}: Tensor algebra abstract type interoperability with vector bundle parameter	
	\item \textbf{Grassmann.jl}: $\langle$Grassmann-Clifford-Hestenes-Leibniz$\rangle$ differential conformal geometric algebra
	\item \textbf{Leibniz.jl}: Operator algebras for mixed-symmetry multivariate differentiable tensor fields
	\item \textbf{Reduce.jl}: Symbolic parser generator for Julia expressions using REDUCE algebra term rewriter
\end{itemize}

The nature of the geometric algebra code generation enables one to easily extend the abstract product operations to any specific number field type (including Leibniz differentials with \textit{Leibniz.jl} or symbolic coefficients with \textit{Reduce.jl}), by taking advantage of Julia's type system. With the type system, it is possible to construct mixed tensor products with their coefficients, e.g. bivector elements of Lie groups \cite{hestenes}\cite{shahshahani}.

\section{Direct sum parametric type polymorphism}

The \textit{DirectSum.jl} package is a work in progress providing the necessary tools to work with arbitrary dual \verb`VectorBundle` elements with optional origin. Due to the parametric type system for the generating \verb`VectorBundle`, the Julia compiler can fully preallocate and often cache values efficiently ahead of run-time.
Although intended for use with the \textit{Grassmann.jl} package, \verb`DirectSum` can be used independently.

\begin{definition}[Vector bundle of submanifold]
	Let $T^\mu V\in\text{Vect}_{\mb K}$ be a \verb`VectorBundle<:Manifold` of rank $n$,
	\begin{align*}
		T^\mu V &= (n,\mb P,g,\mu), & n,\mu &\in\mb N, & \mb P &\subseteq\gen{v_\infty,v_\emptyset}, & g &:V\times V\ra\mb K
	\end{align*}
	The type \verb+VectorBundle{n,+$\mb P$\verb+,g,+$\mu$\verb+}+ uses \textit{byte-encoded} data available at pre-compilation, where
	$\mb P$ specifies the null-basis from the projective split,
	$g$ is a bilinear form that specifies the metric of the space,
	and $\mu$ is an integer specifying the order of the tangent bundle (i.e. multiplicity limit of Leibniz-Taylor monomials).

	The dual space functor $(\cdot)':\text{Vect}_{\mb K}^\text{op}\ra\text{Vect}_{\mb K}$ 
	is an involution which toggles a dual vector space with inverted signature with property $V' = \text{Hom}(V,\mb K)$ and having the \verb`Basis` generators
	$$\gen{v_1,\dots,v_n,\partial_1,\dots,\partial_n}=T^\mu V\leftrightarrow T^\mu V' = \gen{w_1,\dots,w_n,\epsilon_1,\dots,\epsilon_n}.$$

	The metric signature of the \verb+Basis{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the \verb+Basis{V,1}+ element of the corresponding index squares to \verb`+1` or \verb`-1`.
	For example, \verb`V"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
	It is possible to specify an arbitrary \verb`DiagonalForm` for the basis elements with \verb`V"0,0,0"` or \verb`V"-1,1,1,1"`, although the $\pm$ format has better performance.
	Further development of the \textit{DirectSum.jl} will result in more metric types.

	The direct sum operator \verb`⊕` can be used to join spaces (alternatively \verb`+`).
	The direct sum of a \verb`VectorBundle` and its dual \verb`V⊕V'` represents the full mother space \verb`V*`.
	Additionally to the direct-sum operation, several other operations are supported, such as $\cup,\cap,\subseteq,\supseteq$ for set operations.
	Due to the design of the \verb`VectorBundle` type system, these operations make code optimization easier at compile-time by evaluating the bit parameters.
	$$ \bigcup T^{\mu_i}V_i = \plr{|\mb P|+\max\set{n_i-|\mb P_i|}_i,\, \bigcup \mb P_i,\, \cup g_i,\, \max\set{\mu_i}_i} $$
	$$ \bigoplus T^{\mu_i}V_i = \plr{\mlr{\mb P}+\sum (n_i-|\mb P_i|),\, \bigcup \mb P_i,\, \oplus_i g_i,\,\max\set{\mu_i}_i} $$
\end{definition}
\begin{note}
	Although some of the type operations like $\bigcup$ and $\bigoplus$ are similar and sometimes result in equal values, the union and sum are entirely different operations in general. The \verb`tangent` map is used for specifying $\mu$.
\end{note}

For any \verb+SubManifold{m,V,s} where+ $\set{n\geq m\in\mb N,V\in\text{Vect}_{\mb K},s\in V}$ we can define the orthogonal space $Z$:
$$T^eV \subset T^\mu W \iff \exists Z\in\text{Vect}_{\mb K}(T^e(V\oplus Z) = T^{e\leq \mu}W,\,V\perp Z),$$
such that computing unions of sub-manifolds is done by inspecting the parameter $s\in V\subseteq W$ and $s\notin Z$.

\section{Tensor basis equivalence classes of Leibniz and Grassmann}

The \verb`AbstractTensors` package is intended for universal interoperability of the abstract \verb`TensorAlgebra` type system.
All \verb`TensorAlgebra{V}` subtypes contain \verb`V` in their type parameters, used to store a \verb`VectorBundle` value obtained from the \textit{DirectSum.jl} package.
By itself, this package does not impose any structure or specifications on the \verb`TensorAlgebra{V}` subtypes and elements, aside from requiring $V$ to be a \verb`VectorBundle`.
This means that different packages can create tensor types with a common underlying \verb`VectorBundle` structure.

\begin{definition}
	Let $V\in\text{Vect}_{\mb k}$ be a \verb`VectorBundle` with dual space $V'$ and the basis elements $w_k:V\ra\mb K$, then for all $x\in V,c\in\mb K$ the properties $(w_i+w_j)(x) = w_i(x)+w_j(x)$ and $(cw_k)(x) = cw_k(x)$ hold.
	An element of a mixed-symmetry \verb`TensorAlgebra{V}` is a multilinear mapping formally constructed by taking the tensor products of linear and multilinear maps,
	$(\bigotimes_k \omega_k)(v_1,\dots,v_{\sum_k p_k}) = \prod_k \omega_k(v_1,\dots,v_{p_k})$.
\end{definition}
\begin{definition}[Mixed-symmetry basis]
	Combining linear basis generating elements with each other using the multi-linear tensor product yields a graded (decomposable) tensor \verb`Basis` $\langle w_{p_1}\otimes\dots\otimes w_{p_k}\rangle_k$, where the \verb`grade` $k$ is determined by the number of basis elements in the tensor product decomposition.
	The algebra is partitioned into symmetric and anti-symmetric tensor equivalence classes.
	For any pair of tensors, either
	\begin{align*}
		&\us{\text{anti-symmetric}}{\omega\otimes\eta = -\eta\otimes\omega}, & &\us{\text{symmetric}}{\omega\otimes\eta = \eta\otimes\omega}.
	\end{align*}
	Typically the $k$ in $\plr{\partial_{p_1}\otimes\cdots\otimes\partial_{p_k}}^{(k)}$ is referred to as the \verb`order` of the element for fully symmetric tensors, which is tracked separately from the \verb`grade` such that $\partial_k\gen{w_j}_r = \gen{\partial_kw_j}_r$ and $(\partial_k)^{(r)}\omega_j = (\partial_kw_j)^{(r)}$.
	Hence, there is a partitioning into \verb`even` grade components $\omega_+$ and \verb`odd` grade components $\omega_-$ with $\omega_++\omega_-=\omega$.
\end{definition}
\begin{remark}
	Observe that the anti-symmetric property implies that $\omega\otimes\omega=0$, while the symmetric property neither implies nor denies such a property.
	In 1862, Grassmann remarked \cite{grassmann-2} that the symmetric algebra of functions is by far more complicated than his anti-symmetric exterior algebra.
	The first part of the book focused on anti-symmetric exterior algebra, while the more complex symmetric function algebra of Leibniz was subject of the second part of the book.
	Elements $\omega_k$ in the space $\Lambda V$ of anti-symmetric algebra are often studied as unit quantum state vectors in a unitary probability space, where $\sum_k\omega_k\neq\bigotimes_k\omega_k$ is entanglement.
\end{remark}
\begin{definition}
	The Grassmann anti-symmetric exterior basis is denoted by $v_{i_1\dots i_g}\in\Lambda_gV$ with its dual basis $w^{i_1\cdots i_g}\in\Lambda^gV$, while the Leibniz symmetric basis will be $\partial_{i_1}^{\mu_1}\dots\partial_{i_g}^{\mu_g}\in L_gV$ with $\epsilon_{i_1}^{\mu_1}\dots\epsilon_{i_g}^{\mu_g}\in L^gV$ dual elements.
\end{definition}
Higher-order composite tensor elements will be denoted by an oriented-multi-set $X\in\text{OMSet}$ such that $w_X = \bigotimes_k w_{i_k}^{\otimes\mu_k}$ with $X = \plr{(i_1,\mu_1),\dots,(i_g,\mu_g)}$ and $|X|=\sum_k\mu_k$ is \verb`grade`+\verb`order`.
%There are two orientations and higher multiplicities result in zero for anti-symmetric tensors denoted by indices $\Lambda X\subseteq\Lambda V$, so the only interesting multiplicity is $\mu_k\equiv 1$.
Indices $\Lambda X\subseteq\Lambda V$ that are anti-symmetric have two orientations and higher multiplicities of those result in zero values, so the only interesting multiplicity is $\mu_k\equiv 1$.
Symmetric tensors have an ambiguous multiplicity of nilpotence; decide that $\epsilon_k^{\mu+1}=0$, so $\mu_k\leq\mu$ can be non-trivial, negative, or possibly unbounded.
Grassmann's exterior algebra is fundamentally simpler in structure than the symmetric generated algebra, as it doesn't invoke the properties of multi-sets.
The exterior Grassmann index algebra is related to the algebra of oriented sets and the Leibniz symmetric algebra is that of unoriented multi-sets. 
Combined, the mixed-symmetry algebra yield a multi-linear propositional lattice.
The formal sum of equal \verb`grade` elements is an oriented \verb`Chain` and with mixed \verb`grade` it is a \verb`MultiVector`.
Thus, various standard operations on the oriented multi-sets are possible including $\cup,\cap,\oplus$ and most importantly the $X\ominus Y=(X\cup Y)\bs(X\cap Y)$ symmetric difference operation $\veebar$.

In order to work with a \verb`TensorAlgebra{V}`, it is necessary for some computations to be cached. This is usually done automatically when accessed.
The staging of the precompilation and caching is designed so that a user can smoothly transition between very high dimensional and low dimensional algebras in a single session, with varying levels of extra caching and optimizations.
The parametric type formalism in \verb`Grassmann` is highly expressive to enable the pre-allocation of geometric algebra computations for specific sparse-subalgebras, including the representation of rotational groups.
It is possible to reach \verb`Basis` elements having up to $n=62$ indices, % with \verb`TensorAlgebra` having higher maximum dimensions than supported by Julia natively.
requiring full alpha-numeric labeling with lower-case and capital letters. 
However, Julia is only able to allocate full \verb`MultiVector` for $n\leq22$, with only sparse operations available at higher dimension form there.
While \verb`Grassmann.Algebra{V}` is a container for the \verb`TensorAlgebra` generators of $V$, the \verb`Grassmann.Algebra` is only cached for $n\leq8$.
For a \verb`VectorBundle{n}` of dimension $8<n\leq22$, the \verb`Grassmann.SparseAlgebra` type is used.
To reach higher dimensions, for $n>22$ the \verb`Grassmann.ExtendedAlgebra` type is used.

\section{Geometric algebraic product structure}

While oriented sets of the Grassmann exterior algebra are simpler, the parity \cite{artin} of $(-1)^\Pi$ is factored into transposition compositions when interchanging the ordering of the tensor product argument permutation.
Alternatively, symmetric algebra does not need to track the parity but does have multiplicity in its indices.
Symmetric differential function algebra of Leibniz trivializes the orientation property of index multi-sets, while Grassmann's exterior algebra is partitioned into two oriented equivalence classes by anti-symmetry.
The full tensor algebra can be sub-partitioned into equivalence classes in multiple ways based on the composite symmetry, grade, and metric signature properties.
%It can be said that the Leibniz symmetry class has a neutral orientation, while Grassmann's anti-symmetric class is partitinoned into positive and negative orientation.
Both of the symmetry classes can be characterized by the same geometric product, which is written as multiplication but explicitly denoted by $\ominus$ for clarity here.
%It is possible to express this universal product in terms of ordered-multi-set operations.

\begin{definition}
	The \textit{geometric algebraic product} is the $\Pi$ oriented symmetric difference operator $\ominus$ (weighted by the bilinear form $g$) and multi-set sum $\oplus$ applied to multilinear tensor products $\otimes$ in a single operation:
	$$ \omega_X\ominus \eta_Y = \ub{\text{$\Lambda^1$-anti-symmetric, $\Lambda^g$-mixed-symmetry}}{(-1)^{\Pi(\Lambda X,\Lambda Y)}\det\mat{g_{\Lambda(X\cap Y)}} (\bigotimes_{k\in \Lambda(X\ominus Y)} w^{i_k})}\otimes \ub{\text{$L^g$-symmetric}}{(\bigotimes_{k\in L(X\oplus Y)} \epsilon_{i_k}^{\otimes\mu_k})}$$
\end{definition}

\begin{note}
	The product symbol $\ominus$ will be used to expliclity denote usage of the geometric algebraic product, altough the standard number product \verb`*` notation could also be used. This choice is to help emphasize that the geometric algebraic product is characterized by symmetric differencing of anti-symmetric indices.
\end{note}

\begin{definition}
	The symmetry properties of the tensor algebra can be characterized in terms of the geometric product by two averaging operations, which are the symmetrization $\odot$ and anti-symmetrization $\boxtimes$ operators:
	\begin{align*}
		\bigodot_{k=1}^j \omega_k &= \frac1{j!}\sum_{\sigma\in S_P}\bigominus_k\omega_{\sigma(k)}, &
		\bigboxtimes_{k=1}^j \omega_k &= \frac1{j!}\sum_{\sigma\in S_P}(-1)^{\Pi(\sigma)}\bigominus_k\omega_{\sigma(k)}
	\end{align*}
\end{definition}
These products satisfy various \verb`MultiVector` properties, including the associative and distributive laws.

\begin{definition}[Exterior product]
	Let $w_k:V^{p_k}\times V'^{q_k}\ra\mb K$ such that $k\in\Lambda^{p_k}V$, then for all $\sigma\in S_{\sum p_k}$
	$$ (-1)^{\Pi(\sigma)}(\bigotimes_k \omega_k)(v_{\sigma(1)},\dots,v_{\sigma(\sum p_k)}) \sim \bigwedge_k \omega_k(v_{1},\dots,v_{p_k}) \iff \bigominus_k\omega_k = \bigboxtimes_k\omega_k $$
	there is an equivalence relation $\sim$ which holds. It has become typical to use the $\wedge$ product symbol to denote products of such elements as $\bigwedge\Lambda V \equiv \bigotimes\Lambda V/\sim$ modulo anti-symmetrization.
\end{definition}

\begin{definition}[Symmetric tensor of Leibniz differentials]
	Let $\partial_k = \frac\partial{\partial x_k}\in L_gV\,$ Leibnizian symmetric tensors, then there is an equivalence relation $\asymp$ which holds for each $\sigma\in S_p$ along with each derivation property,
	\begin{align*}
		(\bigotimes_k \partial_{\sigma(k)})\omega &\asymp (\partial_p \circ \dots\circ  \partial_1)\omega \iff \bigominus_k\partial_k = \bigodot_k\partial_k, & \partial_k(\omega\eta) &= \partial_k(\omega)\eta + \omega\partial_k(\eta).
	\end{align*}
\end{definition}

%\subsubsection{Interoperability for TensorAlgebra}

%\textit{AbstractTensors.jl} provides the abstract interoperability between tensor algebras having differing \verb`VectorBundle` parameters. The \verb`VectorBundle` unions and intersections are handled separately in a different package and the actual tensor implementations are handled separately also. This enables anyone who wishes to be interoperable with \verb`TensorAlgebra` to build their own subtypes in their own separate package with interoperability automatically possible between it all, provided the guidelines are followed.

%The key to making the whole interoperability work is that each \verb`TensorAlgebra` subtype shares a \verb`VectorBundle` parameter (with all \verb`isbitstype` parameters), which contains all the info needed at compile time to make decisions about conversions. So other packages need only use the vector space information to decide on how to convert based on the implementation of a type. If external methods are needed, they can be loaded by \verb`Requires` when making a separate package with \verb`TensorAlgebra` interoperability.

Since \verb`VectorBundle` choices are fundamental to \verb`TensorAlgebra` operations, the universal interoperability between \verb`TensorAlgebra{V}` elements with different associated \verb`VectorBundle` choices is naturally realized by applying the \verb`union` morphism to type operations.
For example, $\bigwedge :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{\sum_kp_k}\bigcup_k V_k$. 
% where $\bigwedge \Lambda V \equiv \bigotimes \Lambda V/\sim$ is made interoperable by $\cup$.

\begin{definition}[Reverse, involute, conjugate]
	The \verb`reverse` of $\gen{\omega}_r$ is defined as $\gen{\tilde\omega}_r = (-1)^{(r-1)r/2}\gen{\omega}_r$, while the \verb`involute` is $(-1)^r\gen{\omega}_r$ and Clifford \verb`conj`  $\gen{\omega}_r^\ddagger$ is the composition of \verb`involute` and \verb`reverse`.
\end{definition}

\begin{definition}[Reversed product]
	The \textit{reversed geometric product} $\ast$ yields a Hilbert space structure:
	\begin{align*}
		\omega\ast\eta &= \tilde\omega\ominus\eta, & \omega\ast'\eta &= \omega\ominus\tilde\eta, & |\omega|^2 &= \omega\ast\omega, & |\omega| &= \sqrt{\omega\ast\omega}, & ||\omega|| = \text{Euclidean }|\omega|
	\end{align*}
\end{definition}
\begin{definition}[Sandwich product]
	The sandwich product is defined as $\eta\oslash\omega = (\eta\ast\omega)\ominus\eta$. Alternatively, the reversed definition is $\eta\obackslash\omega = \eta\ominus(\omega\ast'\eta)$ or in Julia $\eta\,$\verb`>>>`$\,\omega$, which is often found in literature.
\end{definition}
\begin{note}
	Observe that $\ast$ and $\ast'$ could both be used in \verb`abs`, \verb`abs2`, and \verb`norm`; however they are different products.
	The \textit{scalar product} $\circledast$ is the scalar part of the reversed product $\eta\circledast\omega = \gen{\eta\ast\omega}$.
	In general $\sqrt\omega = e^{(\log\omega)/2}$ is valid for \verb`inv`ertible multivectors $\omega\inv = \omega\ast|\omega|^{-2} = \tilde\omega/|\omega|^2$, where $\eta/\omega = \eta\ominus\omega\inv = \eta\ominus(\tilde\omega/(\omega\oslash1))$.
\end{note}
\begin{remark}
	It is overall more simple to use the $\ast$ and $\oslash$ operations instead of the $\ast'$ and $\obackslash$ variations.
\end{remark}
The \verb`real` part $\Re\omega = (\omega+\tilde\omega)/2$ is defined by the property $|\Re\omega|^2 = (\Re\omega)^{\ominus2}$ and the \verb`imag` part $\Im\omega = (\omega-\tilde\omega)/2$ by $|\Im\omega|^2 = -(\Im\omega)^{\ominus2}$, such that for any multivector $\omega = \Re\omega+\Im\omega$ has real and imaginary partitioned by 
$$\gen{\tilde\omega}_r/\mlr{\gen{\omega}_r} = \sqrt{\gen{\tilde\omega}_r^2/\big|\gen{\omega}_r\big|^2} = \sqrt{\gen{\omega}_r\ast\gen{\omega}_r\inv} = \sqrt{\gen{\tilde\omega}_r/\gen{\omega}_r}=\sqrt{(-1)^{(r-1)r/2}} \in\set{1,\sqrt{-1}},$$
which is a unique partitioning completely independent of the metric space and manifold of the algebra \cite{chappell-iqbal-gunn-abbott}.
$$ \omega\ast\omega = |\omega|^2 = |\Re\omega+\Im\omega|^2 = |\Re\omega|^2 + |\Im\omega|^2 + \Re\omega\ast\Im\omega + \Im\omega\ast\Re\omega = |\Re\omega|^2+|\Im\omega|^2 + 2\Re(\Re\omega\ast\Im\omega) $$
The \verb`radial` and \verb`angular` components in a multivector exponential are partitioned by the parity of their metric.

The Grassmann \verb`Basis` elements $v_k\in\Lambda_1V$ and $w^k\in\Lambda^1V$ are linearly independent vector and covector elements of $V$, while the Leibniz \verb`Operator` elements $\partial_k\in L_1V$ are partial tangent derivations and $\epsilon_k(x)\in L^1V$ are dependent functions of the \verb`tangent` manifold. 
Higher \verb`grade` elements of $\Lambda V$ correspond to \verb`SubManifold` subspaces, while higher \verb`order` function elements of $LV$ become homogenous polynomials and Taylor series.

%\subsection{Grassmann's duality via Hodge complement}

A universal unit volume element can be specified in terms of \verb`LinearAlgebra.UniformScaling`, which is independent of $V$ and has its interpretation only instantiated by the context of the \verb`TensorAlgebra{V}` element being operated on.
The universal interoperability of \verb`LinearAlgebra.UniformScaling` as a pseudoscalar element which takes on the \verb`VectorBundle` form of any other \verb`TensorAlgebra` element is handled globally. 
This enables the usage of \verb`I` from \verb`LinearAlgebra` as a universal pseudoscalar element defined at every point $x$ of the manifold, which is mathematically denoted by $I=I(x)$ and specified by the $g(x)$ bilinear tensor field of $TM$.

\begin{definition}[Grassmann-Poincare-Hodge complement]
	Let $\star\gen{\omega}_p = \gen{\omega}_p\ast I$, %= (-1)^{\frac{p(p+1)}2+\us k\sum i_k}\det\mat{ g_{i_ki_k}}\bigwedge_{m\in J(\omega)} w_m
	 then $\star : \Lambda^pV\ra\Lambda^{n-p}V$.
\end{definition}
\begin{remark}
	While $\star\omega$ is \verb`complementright` of $\omega$, the \verb`complementleft` would be $I\ast'\omega$. The $\star$ symbol was added to the Julia language as unary operator for ease of use with \verb`Grassmann` on Julia's v1.2 release.
\end{remark}

\section{Leibniz operators and Grassmann's Hodge-DeRahm theory}

John Browne has discussed the Grassmann duality principle in book \cite{browne}, stating that every theorem (involving exterior and regressive products) can be translated into its dual theorem by replacing the $\wedge$ and $\vee$ operations and applying \textit{Poincare duality} (homology).
First applying this Grassmann duality principle to the $\wedge$ product alone, let $\set{\omega_k}_k\in\Lambda^{p_k}V, P=\sum_kp_k$, then the co-product
$\bigvee :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{P-(g-1)\#V}\bigcup_k V_k$ is obtained.
in Grassmann's original notation $\wedge,\vee,\star$ operations were combined.
The join $\wedge$ product is analogous to union $\cup$, the meet $\vee$ product is analogous to intersection $\cap$, and the orthogonal complement $\star\mapsto^\perp$ is negation.
Together, $(\wedge,\vee,\star)$ yield an orthocomplementary propositional lattice (quantum logic) by
\begin{align*}
	(\star\bigvee_k &\omega_k)(v_1,\dots,v_P) = (\bigwedge_k\star\omega_k)(v_1,\dots,v_P) \quad \textit{DeMorgan's Law}.
\end{align*}
\begin{definition}
	The left $\lrcorner$ and right $\llcorner$ contraction symmetrically define
	$ \gen{\omega}_r\cdot\gen{\eta}_s = \begin{cases} \omega\llcorner\eta=\omega\vee\star\eta & r\geq s \\ \omega\lrcorner\eta=\eta\vee\star\omega & r\leq s \end{cases} $.
	Note that for $\omega,\eta$ of equal grade, the operations $\omega\circledast\eta = \omega\odot\eta = \omega\cdot\eta = \omega\llcorner\eta = \omega\lrcorner\eta$ are symmetric.
\end{definition}

\begin{definition}
	Let $\nabla = \sum_k\partial_kv_k$ and $\epsilon = \sum_k\epsilon_k(x)w_k \in \Omega^1V$ be unit sums of the mixed-symmetry basis.
	Elements of $\Omega^pV$ are known as \textit{differential} $p$-\textit{forms} and both $\nabla$ and $\epsilon$ are \textit{tensor fields} dependent on $x\in W$.
	Another notation for a differential form is $dx_k = \epsilon_k(x)w_k$, such that $\epsilon_k = dx_k/w_k$ and $\partial_k\omega(x) = \omega'(x)$.
\end{definition}
\begin{note}
	The space $W$ does not have to equal $V\in\text{Vect}_{\mb K}$ above, as $\Omega^pV$ could have coefficients from $\mb K = LW$.
\end{note}
\begin{definition}
	Define \cite{bishop-goldberg} the differential $d:\Omega^p V\ra\Omega^{p+1}V$ and co-differential $\delta:\Omega^pV\ra\Omega^{p-1}V$ such that
	\begin{align*}
		\star d\omega &= \star(\nabla\wedge\omega) = \nabla\times\omega, & \omega\cdot\nabla &= \omega\vee\star\nabla = \partial\omega =-\delta\omega, 
	\end{align*}
	These two maps have the special properties $d\circ d=0$ and $\partial\circ\partial = 0$ for any form $\omega$ and vector field $\nabla$. 
	In topology there is \textit{boundary} operator $\partial$ that can be defined by $\partial\epsilon = \epsilon\cdot\nabla = \sum_k\partial_k\epsilon_k$ and is commonly discussed in terms the limit $\epsilon(x)\cdot\nabla\omega(x) = \lim_{h\ra0} \frac{\omega(x+h\epsilon)-\omega(x)}{h}$, which is the directional derivative \cite{sobczyk}.
\end{definition}
\begin{example}
	[Vorticity of vector-field]
	$\star d(dx_1+dx_2+dx_3) = (∂_2 -∂_3)dx_1 + (∂_3 -∂_1)dx_2 + (∂_1 -∂_2)dx_3$.
\end{example}
\begin{example}
	[Boundary of 3-simplex]
	Faces as oriented \verb`Chain`: $\partial(w_{1234}) = -\partial_4w_{123}+\partial_3w_{124}-\partial_2w_{134}+\partial_1w_{234}$.
\end{example}
\begin{theorem}[Leibniz-Taylor series]
	Let $\partial_X=\bigominus_k\partial_k^{\mu_k}$ be defined so that $|X|=\sum_k\mu_k$, then $e^{\partial\epsilon}\omega(x)$ is
	\begin{align*}
		\sum_{j=0}^\mu \frac{(\partial\epsilon)^{\ominus j}}{j!}\omega(x)
		= \sum_{j=0}^\mu\sum_{|X|=j} \bigominus_k \frac{(\partial_{k}\epsilon_k(x))^{\mu_{k}}}{\mu_k!}\omega(x)
		+ (\mu+1)\sum_{|X|=\mu+1}\int_0^1(1-t)^\mu\bigominus_k\frac{(\partial_k\epsilon_k(x))^{\mu_k}}{\mu_k!}\omega(x+t\epsilon)\,dt.
	\end{align*}
\end{theorem}
The multivariate \textit{chain rule} is encoded into the geometric algebraic product when using mixed-symmetry.

\begin{theorem}[Hilbert adjoint Hodge-DeRahm operators]
	Let $ \nabla \in\Omega_1 V $ be a Leibnizian vector field operator, then $d,-\partial$ are Hilbert adjoint Hodge-DeRahm operators with $\gen{\,\ast\,}$
	\begin{align*}
		\int_M d\omega\wedge\star\eta +\int_M \omega\wedge\star\partial\eta &= 0, & \gen{d\omega\ast\eta} &=\gen{\omega\ast-\partial\eta}
	\end{align*}
\end{theorem}
\begin{proof}
	Observe that $\partial\omega = \omega\cdot\nabla = \star(\star\omega\wedge\star^2\nabla) = (-1)^n(-1)^{nk}\star d\star\omega$.
	Then  substitute this into the integral $\int_M \omega\wedge(-1)^{mk+m+1}\star\star d\star\eta = (-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}\int_M\omega\wedge d\star\eta$,
	with $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and also
	$ (-1)^k\int_M\omega\wedge d\star\eta = \int_M d(\omega\wedge\star\eta) - (-1)^{k-1}\omega\wedge d\star\eta = \int_M d\omega\wedge\star\eta$.
	The other identity can be proved by relying on a variant of the \textit{common factor theorem} by Browne \cite{browne}.
\end{proof}
\begin{theorem}[Clifford-Dirac-Laplacian]
	Dirac operator $ \Delta^\frac12\omega = \mp\omega\ominus\nabla = \pm\nabla\wedge\omega \mp \omega\llcorner\nabla  = \pm d\omega\mp\partial\omega$ \cite{garling}.
	\begin{align*}
		\Delta\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \pm(\pm\omega\ominus\nabla)\ominus\nabla), & \mc H^p M = \setc{\Delta\omega = 0}{\omega\in \Omega^pM}
	\end{align*}
	Elements $\omega$ are \textit{harmonic} if $\Delta\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, Hodge decomposition \cite{ivancevic}:
	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\delta\Omega^{p+1}M}$.
	Warning $\nabla\omega\neq\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
\end{theorem}

%\subsection{Projective null-cones of Dirac-Clifford-Hestenes}

\begin{definition}
	[Null-basis of projective split]
	Let $v_\pm^2 = \pm1$ be a basis with $v_\infty = v_++v_-$ and $v_\emptyset = (v_--v_+)/2$
\end{definition}
An embedding space $\mb R^{n+1,1}$ carrying the action from the group $SO(n+1,1)$ then has
$v_\infty^2 =0$, $v_\emptyset^2 =0$,
$v_\infty \cdot v_\emptyset = 1$,  and $v_{\infty\emptyset}^2 = 1$ with
Minkowski plane $v_{\infty\emptyset}$ having the Hestenes-Dirac-Clifford product properties
\begin{align*}
	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, &
	v_\infty\ominus v_\emptyset &= -1 + v_{\infty\emptyset}, & v_\emptyset\ominus v_\infty &=  -1 - v_{\infty\emptyset}
\end{align*}
Declaring an additional \textit{null-basis} is done by specifying it in the string constructor with \verb`∞` at the first index (i.e. \verb`S"∞+++"`). Likewise, an optional \textit{origin} can be declared by \verb`∅` subsequently (i.e. \verb`S"∅+++"` or \verb`S"∞∅+++"`). These two basis elements will be interpreted in the type system such that they propagate under transformations when combining a mixed index sets (provided the \verb`Signature` is compatible).
\begin{example}[\textit{using Leibniz $\bigoplus\,$Grassmann}]
	\textbf{julia>} S"$\infty\emptyset\text{+++"}(\nabla)$\verb`^`$2 \,\,  \mapsto\, \, \Delta = (-2\partial_{\infty\emptyset} + \partial_1^2 + \partial_2^2 + \partial_3^2)\vec v $
\end{example}

\section{Conclusion}

\textit{Grassmann.jl} and its accompanying support packages provide an extensible platform for fully generalized computing with geometric algebra at high dimensions.
%This will enable the usage of many different types of \verb`TensorAlgebra` along with various \verb`VectorBundle` parameters and interoperability for a wide range of scientific and research applications.
All of the types and operations in this paper are implemented using only a few thousand lines of code with Julia's type polymorphism code generation, although the mixed-symmetry interaction of \verb`Leibniz` and \verb`Grassmann` is still a work in progress.
The goal is to algebraically define operator actions on groups of \textit{Leibniz.jl} differential function elements. 
One way is to use \textit{Reduce.jl} for differentiation and \textit{SyntaxTree.jl} to obtain optimal symbolic polynomial forms \cite{optim-poly}.

Thus, these packages provide general rotational algebras and Lie bivector groups with a full trigonometric suite enabled by $ e^{A} = \sum_n \frac{A^n}{n!} $.
Conformal geometric algebra is possible with the Minkowski plane $v_{\infty\emptyset}$, based on the null-basis.
In general, multivalued quantum logic is enabled by the $\wedge,\vee,\star$ Grassmann-Hodge dual lattice.
Mixed-symmetry algebra with \textit{Leibniz.jl} and \textit{Grassmann.jl}, having the geometric algebraic product chain rule, yields automatic differentiation and Hodge-DeRahm co/homology  as unveiled by Grassmann.
\begin{align*}
	0 &\os d{\us\partial\rightleftarrows} \Omega^0(M) \os d{\us\partial\rightleftarrows} \Omega^1(M) \os d{\us\partial\leftrightarrows} \cdots \os d{\us\partial\rightleftarrows} \Omega^n(M) \os d{\us\partial\rightleftarrows} 0, & \mc H^pM &\cong \frac{\ker(d\Omega^pM)}{\im{d\Omega^{p-1}M}}, & \dim\mc H^pM &= \dim\frac{\ker(\delta\Omega^pM)}{\im{\delta\Omega^{p+1}M}}
\end{align*}
In conclusion, the Dirac-Clifford product yields generalized Hodge-Laplacian and $b_p=\dim\mc H^pM$ are the Betti numbers with Euler characteristic $\chi = \sum_p (-1)^pb_p$.
There will be a more detailed follow-up paper.

\textbf{Acknowledgements}: Many thanks for discussions with Steven De Keninck, Utensil Song, Alexander Arsenovic, Hugo Hadfield, Karl Wessel; the helpful Julia community (e.g. Jameson Nash, Stefan Karpinski, Jeff Bezanson, Kristoffer Carlsson, Tamas Papp, Nathan Smith, etc); and thanks for support from my family.

%\cite{bezanson2017julia}

\input{bib.tex}

\end{document}

### 2019-07-26 src/multivectors.jl
added compatibility for QR decomposition

@@ -598,3 +598,36 @@ function (W::Signature)(m::MultiVector{T,V}) where {T,V}
     end
 end
 
+
+# QR compatibility
+
+convert(a::Type{SBlade{V,G,B,A}},b::SBlade{V,G,B,T}) where {V,G,A,B,T} = SBlade{V,G,B,A}(convert(A,value(b)))
+convert(::Type{SBlade{V,G,B,X}},t::Y) where {V,G,B,X,Y} = SBlade{V,G,B,X}(convert(X,t))
+
+Base.copysign(x::SBlade{V,G,B,T},y::SBlade{V,G,B,T}) where {V,G,B,T} = SBlade{V,G,B,T}(copysign(value(x),value(y)))
+
+@inline function LinearAlgebra.reflectorApply!(x::AbstractVector, τ::TensorAlgebra, A::StridedMatrix)
+    @assert !LinearAlgebra.has_offset_axes(x)
+    m, n = size(A)
+    if length(x) != m
+        throw(DimensionMismatch("reflector has length $(length(x)), which must match the dimension of matrix A, $m"))
+    end
+    @inbounds begin
+        for j = 1:n
+            #dot
+            vAj = A[1,j]
+            for i = 2:m
+                vAj += conj(x[i])*A[i,j]
+            end
+
+            vAj = conj(τ)*vAj
+
+            #ger
+            A[1, j] -= vAj
+            for i = 2:m
+                A[i,j] -= x[i]*vAj
+            end
+        end
+    end
+    return A
+end

### 2019-07-26 src/algebra.jl
added round method

@@ -1227,7 +1227,7 @@ for op ∈ (:div,:rem,:mod,:mod1,:fld,:fld1,:cld,:ldexp)
         Base.$op(a::MultiVector{T,V},m::S) where {T,V,S} = MultiVector{promote_type(T,S),V}($op.(value(a),m))
     end
 end
-for op ∈ (:mod2pi,:rem2pi,:rad2deg,:deg2rad)
+for op ∈ (:mod2pi,:rem2pi,:rad2deg,:deg2rad,:round)
     for Blade ∈ MSB
         @eval Base.$op(b::$Blade{V,G,B,T}) where {V,G,B,T} = $Blade{V,G,B}($op(value(b)))
     end

### 2019-09-07 paper/paper.tex
created JuliaCon 2019 and tidelift links
generalized differential Manifold and SubManifold algebra

@@
 % JuliaCon proceedings template
-\documentclass[]{article}
-%\documentclass{juliacon}
+%\documentclass[]{article}
+\documentclass{juliacon}
 \setcounter{page}{1}
@@
 % Theorems and Propositions
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{proposition}{Proposition}
+%\usepackage{amsthm}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{proposition}{Proposition}
 
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
+%\theoremstyle{definition}
+%\newtheorem{definition}{Definition}
 
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem{example}{Example}
-\newtheorem*{recall}{Recall}
-\newtheorem*{note}{Note}
-\newtheorem*{observe}{Observe}
-\newtheorem*{question}{\underline{Question}}
-\newtheorem*{fact}{Fact}
-\newtheorem{corollary}{Corollary}
-\newtheorem*{lemma}{Lemma}
-\newtheorem{xca}{Exercise}
+%\theoremstyle{remark}
+%\newtheorem*{remark}{Remark}
+%\newtheorem{example}{Example}
+%\newtheorem*{recall}{Recall}
+%\newtheorem*{note}{Note}
+%\newtheorem*{observe}{Observe}
+%\newtheorem*{question}{\underline{Question}}
+%\newtheorem*{fact}{Fact}
+%\newtheorem{corollary}{Corollary}
+%\newtheorem*{lemma}{Lemma}
+%\newtheorem{xca}{Exercise}
 
@@
 \title{Differential geometric algebra using Leibniz, Grassmann}
+\date{July 25th, 2019}
 
@@
 \end{definition}
-\begin{note}
+\begin{remark}
 	Although some of the type operations like $\bigcup$ and $\bigoplus$ are similar and sometimes result in equal values, the union and sum are entirely different operations in general.
 The \verb`tangent` map is used for specifying $\mu$.
-\end{note}
+\end{remark}
 
@@
 \textbf{Acknowledgements}: Many thanks for discussions with Steven De Keninck, Utensil Song, Alexander Arsenovic, Hugo Hadfield, Karl Wessel; the helpful Julia community (e.g.
-Jameson Nash, Stefan Karpinski, Jeff Bezanson, Kristoffer Carlsson, Tamas Papp, Nathan Smith, etc); and thanks for support from my family.
+Jameson Nash, Stefan Karpinski, Jeff Bezanson, Kristoffer Carlsson, Petr Krysl, Nathan Smith, etc); and thanks for support from my family.
 

### 2019-09-07 src/Grassmann.jl

@@ -7,7 +7,7 @@ using Combinatorics, StaticArrays, Requires
 using ComputedFieldTypes, AbstractLattices
 using DirectSum, AbstractTensors
 
-export vectorspace, ⊕, ℝ, @V_str, @S_str, @D_str, Signature, DiagonalForm, value
+export vectorspace, ⊕, ℝ, @V_str, @S_str, @D_str, Signature,DiagonalForm,SubManifold, value
 import DirectSum: hasinf, hasorigin, mixedmode, dual, value, vectorspace, V0, ⊕, pre, vsn
 
 include("utilities.jl")
@@ -19,7 +19,7 @@ include("forms.jl")
 
 ## generators
 
-function labels(V::T,vec::String=pre[1],cov::String=pre[2],duo::String=pre[3],dif::String=pre[4]) where T<:VectorBundle
+function labels(V::T,vec::String=pre[1],cov::String=pre[2],duo::String=pre[3],dif::String=pre[4]) where T<:Manifold
     N,io,icr = ndims(V),IOBuffer(),1
     els = Array{Symbol,1}(undef,1<<N)
     els[1] = Symbol(vec)
@@ -34,9 +34,9 @@ function labels(V::T,vec::String=pre[1],cov::String=pre[2],duo::String=pre[3],di
     return els
 end
 
-#@pure labels(V::T) where T<:VectorBundle = labels(V,pre[1],pre[2],pre[3],pre[4])
+#@pure labels(V::T) where T<:Manifold = labels(V,pre[1],pre[2],pre[3],pre[4])
 
-@pure function generate(V::VectorBundle{N}) where N
+@pure function generate(V::Manifold{N}) where N
     exp = Basis{V}[Basis{V,0,g_zero(Bits)}()]
     for i ∈ 1:N
         set = combo(N,i)
@@ -49,7 +49,7 @@ end
 
 export @basis, @basis_str, @dualbasis, @dualbasis_str, @mixedbasis, @mixedbasis_str
 
-function basis(V::VectorBundle,sig=vsn[1],vec=pre[1],cov=pre[2],duo=pre[3],dif=pre[4])
+function basis(V::Manifold,sig=vsn[1],vec=pre[1],cov=pre[2],duo=pre[3],dif=pre[4])
     N = ndims(V)
     if N > algebra_limit
         Λ(V) # fill cache
@@ -97,7 +97,7 @@ macro mixedbasis_str(str)
     Expr(:block,bases,basis(V',vsn[2]),basis(V),bases.args[end])
 end
 
[…]

### 2019-09-07 src/algebra.jl

@@ -8,12 +8,12 @@ import AbstractTensors: ⊗, ⊛, ⊙, ⊠, ⨼, ⨽, ⋆, ∗, rem, div, contra
 import DirectSum: diffcheck, tangent, hasinforigin, hasorigininf
 export tangent
 
-const Field = Number
+const Field = Real
 const ExprField = Union{Expr,Symbol}
 
 @pure g_one(b::Type{Basis{V}}) where V = getbasis(V,bits(b))
-@pure g_zero(V::VectorBundle) = 0*one(V)
-@pure g_one(V::VectorBundle) = Basis{V}()
+@pure g_zero(V::Manifold) = 0*one(V)
+@pure g_one(V::Manifold) = Basis{V}()
 @pure g_one(::Type{T}) where T = one(T)
 @pure g_zero(::Type{T}) where T = zero(T)
 
@@ -46,19 +46,23 @@ function declare_mutating_operations(M,F,set_val,SUB,MUL)
         end
         for s ∈ (sm,sb)
             @eval begin
-                @inline function $(Symbol(:join,s))(V::W,m::$M,A::Bits,B::Bits,v::S) where W<:VectorBundle{N,D} where {N,D,T<:$F,S<:$F,M}
-                    if v ≠ 0 && !diffcheck(V,A,B)
+                @inline function $(Symbol(:join,s))(V::W,m::$M,a::Bits,b::Bits,v::S) where W<:Manifold{N} where {N,T<:$F,S<:$F,M}
+                    if v ≠ 0 && !diffcheck(V,a,b)
+                        A,B,Q,Z = symmetricmask(V,a,b)
                         val = (typeof(V)<:Signature || count_ones(A&B)==0) ? (parity(A,B,V) ? $SUB(v) : v) : $MUL(parityinner(A,B,V),v)
-                        $s(m,val,A⊻B,Dimension{N}())
+                        diffvars(V)≠0 && !iszero(Z) && (val *= Basis{V}(Z))
+                        $s(m,val,(A⊻B)|Q,Dimension{N}())
                     end
                     return m
                 end
-                @inline function $(Symbol(:geom,s))(V::W,m::$M,A::Bits,B::Bits,v::S) where W<:VectorBundle{N,D} where {N,D,T<:$F,S<:$F,M}
-                    if v ≠ 0 && !diffcheck(V,A,B)
[…]

### 2019-09-07 src/forms.jl

@@ -27,14 +27,14 @@ end
 
 const dualindex_cache = Vector{Vector{Int}}[]
 const dualindexC_cache = Vector{Vector{Int}}[]
-@pure function dualindex(V::VectorBundle{N}) where N
+@pure function dualindex(V::Manifold{N}) where N
     C = mixedmode(V)<0
     for n ∈ 2length(C ? dualindexC_cache : dualindex_cache)+2:2:N
         push!(C ? dualindexC_cache : dualindex_cache,Vector{Int}[])
     end
     M = Int(N/2)
     @inbounds if isempty((C ? dualindexC_cache : dualindex_cache)[M])
-        #df = dualform(C ? VectorBundle(M)⊕VectorBundle(M)' : VectorBundle(n))
+        #df = dualform(C ? Manifold(M)⊕Manifold(M)' : Manifold(n))
         di = Array{Vector{Int},1}(undef,M)
         x = M .+cumsum(collect(2(M-1):-1:M-1))
         @inbounds di[1] = [M;x;collect(x[end]+1:x[end]+M-1)]

### 2019-09-07 src/multivectors.jl

@@ -8,11 +8,15 @@ abstract type GradedAlgebra{V,G} <: TensorAlgebra{V} end
 abstract type TensorTerm{V,G} <: GradedAlgebra{V,G} end
 abstract type TensorMixed{T,V} <: TensorAlgebra{V} end
 
+# number fields
+
+Fields = (Real,Complex)
+
 # symbolic print types
 
-parany = (Expr,Any)
-parsym = (Expr,Symbol)
-parval = (Expr,)
+parany = (Expr,Complex,Any)
+parsym = (Expr,Complex,Symbol)
+parval = (Expr,Complex)
 
 ## pseudoscalar
 
@@ -28,8 +32,8 @@ end
 
 @pure bits(b::Basis{V,G,B} where {V,G}) where B = B
 Base.one(b::Type{Basis{V}}) where V = getbasis(V,bits(b))
-Base.zero(V::VectorBundle) = 0*one(V)
-Base.one(V::VectorBundle) = Basis{V}()
+Base.zero(V::Manifold) = 0*one(V)
+Base.one(V::Manifold) = Basis{V}()
 
 function getindex(b::Basis,i::Int)
     d = one(Bits) << (i-1)
@@ -69,8 +73,12 @@ end
 ==(a::Basis{V,G} where V,b::Basis{W,L} where W) where {G,L} = false
 ==(a::Basis{V,G},b::Basis{W,G}) where {V,W,G} = interop(==,a,b)
 
-==(a::Number,b::TensorTerm{V,G} where V) where G = G==0 ? a==value(b) : 0==a==value(b)
-==(a::TensorTerm{V,G} where V,b::Number) where G = G==0 ? value(a)==b : 0==value(a)==b
+for T ∈ Fields
+    @eval begin
+        ==(a::T,b::TensorTerm{V,G} where V) where {T<:$T,G} = G==0 ? a==value(b) : 0==a==value(b)
+        ==(a::TensorTerm{V,G} where V,b::T) where {T<:$T,G} = G==0 ? value(a)==b : 0==value(a)==b
+    end
+end
 
 @inline show(io::IO, e::Basis) = DirectSum.printindices(io,vectorspace(e),bits(e))
 
@@ -97,7 +105,10 @@ for Blade ∈ MSB
         $Blade{V,G}(v,b::MBlade{V,G}) where {V,G} = $Blade{V,G,basis(b)}(v*b.v)
[…]

### 2019-09-07 src/parity.jl

@@ -22,11 +22,11 @@ for side ∈ (:left,:right)
     p = Symbol(:parity,side)
     @eval begin
         @pure $p(V::Bits,B::Bits,N::Int) = $p(count_ones(V&B),sum(indices(B,N)),count_ones(B),N)
-        @pure $p(V::Signature,B,G=count_ones(B)) = $p(count_ones(value(V)&B),sum(indices(B,ndims(V))),G,ndims(V))
+        @pure $p(V::Signature,B,G=count_ones(B)) = $p(count_ones(value(V)&B),sum(indices(B,ndims(V))),G,ndims(V)-diffvars(V))
         @pure function $p(V::DiagonalForm,B,G=count_ones(B))
             ind = indices(B,ndims(V))
             g = prod(V[ind])
-            $p(0,sum(ind),G,ndims(V)) ? -(g) : g
+            $p(0,sum(ind),G,ndims(V)-diffvars(V)) ? -(g) : g
         end
         @pure $p(b::Basis{V,G,B}) where {V,G,B} = $p(V,B,G)
     end
@@ -36,83 +36,89 @@ end
 
 ## product parities
 
-@pure conformalmask(V::T) where T<:VectorBundle = UInt(2)^(hasinf(V)+hasorigin(V))-1
+@pure conformalmask(V::M) where M<:Manifold = UInt(2)^(hasinf(V)+hasorigin(V))-1
 
-@pure function conformalcheck(V::T,A,B) where T<:VectorBundle
+@pure function conformalcheck(V::M,A,B) where M<:Manifold
     bt = conformalmask(V)
     i2o,o2i = DirectSum.hasinf2origin(V,A,B),DirectSum.hasorigin2inf(V,A,B)
     A&bt, B&bt, i2o, o2i, i2o ⊻ o2i
 end
 
-@pure function parityconformal(V::Signature{N,M,S},A,B) where {N,M,S}
+@pure function parityconformal(V::M,A,B) where M<:Manifold
     C,hio = A ⊻ B, hasinforigin(V,A,B)
     cc = hio || hasorigininf(V,A,B)
     A3,B3,i2o,o2i,xor = conformalcheck(V,A,B)
     pcc,bas = xor⊻i2o⊻(i2o&o2i), xor ? (A3|B3)⊻C : C
-    return pcc, bas, cc
+    return pcc, bas, cc, zero(UInt)
 end
 
[…]

### 2019-09-07 src/utilities.jl

@@ -3,7 +3,7 @@
 #   Grassmann Copyright (C) 2019 Michael Reed
 
 import Base: @pure, print, show, getindex, setindex!, promote_rule, ==, convert, ndims
-import DirectSum: Bits, bit2int, doc2m, indexbits, indices, diffmode, Dim
+import DirectSum: Bits, bit2int, doc2m, indexbits, indices, diffvars, Dim, diffmask, symmetricmask
 
 bcast(op,arg) = op ∈ (:(DirectSum.:∑),:(DirectSum.:-)) ? Expr(:.,op,arg) : Expr(:call,op,arg.args...)
 
@@ -169,7 +169,7 @@ Base.@pure promote_type(t...) = Base.promote_type(t...)
     assign_expr!(e,x,:bn,:(binomial_set(N)))
     assign_expr!(e,x,:df,:(dualform(V)))
     assign_expr!(e,x,:di,:(dualindex(V)))
-    assign_expr!(e,x,:D,:(diffmode(V)))
+    assign_expr!(e,x,:D,:(diffvars(V)))
     return x
 end
 

### 2019-09-09 src/algebra.jl
improved differential mixed symmetry dispatch #31

@@ -5,7 +5,7 @@
 import Base: +, -, *, ^, /, //, inv, <, >, <<, >>, >>>
 import AbstractLattices: ∧, ∨, dist
 import AbstractTensors: ⊗, ⊛, ⊙, ⊠, ⨼, ⨽, ⋆, ∗, rem, div, contraction
-import DirectSum: diffcheck, tangent, hasinforigin, hasorigininf
+import DirectSum: diffcheck, diffmode, tangent, hasinforigin, hasorigininf
 export tangent
 
 const Field = Real
@@ -50,7 +50,7 @@ function declare_mutating_operations(M,F,set_val,SUB,MUL)
                     if v ≠ 0 && !diffcheck(V,a,b)
                         A,B,Q,Z = symmetricmask(V,a,b)
                         val = (typeof(V)<:Signature || count_ones(A&B)==0) ? (parity(A,B,V) ? $SUB(v) : v) : $MUL(parityinner(A,B,V),v)
-                        diffvars(V)≠0 && !iszero(Z) && (val *= Basis{V}(Z))
+                        diffvars(V)≠0 && !iszero(Z) && (val *= Basis{V}(Z); count_ones(Q)+order(val)>diffmode(V) && (return m))
                         $s(m,val,(A⊻B)|Q,Dimension{N}())
                     end
                     return m
@@ -60,7 +60,7 @@ function declare_mutating_operations(M,F,set_val,SUB,MUL)
                         A,B,Q,Z = symmetricmask(V,a,b)
                         pcc,bas,cc = (hasinf(V) && hasorigin(V)) ? conformal(A,B,V) : (false,A⊻B,false)
                         val = (typeof(V)<:Signature || count_ones(A&B)==0) ? (parity(A,B,V)⊻pcc ? $SUB(v) : v) : $MUL(parityinner(A,B,V),pcc ? $SUB(v) : v)
-                        diffvars(V)≠0 && !iszero(Z) && (val *= Basis{V}(Z))
+                        diffvars(V)≠0 && !iszero(Z) && (val *= Basis{V}(Z); count_ones(Q)+order(val)>diffmode(V) && (return m))
                         $s(m,val,bas|Q,Dimension{N}())
                         cc && $s(m,hasinforigin(V,A,B) ? $SUB(val) : val,(conformalmask(V)⊻bas)|Q,Dimension{N}())
[…]

### 2019-09-09 src/multivectors.jl

@@ -96,18 +96,26 @@ for Blade ∈ MSB
         export $Blade
         @pure $Blade(b::Basis{V,G}) where {V,G} = $Blade{V}(b)
         @pure $Blade{V}(b::Basis{V,G}) where {V,G} = $Blade{V,G,b,Int}(1)
-        $Blade(v,b::TensorTerm{V}) where V = $Blade{V}(v,b)
-        $Blade{V}(v,b::SBlade{V,G}) where {V,G} = $Blade{V,G,basis(b)}(v*b.v)
-        $Blade{V}(v,b::MBlade{V,G}) where {V,G} = $Blade{V,G,basis(b)}(v*b.v)
-        $Blade{V}(v::T,b::Basis{V,G}) where {V,G,T} = $Blade{V,G,b,T}(v)
-        $Blade{V,G}(v::T,b::Basis{V,G}) where {V,G,T} = $Blade{V,G,b,T}(v)
-        $Blade{V,G}(v,b::SBlade{V,G}) where {V,G} = $Blade{V,G,basis(b)}(v*b.v)
-        $Blade{V,G}(v,b::MBlade{V,G}) where {V,G} = $Blade{V,G,basis(b)}(v*b.v)
-        $Blade{V,G,B}(v::T) where {V,G,B,T} = $Blade{V,G,B,T}(v)
         $Blade{V}(v::T) where {V,T} = $Blade{V,0,Basis{V}(),T}(v)
+        $Blade{V,G,B}(v::T) where {V,G,B,T} = $Blade{V,G,B,T}(v)
+        $Blade(v,b::TensorTerm{V}) where V = $Blade{V}(v,b)
+        $Blade{V}(v::T,b::Basis{V,G}) where {V,G,T} = $Blade{V,G}(v,b)
+        function $Blade{V,G}(v::T,b::Basis{V,G}) where {V,G,T}
+            order(v)+order(b)>diffmode(V) ? zero(V) : $Blade{V,G,b,T}(v)
+        end
+        function $Blade{V,G,B}(b::T) where T<:TensorTerm{V} where {V,G,B}
+            order(B)+order(b)>diffmode(V) ? zero(V) : $Blade{V,G,B,Any}(b)
+        end
         function show(io::IO,m::$Blade)
             T = valuetype(m)
-            print(io,((!(T<:TensorMixed))&&T∉parany ? [m.v] : ['(',m.v,')'])...,basis(m))
+            par = (!(T<:TensorMixed)) && T∉parany
[…]

### 2019-09-09 src/algebra.jl
further improved dispatch of differentials

@@ -50,21 +50,29 @@ function declare_mutating_operations(M,F,set_val,SUB,MUL)
                     if v ≠ 0 && !diffcheck(V,a,b)
                         A,B,Q,Z = symmetricmask(V,a,b)
                         val = (typeof(V)<:Signature || count_ones(A&B)==0) ? (parity(A,B,V) ? $SUB(v) : v) : $MUL(parityinner(A,B,V),v)
-                        diffvars(V)≠0 && !iszero(Z) && (val *= Basis{V}(Z); count_ones(Q)+order(val)>diffmode(V) && (return m))
+                        if diffvars(V)≠0 && !iszero(Z)
+                            #T≠Any && (return true)
+                            val *= getbasis(V,Z)
+                            count_ones(Q)+order(val)>diffmode(V) && (return false)
+                        end
                         $s(m,val,(A⊻B)|Q,Dimension{N}())
                     end
-                    return m
+                    return false
                 end
                 @inline function $(Symbol(:geom,s))(V::W,m::$M,a::Bits,b::Bits,v::S) where W<:Manifold{N} where {N,T<:$F,S<:$F,M}
                     if v ≠ 0 && !diffcheck(V,a,b)
                         A,B,Q,Z = symmetricmask(V,a,b)
                         pcc,bas,cc = (hasinf(V) && hasorigin(V)) ? conformal(A,B,V) : (false,A⊻B,false)
                         val = (typeof(V)<:Signature || count_ones(A&B)==0) ? (parity(A,B,V)⊻pcc ? $SUB(v) : v) : $MUL(parityinner(A,B,V),pcc ? $SUB(v) : v)
-                        diffvars(V)≠0 && !iszero(Z) && (val *= Basis{V}(Z); count_ones(Q)+order(val)>diffmode(V) && (return m))
+                        if diffvars(V)≠0 && !iszero(Z)
+                            #T≠Any && (return true)
+                            val *= getbasis(V,Z)
+                            count_ones(Q)+order(val)>diffmode(V) && (return false)
+                        end
[…]

### 2019-09-09 src/multivectors.jl

@@ -480,6 +480,7 @@ valuetype(t::MultiGrade) = promote_type(valuetype.(terms(t))...)
 @pure valuetype(::TensorMixed{T}) where T = T
 @inline value(::Basis,T=Int) = one(T)
 @inline value(m::VBV,T::DataType=valuetype(m)) = T∉(valuetype(m),Any) ? convert(T,m.v) : m.v
+@inline value_diff(m::T) where T<:TensorTerm = (v=value(m);typeof(v)<:TensorAlgebra ? v : m)
 @pure basis(m::Basis) = m
 @pure basis(m::Union{MBlade{V,G,B},SBlade{V,G,B}}) where {V,G,B} = B
 @pure grade(m::TensorTerm{V,G} where V) where G = G

### 2019-09-09 src/utilities.jl

@@ -154,13 +154,13 @@ Base.@pure promote_type(t...) = Base.promote_type(t...)
 
 @inline assign_expr!(e,x::Vector{Any},v::Symbol,expr) = v ∈ e && push!(x,Expr(:(=),v,expr))
 
-@pure function insert_expr(e,vec=:mvec,T=:(valuetype(a)),S=:(valuetype(b)),L=:(2^N))
+@pure function insert_expr(e,vec=:mvec,T=:(valuetype(a)),S=:(valuetype(b)),L=:(2^N);mv=0)
     x = Any[] # Any[:(sigcheck(sig(a),sig(b)))]
     assign_expr!(e,x,:N,:(ndims(V)))
     assign_expr!(e,x,:M,:(Int(N/2)))
     assign_expr!(e,x,:t,vec≠:mvec ? :Any : :(promote_type($T,$S)))
-    assign_expr!(e,x,:out,:(zeros($vec(N,t))))
-    assign_expr!(e,x,:mv,:(MBlade{V,0,getbasis(V,0),t}(0)))
+    assign_expr!(e,x,:out,mv≠0 ? :(t=Any;zeros(svec(N,Any)).+out) : :(zeros($vec(N,t))))
+    assign_expr!(e,x,:mv,:(MBlade{V,0,getbasis(V,0),$(mv≠0 ? Any : :t)}($mv)))
     assign_expr!(e,x,:r,:(binomsum(N,G)))
     assign_expr!(e,x,:bng,:(binomial(N,G)))
     assign_expr!(e,x,:bnl,:(binomial(N,L)))
@@ -170,6 +170,7 @@ Base.@pure promote_type(t...) = Base.promote_type(t...)
     assign_expr!(e,x,:df,:(dualform(V)))
     assign_expr!(e,x,:di,:(dualindex(V)))
     assign_expr!(e,x,:D,:(diffvars(V)))
+    assign_expr!(e,x,:μ,:(diffvars(V)≠0))
     return x
 end
 

### 2019-09-10 src/algebra.jl
activated nested differential type promotion

@@ -51,7 +51,7 @@ function declare_mutating_operations(M,F,set_val,SUB,MUL)
                         A,B,Q,Z = symmetricmask(V,a,b)
                         val = (typeof(V)<:Signature || count_ones(A&B)==0) ? (parity(A,B,V) ? $SUB(v) : v) : $MUL(parityinner(A,B,V),v)
                         if diffvars(V)≠0 && !iszero(Z)
-                            #T≠Any && (return true)
+                            T≠Any && (return true)
                             val *= getbasis(V,Z)
                             count_ones(Q)+order(val)>diffmode(V) && (return false)
                         end
@@ -65,7 +65,7 @@ function declare_mutating_operations(M,F,set_val,SUB,MUL)
                         pcc,bas,cc = (hasinf(V) && hasorigin(V)) ? conformal(A,B,V) : (false,A⊻B,false)
                         val = (typeof(V)<:Signature || count_ones(A&B)==0) ? (parity(A,B,V)⊻pcc ? $SUB(v) : v) : $MUL(parityinner(A,B,V),pcc ? $SUB(v) : v)
                         if diffvars(V)≠0 && !iszero(Z)
-                            #T≠Any && (return true)
+                            T≠Any && (return true)
                             val *= getbasis(V,Z)
                             count_ones(Q)+order(val)>diffmode(V) && (return false)
                         end
@@ -87,7 +87,7 @@ function declare_mutating_operations(M,F,set_val,SUB,MUL)
                             g,C,t,Z = $uct(A,B,V)
                             v = val
                             if diffvars(V)≠0 && !iszero(Z)
-                                #T≠Any && (return true)
+                                T≠Any && (return true)
                                 _,_,Q,_ = symmetricmask(V,A,B)
                                 v *= getbasis(V,Z)
                                 count_ones(Q)+order(v)>diffmode(V) && (return false)
@@ -481,7 +481,7 @@ function generate_product_algebra(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CON
         @inline function inneraddvalue!(mv::MBlade{V,0,B,T} where {W,B},α,β,γ::T) where {V,T<:$Field}
             if γ≠0
                 g,C,f,Z = interior(α,β,V)
-                #!iszero(C) && T≠Any && (return true)
+                !iszero(C) && T≠Any && (return true)
[…]

### 2019-09-19 paper/paper.tex
transitioned JuliaCon paper and revised dispatch

@@
 \usepackage{graphicx}
-\usepackage[left=1.00in, right=1.00in, top=1.00in, bottom=1.00in]{geometry}
+%\usepackage[left=1.00in, right=1.00in, top=1.00in, bottom=1.00in]{geometry}
 
@@
 %\newtheorem*{recall}{Recall}
-%\newtheorem*{note}{Note}
+%\newtheorem*{remark}{Note}
 %\newtheorem*{observe}{Observe}
@@
 \author{Michael Reed (Crucial Flow Research)}
-\title{Differential geometric algebra using Leibniz, Grassmann}
+\title{Differential geometric algebra with Leibniz and Grassmann}
 \date{July 25th, 2019}
@@
 	outer, regressive, inner, geometric, and cross products along with the Hodge star, adjoint, and multivector reversal operations. 
-	The kernelized operations are built on composite sparse tensor products and Hodge duality, with high dimensional support for up to 62 indices and staged caching / precompilation.
-Code generation enables making concise and extensible definitions.
+	The kernelized operations are built up from composite sparse tensor products and Hodge duality, with high dimensional support for up to 62 indices using staged caching and precompilation.
+Code generation enables concise and also extensible definitions.
 	The \textit{DirectSum.jl}
-	multivector parametric type polymorphism is based on various tangent vector spaces and conformal projective geometry.
-	Additionally, interoperability between different sub-algebras is enabled by \textit{AbstractTensors.jl},
+	multivector parametric type polymorphism is based on tangent vector spaces and conformal projective geometry.
+	Additionally, universal interoperability between different sub-algebras is enabled by \textit{AbstractTensors.jl},
 	on which the type system is built.
@@
 
-In this paper, the mathematical foundations and some of the nuances in the definitions specific to the \textit{Grassmann.jl} implementation are concisely described.
-The \textit{Grassmann.jl} package and its accompanying support packages provide an extensible platform for computing with geometric algebra at high dimensions. 
-The design is based on the \verb`TensorAlgebra` abstract type system interoperability from \textit{AbstractTensors.jl} with a \verb`VectorBundle` type parameter from \textit{DirectSum.jl}.
+Mathematical foundations and some of the nuances in the definitions specific to the \textit{Grassmann.jl} implementation are concisely described, along with the accompanying support packages that provide an extensible platform for computing with geometric algebra at high dimensions.
+The design is based on the \verb`TensorAlgebra` abstract type interoperability from \textit{AbstractTensors.jl} with a \verb`VectorBundle` type parameter from \textit{DirectSum.jl}.
 Abstract vector space type operations happen at compile-time, resulting in a differential conformal geometric algebra of hyper-dual multivector forms.
@@
 	\item \textbf{AbstractTensors.jl}: Tensor algebra abstract type interoperability with vector bundle parameter	
-	\item \textbf{Grassmann.jl}: $\langle$Grassmann-Clifford-Hestenes-Leibniz$\rangle$ differential conformal geometric algebra
-	\item \textbf{Leibniz.jl}: Operator algebras for mixed-symmetry multivariate differentiable tensor fields
+	\item \textbf{Grassmann.jl}: $\langle$Leibniz+Grassmann-Clifford-Hestenes$\rangle$ differential conformal geometric algebra
+	\item \textbf{Leibniz.jl}: Derivation operator algebras for tensor fields
 	\item \textbf{Reduce.jl}: Symbolic parser generator for Julia expressions using REDUCE algebra term rewriter
@@
 
-The nature of the geometric algebra code generation enables one to easily extend the abstract product operations to any specific number field type (including Leibniz differentials with \textit{Leibniz.jl} or symbolic coefficients with \textit{Reduce.jl}), by taking advantage of Julia's type system.
-With the type system, it is possible to construct mixed tensor products with their coefficients, e.g.
-bivector elements of Lie groups \cite{hestenes}\cite{shahshahani}.
+The nature of the geometric algebra code generation enables one to easily extend the abstract product operations to any specific number field type (including Leibniz differentials with \textit{Leibniz.jl} or symbolic coefficients with \textit{Reduce.jl}), by making use of Julia's type system.
+Mixed tensor products with their coefficients are constructed from these operations to work with bivector elements of Lie groups \cite{hestenes}\cite{shahshahani}.
 
@@
 
-The \textit{DirectSum.jl} package is a work in progress providing the necessary tools to work with arbitrary dual \verb`VectorBundle` elements with optional origin.
-Due to the parametric type system for the generating \verb`VectorBundle`, the Julia compiler can fully preallocate and often cache values efficiently ahead of run-time.
+The \textit{DirectSum.jl} package is a work in progress providing the necessary tools to work with an arbitrary \verb`Manifold` specified by an encoding.
+Due to the parametric type system for the generating \verb`VectorBundle`, the Julia compiler can fully pre-allocate and often cache values efficiently ahead of run-time.
 Although intended for use with the \textit{Grassmann.jl} package, \verb`DirectSum` can be used independently.
 
-\begin{definition}[Vector bundle of submanifold]
-	Let $T^\mu V\in\text{Vect}_{\mb K}$ be a \verb`VectorBundle<:Manifold` of rank $n$,
+\begin{definition}[Vector bundle of submanifolds]
+	Let $M = T^\mu V\in\text{Vect}_{\mb K}$ be a \verb`VectorBundle<:Manifold` of rank $n$,
 	\begin{align*}
-		T^\mu V &= (n,\mb P,g,\mu), & n,\mu &\in\mb N, & \mb P &\subseteq\gen{v_\infty,v_\emptyset}, & g &:V\times V\ra\mb K
+		T^\mu V &= (n,\mb P,g,\nu,\mu), & \mb P &\subseteq\gen{v_\infty,v_\emptyset}, & g &:V\times V\ra\mb K
 	\end{align*}
-	The type \verb+VectorBundle{n,+$\mb P$\verb+,g,+$\mu$\verb+}+ uses \textit{byte-encoded} data available at pre-compilation, where
+	The type \verb+VectorBundle{n,+$\mb P$\verb+,g,+$\nu,\mu$\verb+}+ uses \textit{byte-encoded} data available at pre-compilation, where
 	$\mb P$ specifies the null-basis from the projective split,
 	$g$ is a bilinear form that specifies the metric of the space,
-	and $\mu$ is an integer specifying the order of the tangent bundle (i.e. multiplicity limit of Leibniz-Taylor monomials).
+	and $\mu$ is an integer specifying the order of the tangent bundle (i.e. multiplicity limit of Leibniz-Taylor monomials). Lastly, $\nu$ is the number of tangent variables.
+\end{definition}
+	The metric signature of the \verb+Basis{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the \verb+Basis{V,1}+ element of the corresponding index squares to \verb`+1` or \verb`-1`.
+	For example, \verb`V"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
+	It is also possible to specify an arbitrary \verb`DiagonalForm` having numerical values for the basis with \verb`V"0,0,0"` or \verb`V"-1,1,1,1"`, although the $\pm$ format provides better performance.
+	Further development will result in more metric types.
+
+	The \verb`tangent(V,`$\mu$\verb`,`$\nu$\verb`)` map can be used to specify $\mu$ and $\nu$.
 
 	The dual space functor $(\cdot)':\text{Vect}_{\mb K}^\text{op}\ra\text{Vect}_{\mb K}$
-	is an involution which toggles a dual vector space with inverted signature with property $V' = \text{Hom}(V,\mb K)$ and having the \verb`Basis` generators
-	$$\gen{v_1,\dots,v_n,\partial_1,\dots,\partial_n}=T^\mu V\leftrightarrow T^\mu V' = \gen{w_1,\dots,w_n,\epsilon_1,\dots,\epsilon_n}.$$
-
-	The metric signature of the \verb+Basis{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the \verb+Basis{V,1}+ element of the corresponding index squares to \verb`+1` or \verb`-1`.
-	For example, \verb`V"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
-	It is possible to specify an arbitrary \verb`DiagonalForm` for the basis elements with \verb`V"0,0,0"` or \verb`V"-1,1,1,1"`, although the $\pm$ format has better performance.
-	Further development of the \textit{DirectSum.jl} will result in more metric types.
+	is an involution which toggles a dual vector space with inverted signature with property $V' = \text{Hom}(V,\mb K)$ and having \verb`Basis` generators
+	$$\gen{v_1,\dots,v_{n-\nu},\partial_1,\dots,\partial_\nu}=M\leftrightarrow M' = \gen{w_1,\dots,w_{n-\nu},\epsilon_1,\dots,\epsilon_\nu}$$
 
@@
 	The direct sum of a \verb`VectorBundle` and its dual \verb`V⊕V'` represents the full mother space \verb`V*`.
-	Additionally to the direct-sum operation, several other operations are supported, such as $\cup,\cap,\subseteq,\supseteq$ for set operations.
-	Due to the design of the \verb`VectorBundle` type system, these operations make code optimization easier at compile-time by evaluating the bit parameters.
+	In addition to the direct-sum operation, several other operations exist, such as $\cup,\cap,\subseteq,\supseteq$ for set operations.
+	Due to the design of the \verb`VectorBundle` dispatch, these operations enable code optimizations at compile-time provided by the bit parameters.
 	$$ \bigcup T^{\mu_i}V_i = \plr{|\mb P|+\max\set{n_i-|\mb P_i|}_i,\, \bigcup \mb P_i,\, \cup g_i,\, \max\set{\mu_i}_i} $$
 	$$ \bigoplus T^{\mu_i}V_i = \plr{\mlr{\mb P}+\sum (n_i-|\mb P_i|),\, \bigcup \mb P_i,\, \oplus_i g_i,\,\max\set{\mu_i}_i} $$
-\end{definition}
+	These are roughly the formulas used for those operations.
+%\end{definition}
 \begin{remark}
-	Although some of the type operations like $\bigcup$ and $\bigoplus$ are similar and sometimes result in equal values, the union and sum are entirely different operations in general.
-The \verb`tangent` map is used for specifying $\mu$.
+	Although some type operations like $\bigcup$ and $\bigoplus$ are similar and sometimes result in equal values, the union and sum are entirely different operations in general.
 \end{remark}
 
-For any \verb+SubManifold{m,V,s} where+ $\set{n\geq m\in\mb N,V\in\text{Vect}_{\mb K},s\in V}$ we can define the orthogonal space $Z$:
+Calling manifolds with sets of indices constructs the subspace representations.
+Given \verb`M(s::Int...)` one can encode \verb+SubManifold{+$|s|,M,s$\verb+}+ with induced orthogonal space $Z$:
 $$T^eV \subset T^\mu W \iff \exists Z\in\text{Vect}_{\mb K}(T^e(V\oplus Z) = T^{e\leq \mu}W,\,V\perp Z),$$
-such that computing unions of sub-manifolds is done by inspecting the parameter $s\in V\subseteq W$ and $s\notin Z$.
+such that computing unions of submanifolds is done by inspecting the parameter $s\in V\subseteq W$ and $s\notin Z$.
 
-\section{Tensor basis equivalence classes of Leibniz and Grassmann}
+\section{Tensor basis equivalence classes}% of Leibniz and Grassmann}
 
 The \verb`AbstractTensors` package is intended for universal interoperability of the abstract \verb`TensorAlgebra` type system.
-All \verb`TensorAlgebra{V}` subtypes contain \verb`V` in their type parameters, used to store a \verb`VectorBundle` value obtained from the \textit{DirectSum.jl} package.
-By itself, this package does not impose any structure or specifications on the \verb`TensorAlgebra{V}` subtypes and elements, aside from requiring $V$ to be a \verb`VectorBundle`.
-This means that different packages can create tensor types with a common underlying \verb`VectorBundle` structure.
+All \verb`TensorAlgebra{V}` subtypes have type parameter \verb`V`, used to store a \verb`VectorBundle` value obtained from \textit{DirectSum.jl}.
+By itself, this package does not impose any specifications or structure on the \verb`TensorAlgebra{V}` subtypes and elements, aside from requiring $V$ to be a \verb`VectorBundle`.
+This means that different packages can create tensor types having a common underlying \verb`VectorBundle` structure.
 
@@
 	Let $V\in\text{Vect}_{\mb k}$ be a \verb`VectorBundle` with dual space $V'$ and the basis elements $w_k:V\ra\mb K$, then for all $x\in V,c\in\mb K$ the properties $(w_i+w_j)(x) = w_i(x)+w_j(x)$ and $(cw_k)(x) = cw_k(x)$ hold.
-	An element of a mixed-symmetry \verb`TensorAlgebra{V}` is a multilinear mapping formally constructed by taking the tensor products of linear and multilinear maps,
+	An element of a mixed-symmetry \verb`TensorAlgebra{V}` is a multilinear mapping that is formally constructed by taking the tensor products of linear and multilinear maps,
 	$(\bigotimes_k \omega_k)(v_1,\dots,v_{\sum_k p_k}) = \prod_k \omega_k(v_1,\dots,v_{p_k})$.
@@
 \begin{definition}[Mixed-symmetry basis]
-	Combining linear basis generating elements with each other using the multi-linear tensor product yields a graded (decomposable) tensor \verb`Basis` $\langle w_{p_1}\otimes\dots\otimes w_{p_k}\rangle_k$, where the \verb`grade` $k$ is determined by the number of basis elements in the tensor product decomposition.
-	The algebra is partitioned into symmetric and anti-symmetric tensor equivalence classes.
-	For any pair of tensors, either
+	Combining the linear basis generating elements with each other using the multilinear tensor product yields a graded (decomposable) tensor \verb`Basis` $\langle w_{p_1}\otimes\dots\otimes w_{p_k}\rangle_k$, where \verb`grade` $k$ is determined by the number of $w_i$ basis elements in its tensor product decomposition.
+	The algebra partitions into symmetric and anti-symmetric tensor equivalence classes.
+	For any pair, %of tensors, either
 	\begin{align*}
-		&\us{\text{anti-symmetric}}{\omega\otimes\eta = -\eta\otimes\omega}, & &\us{\text{symmetric}}{\omega\otimes\eta = \eta\otimes\omega}.
+		&\us{\text{anti-symmetric}}{\omega\otimes\eta = -\eta\otimes\omega} & \text{or} &  &\us{\text{symmetric}}{\omega\otimes\eta = \eta\otimes\omega}.
 	\end{align*}
-	Typically the $k$ in $\plr{\partial_{p_1}\otimes\cdots\otimes\partial_{p_k}}^{(k)}$ is referred to as the \verb`order` of the element for fully symmetric tensors, which is tracked separately from the \verb`grade` such that $\partial_k\gen{w_j}_r = \gen{\partial_kw_j}_r$ and $(\partial_k)^{(r)}\omega_j = (\partial_kw_j)^{(r)}$.
-	Hence, there is a partitioning into \verb`even` grade components $\omega_+$ and \verb`odd` grade components $\omega_-$ with $\omega_++\omega_-=\omega$.
+	Typically the $k$ in a product $\plr{\partial_{p_1}\otimes\cdots\otimes\partial_{p_k}}^{(k)}$ is referred to as the \verb`order` of the element if it is fully symmetric, which is overall tracked separately from the \verb`grade` such that $\partial_k\gen{w_j}_r = \gen{\partial_kw_j}_r$ and $(\partial_k)^{(r)}\omega_j = (\partial_kw_j)^{(r)}$.
+	Hence, there is a partitioning into \verb`even` grade components $\omega_+$ and \verb`odd` grade components $\omega_-$ such that $\omega_++\omega_-=\omega$.
 \end{definition}
@@
 	Observe that the anti-symmetric property implies that $\omega\otimes\omega=0$, while the symmetric property neither implies nor denies such a property.
-	In 1862, Grassmann remarked \cite{grassmann-2} that the symmetric algebra of functions is by far more complicated than his anti-symmetric exterior algebra.
-	The first part of the book focused on anti-symmetric exterior algebra, while the more complex symmetric function algebra of Leibniz was subject of the second part of the book.
+	Grassmann remarked \cite{grassmann-2} in 1862 that the symmetric algebra of functions is by far more complicated than his anti-symmetric exterior algebra.
+	The first part of the book focused on anti-symmetric exterior algebra, while the more complex symmetric function algebra of Leibniz was subject of the second multivariable part of the book.
 	Elements $\omega_k$ in the space $\Lambda V$ of anti-symmetric algebra are often studied as unit quantum state vectors in a unitary probability space, where $\sum_k\omega_k\neq\bigotimes_k\omega_k$ is entanglement.
@@
 \begin{definition}
-	The Grassmann anti-symmetric exterior basis is denoted by $v_{i_1\dots i_g}\in\Lambda_gV$ with its dual basis $w^{i_1\cdots i_g}\in\Lambda^gV$, while the Leibniz symmetric basis will be $\partial_{i_1}^{\mu_1}\dots\partial_{i_g}^{\mu_g}\in L_gV$ with $\epsilon_{i_1}^{\mu_1}\dots\epsilon_{i_g}^{\mu_g}\in L^gV$ dual elements.
+	The Grassmann anti-symmetric exterior basis is denoted by $v_{i_1\dots i_g}\in\Lambda_gV$ with its dual $w^{i_1\cdots i_g}\in\Lambda^gV$, while the Leibniz symmetric basis will be $\partial_{i_1}^{\mu_1}\dots\partial_{i_g}^{\mu_g}\in L_gV$ with $\epsilon_{i_1}^{\mu_1}\dots\epsilon_{i_g}^{\mu_g}\in L^gV$ dual elements.
 \end{definition}
-Higher-order composite tensor elements will be denoted by an oriented-multi-set $X\in\text{OMSet}$ such that $w_X = \bigotimes_k w_{i_k}^{\otimes\mu_k}$ with $X = \plr{(i_1,\mu_1),\dots,(i_g,\mu_g)}$ and $|X|=\sum_k\mu_k$ is \verb`grade`+\verb`order`.
+Higher-order composite tensor elements will be denoted by an oriented-multi-set $X$ %\in\text{OMSet}$
+such that $w_X = \bigotimes_k w_{i_k}^{\otimes\mu_k}$ with $X = \plr{(i_1,\mu_1),\dots,(i_g,\mu_g)}$ and $|X|=\sum_k\mu_k$ is \verb`grade`,$\,$ \verb`order`.
 %There are two orientations and higher multiplicities result in zero for anti-symmetric tensors denoted by indices $\Lambda X\subseteq\Lambda V$, so the only interesting multiplicity is $\mu_k\equiv 1$.
-Indices $\Lambda X\subseteq\Lambda V$ that are anti-symmetric have two orientations and higher multiplicities of those result in zero values, so the only interesting multiplicity is $\mu_k\equiv 1$.
-Symmetric tensors have an ambiguous multiplicity of nilpotence; decide that $\epsilon_k^{\mu+1}=0$, so $\mu_k\leq\mu$ can be non-trivial, negative, or possibly unbounded.
+Anti-symmetric ndices $\Lambda X\subseteq\Lambda V$ have two orientations and higher multiplicities of them result in zero values, so the only interesting multiplicity is $\mu_k\equiv 1$.
+Symmetric tensors have an ambiguous multiplicity of nilpotence; decide that $\epsilon_k^{\mu+1}=0$, so $\mu_k\leq\mu$ can be non-trivial, negative, or unbounded.
+
 Grassmann's exterior algebra is fundamentally simpler in structure than the symmetric generated algebra, as it doesn't invoke the properties of multi-sets.
-The exterior Grassmann index algebra is related to the algebra of oriented sets and the Leibniz symmetric algebra is that of unoriented multi-sets. 
+The exterior Grassmann algebra is related to the algebra of oriented sets and the Leibniz symmetric algebra is that of unoriented multi-sets.
 Combined, the mixed-symmetry algebra yield a multi-linear propositional lattice.
 The formal sum of equal \verb`grade` elements is an oriented \verb`Chain` and with mixed \verb`grade` it is a \verb`MultiVector`.
-Thus, various standard operations on the oriented multi-sets are possible including $\cup,\cap,\oplus$ and most importantly the $X\ominus Y=(X\cup Y)\bs(X\cap Y)$ symmetric difference operation $\veebar$.
+Thus, various standard operations on the oriented multi-sets are possible including $\cup,\cap,\oplus$ and most importantly the index operation $X\ominus Y=(X\cup Y)\bs(X\cap Y)$, which is symmetric difference operation $\veebar$.
 
 In order to work with a \verb`TensorAlgebra{V}`, it is necessary for some computations to be cached. This is usually done automatically when accessed.
-The staging of the precompilation and caching is designed so that a user can smoothly transition between very high dimensional and low dimensional algebras in a single session, with varying levels of extra caching and optimizations.
-The parametric type formalism in \verb`Grassmann` is highly expressive to enable the pre-allocation of geometric algebra computations for specific sparse-subalgebras, including the representation of rotational groups.
-It is possible to reach \verb`Basis` elements having up to $n=62$ indices, % with \verb`TensorAlgebra` having higher maximum dimensions than supported by Julia natively.
+Staging of precompilation and caching is designed so that a user can smoothly transition between very high dimensional and low dimensional algebras in a single session, with varying levels of extra caching and optimizations.
+The parametric type formalism in \verb`Grassmann` is highly expressive and enables pre-allocation of geometric algebra computations involving specific sparse subalgebras, including the representation of rotational groups.
+
+It is possible to reach \verb`Basis` elements with up to $n=62$ indices, % with \verb`TensorAlgebra` having higher maximum dimensions than supported by Julia natively.
 requiring full alpha-numeric labeling with lower-case and capital letters. 
-However, Julia is only able to allocate full \verb`MultiVector` for $n\leq22$, with only sparse operations available at higher dimension form there.
+Full \verb`MultiVector` allocations are only possible for $n\leq22$, but sparse operations are also available at higher dimensions.
 While \verb`Grassmann.Algebra{V}` is a container for the \verb`TensorAlgebra` generators of $V$, the \verb`Grassmann.Algebra` is only cached for $n\leq8$.
-For a \verb`VectorBundle{n}` of dimension $8<n\leq22$, the \verb`Grassmann.SparseAlgebra` type is used.
-To reach higher dimensions, for $n>22$ the \verb`Grassmann.ExtendedAlgebra` type is used.
+For the range of dimensions $8<n\leq22$, the \verb`Grassmann.SparseAlgebra` type is used.
+To reach higher dimensions with $n>22$, the \verb`Grassmann.ExtendedAlgebra` type is used.
 
@@
 
-While oriented sets of the Grassmann exterior algebra are simpler, the parity \cite{artin} of $(-1)^\Pi$ is factored into transposition compositions when interchanging the ordering of the tensor product argument permutation.
-Alternatively, symmetric algebra does not need to track the parity but does have multiplicity in its indices.
-Symmetric differential function algebra of Leibniz trivializes the orientation property of index multi-sets, while Grassmann's exterior algebra is partitioned into two oriented equivalence classes by anti-symmetry.
-The full tensor algebra can be sub-partitioned into equivalence classes in multiple ways based on the composite symmetry, grade, and metric signature properties.
+While oriented sets of the Grassmann exterior algebra are simpler, the parity of $(-1)^\Pi$ is factored into transposition compositions when interchanging ordering of the tensor product argument permutations \cite{artin}.
+However, symmetrical algebra does not need to track this parity but has higher multiplicities in its indices.
+Symmetric differential function algebra of Leibniz trivializes the orientation into a single class of index multi-sets, while Grassmann's exterior algebra is partitioned into two oriented equivalence classes by anti-symmetry.
+The full tensor algebra can be sub-partitioned into equivalence classes in multiple ways based on element symmetry, grade, and metric signature composite properties.
 %It can be said that the Leibniz symmetry class has a neutral orientation, while Grassmann's anti-symmetric class is partitinoned into positive and negative orientation.
-Both of the symmetry classes can be characterized by the same geometric product, which is written as multiplication but explicitly denoted by $\ominus$ for clarity here.
+Both of the symmetry classes can be characterized by the same geometric product, which is typically written as multiplication but explicitly denoted by $\ominus$ for clarity here.
 %It is possible to express this universal product in terms of ordered-multi-set operations.
@@
 	The \textit{geometric algebraic product} is the $\Pi$ oriented symmetric difference operator $\ominus$ (weighted by the bilinear form $g$) and multi-set sum $\oplus$ applied to multilinear tensor products $\otimes$ in a single operation:
-	$$ \omega_X\ominus \eta_Y = \ub{\text{$\Lambda^1$-anti-symmetric, $\Lambda^g$-mixed-symmetry}}{(-1)^{\Pi(\Lambda X,\Lambda Y)}\det\mat{g_{\Lambda(X\cap Y)}} (\bigotimes_{k\in \Lambda(X\ominus Y)} w^{i_k})}\otimes \ub{\text{$L^g$-symmetric}}{(\bigotimes_{k\in L(X\oplus Y)} \epsilon_{i_k}^{\otimes\mu_k})}$$
+	$ \omega_X\ominus \eta_Y = $
+	%$$\ub{\text{$\Lambda^1$-anti-symmetric, $\Lambda^g$-mixed-symmetry}}{(-1)^{\Pi(X,Y)}\det\mat{g_{\Lambda(X\cap Y)}} (\bigotimes_{k\in \Lambda(X\ominus Y)} w^{i_k})} \otimes \ub{\text{$L^g$-symmetric}}{(\bigotimes_{k\in L(X\oplus Y)} \epsilon_{i_k}^{\otimes\mu_k})}$$
+	$$\ub{\text{$\Lambda^1$-anti-symmetric, $\Lambda^g$-mixed-symmetry}}{\ob{\text{orient parity}}{(-1)^{\Pi(X,Y)}}\ob{\text{intersect metric}}{\det\mat{g_{\Lambda(X\cap Y)}}} (\ob{(X\cup Y)\bs(X\cap Y)}{\bigotimes_{k\in \Lambda(X\ominus Y)} w^{i_k}}})\otimes (\ub{\text{$L^g$-symmetric}}{\ob{\text{multi-set sum}}{\bigotimes_{k\in L(X\oplus Y)} \epsilon_{i_k}^{\otimes\mu_k}}})$$
 \end{definition}
 
-\begin{note}
-	The product symbol $\ominus$ will be used to expliclity denote usage of the geometric algebraic product, altough the standard number product \verb`*` notation could also be used.
-This choice is to help emphasize that the geometric algebraic product is characterized by symmetric differencing of anti-symmetric indices.
-\end{note}
+\begin{remark}
+	The product symbol $\ominus$ will be used to denote explicitly usage of the geometric algebraic product, altough the standard number product \verb`*` notation could also be used.
+	The $\ominus$ choice helps emphasize that the geometric algebraic product is characterized by symmetric differencing of anti-symmetric indices.
+\end{remark}
 
 \begin{definition}
-	The symmetry properties of the tensor algebra can be characterized in terms of the geometric product by two averaging operations, which are the symmetrization $\odot$ and anti-symmetrization $\boxtimes$ operators:
+	Symmetry properties of the tensor algebra can be characterized in terms of the geometric product by two averaging operations, which are the symmetrization $\odot$ and anti-symmetrization $\boxtimes$ operators:
 	\begin{align*}
 		\bigodot_{k=1}^j \omega_k &= \frac1{j!}\sum_{\sigma\in S_P}\bigominus_k\omega_{\sigma(k)}, &
-		\bigboxtimes_{k=1}^j \omega_k &= \frac1{j!}\sum_{\sigma\in S_P}(-1)^{\Pi(\sigma)}\bigominus_k\omega_{\sigma(k)}
+		\bigboxtimes_{k=1}^j \omega_k &= \sum_{\sigma\in S_P}\frac{(-1)^{\Pi(\sigma)}}{j!}\bigominus_k\omega_{\sigma(k)}
 	\end{align*}
@@
 \begin{definition}[Exterior product]
-	Let $w_k:V^{p_k}\times V'^{q_k}\ra\mb K$ such that $k\in\Lambda^{p_k}V$, then for all $\sigma\in S_{\sum p_k}$
-	$$ (-1)^{\Pi(\sigma)}(\bigotimes_k \omega_k)(v_{\sigma(1)},\dots,v_{\sigma(\sum p_k)}) \sim \bigwedge_k \omega_k(v_{1},\dots,v_{p_k}) \iff \bigominus_k\omega_k = \bigboxtimes_k\omega_k $$
-	there is an equivalence relation $\sim$ which holds.
+	%Let $w_k:V^{p_k}\times V'^{q_k}\ra\mb K$ such that
+	Let $w_k\in\Lambda^{p_k}V$, then for all $\sigma\in S_{\sum p_k}$ define an equivalence relation $\sim$ such that
+	$$ (-1)^{\Pi(\sigma)}(\bigotimes_k \omega_k)(v_{\sigma(1)},\dots,v_{\sigma(\sum p_k)}) \sim \bigwedge_k \omega_k(v_{1},\dots,v_{p_k}) $$
+	if and only if $ \bigominus_k\omega_k = \bigboxtimes_k\omega_k$ holds.
+	%there is an equivalence relation $\sim$ which holds.
 	It has become typical to use the $\wedge$ product symbol to denote products of such elements as $\bigwedge\Lambda V \equiv \bigotimes\Lambda V/\sim$ modulo anti-symmetrization.
@@
 
-\begin{definition}[Symmetric tensor of Leibniz differentials]
-	Let $\partial_k = \frac\partial{\partial x_k}\in L_gV\,$ Leibnizian symmetric tensors, then there is an equivalence relation $\asymp$ which holds for each $\sigma\in S_p$ along with each derivation property,
+\begin{definition}[Symmetric Leibniz differentials]
+	Let $\partial_k = \frac\partial{\partial x_k}\in L_gV\,$ be Leibnizian symmetric tensors, then there is an equivalence relation $\asymp$ which holds for each $\sigma\in S_p$
 	\begin{align*}
-		(\bigotimes_k \partial_{\sigma(k)})\omega &\asymp (\partial_p \circ \dots\circ  \partial_1)\omega \iff \bigominus_k\partial_k = \bigodot_k\partial_k, & \partial_k(\omega\eta) &= \partial_k(\omega)\eta + \omega\partial_k(\eta).
+		(\bigotimes_k \partial_{\sigma(k)})\omega &\asymp (\partial_p \circ \dots\circ  \partial_1)\omega \iff \bigominus_k\partial_k = \bigodot_k\partial_k,
 	\end{align*}
+	along with each derivation $\partial_k(\omega\eta) = \partial_k(\omega)\eta + \omega\partial_k(\eta)$.
 \end{definition}
@@
 Since \verb`VectorBundle` choices are fundamental to \verb`TensorAlgebra` operations, the universal interoperability between \verb`TensorAlgebra{V}` elements with different associated \verb`VectorBundle` choices is naturally realized by applying the \verb`union` morphism to type operations.
-For example, $\bigwedge :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{\sum_kp_k}\bigcup_k V_k$. 
+For example, $$\bigwedge :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{\sum_kp_k}\bigcup_k V_k.$$
 % where $\bigwedge \Lambda V \equiv \bigotimes \Lambda V/\sim$ is made interoperable by $\cup$.
@@
 \begin{definition}[Reversed product]
-	The \textit{reversed geometric product} $\ast$ yields a Hilbert space structure:
+	Define the index reversed product $\ast$ which yields a Hilbert space structure:
 	\begin{align*}
-		\omega\ast\eta &= \tilde\omega\ominus\eta, & \omega\ast'\eta &= \omega\ominus\tilde\eta, & |\omega|^2 &= \omega\ast\omega, & |\omega| &= \sqrt{\omega\ast\omega}, & ||\omega|| = \text{Euclidean }|\omega|
+		\omega\ast\eta &= \tilde\omega\ominus\eta, & \text{or} & & \omega\ast'\eta &= \omega\ominus\tilde\eta,
+	\end{align*}
+	\begin{align*}
+		|\omega|^2 &= \omega\ast\omega, & |\omega| &= \sqrt{\omega\ast\omega}, & ||\omega|| = \text{Euclidean }|\omega|.
 	\end{align*}
@@
 \begin{definition}[Sandwich product]
-	The sandwich product is defined as $\eta\oslash\omega = (\eta\ast\omega)\ominus\eta$.
+	This product can be defined as $\eta\oslash\omega = (\eta\ast\omega)\ominus\eta$.
 Alternatively, the reversed definition is $\eta\obackslash\omega = \eta\ominus(\omega\ast'\eta)$ or in Julia $\eta\,$\verb`>>>`$\,\omega$, which is often found in literature.
 \end{definition}
-\begin{note}
-	Observe that $\ast$ and $\ast'$ could both be used in \verb`abs`, \verb`abs2`, and \verb`norm`; however they are different products.
+\begin{remark}
+	Observe that $\ast$ and $\ast'$ could both be exchanged in \verb`abs`, \verb`abs2`, and \verb`norm`; however, these are different products.
 	The \textit{scalar product} $\circledast$ is the scalar part of the reversed product $\eta\circledast\omega = \gen{\eta\ast\omega}$.
 	In general $\sqrt\omega = e^{(\log\omega)/2}$ is valid for \verb`inv`ertible multivectors $\omega\inv = \omega\ast|\omega|^{-2} = \tilde\omega/|\omega|^2$, where $\eta/\omega = \eta\ominus\omega\inv = \eta\ominus(\tilde\omega/(\omega\oslash1))$.
-\end{note}
-\begin{remark}
-	It is overall more simple to use the $\ast$ and $\oslash$ operations instead of the $\ast'$ and $\obackslash$ variations.
+	Observe that it is overall more simple and consistent to use the $\ast$ and $\oslash$ operations instead of the $\ast'$ and $\obackslash$ variations.
 \end{remark}
-The \verb`real` part $\Re\omega = (\omega+\tilde\omega)/2$ is defined by the property $|\Re\omega|^2 = (\Re\omega)^{\ominus2}$ and the \verb`imag` part $\Im\omega = (\omega-\tilde\omega)/2$ by $|\Im\omega|^2 = -(\Im\omega)^{\ominus2}$, such that for any multivector $\omega = \Re\omega+\Im\omega$ has real and imaginary partitioned by
-$$\gen{\tilde\omega}_r/\mlr{\gen{\omega}_r} = \sqrt{\gen{\tilde\omega}_r^2/\big|\gen{\omega}_r\big|^2} = \sqrt{\gen{\omega}_r\ast\gen{\omega}_r\inv} = \sqrt{\gen{\tilde\omega}_r/\gen{\omega}_r}=\sqrt{(-1)^{(r-1)r/2}} \in\set{1,\sqrt{-1}},$$
+The \verb`real` part $\Re\omega = (\omega+\tilde\omega)/2$ is defined by $|\Re\omega|^2 = (\Re\omega)^{\ominus2}$ and the \verb`imag` part $\Im\omega = (\omega-\tilde\omega)/2$ by $|\Im\omega|^2 = -(\Im\omega)^{\ominus2}$, such that for any multivector $\omega = \Re\omega+\Im\omega$ has real and imaginary partitioned by
+\begin{align*}
+	\gen{\tilde\omega}_r/\mlr{\gen{\omega}_r} &= \sqrt{\gen{\tilde\omega}_r^2/\big|\gen{\omega}_r\big|^2} = \sqrt{\gen{\omega}_r\ast\gen{\omega}_r\inv} \\
+	&= \sqrt{\gen{\tilde\omega}_r/\gen{\omega}_r}=\sqrt{(-1)^{(r-1)r/2}} \in\set{1,\sqrt{-1}},
+\end{align*}
 which is a unique partitioning completely independent of the metric space and manifold of the algebra \cite{chappell-iqbal-gunn-abbott}.
-$$ \omega\ast\omega = |\omega|^2 = |\Re\omega+\Im\omega|^2 = |\Re\omega|^2 + |\Im\omega|^2 + \Re\omega\ast\Im\omega + \Im\omega\ast\Re\omega = |\Re\omega|^2+|\Im\omega|^2 + 2\Re(\Re\omega\ast\Im\omega) $$
+$$ \omega\ast\omega = |\omega|^2 = |\Re\omega+\Im\omega|^2 = %|\Re\omega|^2 + |\Im\omega|^2 + \Re\omega\ast\Im\omega + \Im\omega\ast\Re\omega =
+|\Re\omega|^2+|\Im\omega|^2 + 2\Re(\Re\omega\ast\Im\omega) $$
 The \verb`radial` and \verb`angular` components in a multivector exponential are partitioned by the parity of their metric.
@@
 A universal unit volume element can be specified in terms of \verb`LinearAlgebra.UniformScaling`, which is independent of $V$ and has its interpretation only instantiated by the context of the \verb`TensorAlgebra{V}` element being operated on.
-The universal interoperability of \verb`LinearAlgebra.UniformScaling` as a pseudoscalar element which takes on the \verb`VectorBundle` form of any other \verb`TensorAlgebra` element is handled globally.
-This enables the usage of \verb`I` from \verb`LinearAlgebra` as a universal pseudoscalar element defined at every point $x$ of the manifold, which is mathematically denoted by $I=I(x)$ and specified by the $g(x)$ bilinear tensor field of $TM$.
+Universal interoperability of \verb`LinearAlgebra.UniformScaling` as the pseudoscalar element which takes on the \verb`VectorBundle` form of any other \verb`TensorAlgebra` element is handled globally.
+This enables the usage of \verb`I` from \verb`LinearAlgebra` as a universal pseudoscalar element defined at every point $x$ of a \verb`Manifold`, which is mathematically denoted by $I=I(x)$ and specified by the $g(x)$ bilinear tensor field of $TM$.
 
-\begin{definition}[Grassmann-Poincare-Hodge complement]
-	Let $\star\gen{\omega}_p = \gen{\omega}_p\ast I$, %= (-1)^{\frac{p(p+1)}2+\us k\sum i_k}\det\mat{ g_{i_ki_k}}\bigwedge_{m\in J(\omega)} w_m
+\begin{definition}[Poincare-Hodge dual complement]
+	Let $\star\gen{\omega}_p = \gen{\omega}_p\ast I = \gen{\tilde\omega}_p\ominus I$, %= (-1)^{\frac{p(p+1)}2+\us k\sum i_k}\det\mat{ g_{i_ki_k}}\bigwedge_{m\in J(\omega)} w_m
 	 then $\star : \Lambda^pV\ra\Lambda^{n-p}V$.
@@
 John Browne has discussed the Grassmann duality principle in book \cite{browne}, stating that every theorem (involving exterior and regressive products) can be translated into its dual theorem by replacing the $\wedge$ and $\vee$ operations and applying \textit{Poincare duality} (homology).
-First applying this Grassmann duality principle to the $\wedge$ product alone, let $\set{\omega_k}_k\in\Lambda^{p_k}V, P=\sum_kp_k$, then the co-product
-$\bigvee :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{P-(g-1)\#V}\bigcup_k V_k$ is obtained.
-in Grassmann's original notation $\wedge,\vee,\star$ operations were combined.
+First applying this Grassmann duality principle to the $\wedge$ product alone, let $\set{\omega_k}_k\in\Lambda^{p_k}V, P=\sum_kp_k$, then it is possible to obtain the co-product
+$\bigvee :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{P-(g-1)\#V}\bigcup_k V_k$.
+Grassmann's original notation implicitly combined $\wedge,\vee,\star$.
 The join $\wedge$ product is analogous to union $\cup$, the meet $\vee$ product is analogous to intersection $\cap$, and the orthogonal complement $\star\mapsto^\perp$ is negation.
-Together, $(\wedge,\vee,\star)$ yield an orthocomplementary propositional lattice (quantum logic) by
+Together, $(\wedge,\vee,\star)$ yield an orthocomplementary propositional lattice (quantum logic):
 \begin{align*}
-	(\star\bigvee_k &\omega_k)(v_1,\dots,v_P) = (\bigwedge_k\star\omega_k)(v_1,\dots,v_P) \quad \textit{DeMorgan's Law}.
+	(\star\bigvee_k &\omega_k)(v_1,\dots,v_P) = (\bigwedge_k\star\omega_k)(v_1,\dots,v_P) \quad \textit{DeMorgan's Law},
 \end{align*}
+where DeMorgan's law is used to derive tensor contractions.
 \begin{definition}
-	The left $\lrcorner$ and right $\llcorner$ contraction symmetrically define
+	The left $\lrcorner$ and right $\llcorner$ contraction are symmetrically defined
 	$ \gen{\omega}_r\cdot\gen{\eta}_s = \begin{cases} \omega\llcorner\eta=\omega\vee\star\eta & r\geq s \\ \omega\lrcorner\eta=\eta\vee\star\omega & r\leq s \end{cases} $.
-	Note that for $\omega,\eta$ of equal grade, the operations $\omega\circledast\eta = \omega\odot\eta = \omega\cdot\eta = \omega\llcorner\eta = \omega\lrcorner\eta$ are symmetric.
+	Note for $\omega,\eta$ of equal grade, $\omega\circledast\eta = \omega\odot\eta = \omega\cdot\eta = \omega\llcorner\eta = \omega\lrcorner\eta$ are all symmetric operations.
 \end{definition}
@@
 \begin{definition}
-	Let $\nabla = \sum_k\partial_kv_k$ and $\epsilon = \sum_k\epsilon_k(x)w_k \in \Omega^1V$ be unit sums of the mixed-symmetry basis.
+	Let $\nabla = \sum_k\partial_kv_k$ be a vector field and $\epsilon = \sum_k\epsilon_k(x)w_k \in \Omega^1V$ be unit sums of the mixed-symmetry basis.
 	Elements of $\Omega^pV$ are known as \textit{differential} $p$-\textit{forms} and both $\nabla$ and $\epsilon$ are \textit{tensor fields} dependent on $x\in W$.
@@
 \end{definition}
-\begin{note}
+\begin{remark}
 	The space $W$ does not have to equal $V\in\text{Vect}_{\mb K}$ above, as $\Omega^pV$ could have coefficients from $\mb K = LW$.
-\end{note}
+\end{remark}
 \begin{definition}
-	Define \cite{bishop-goldberg} the differential $d:\Omega^p V\ra\Omega^{p+1}V$ and co-differential $\delta:\Omega^pV\ra\Omega^{p-1}V$ such that
+	Define differential $d:\Omega^p V\ra\Omega^{p+1}V$ and co-differential $\delta:\Omega^pV\ra\Omega^{p-1}V$ such that \cite{bishop-goldberg}
 	\begin{align*}
-		\star d\omega &= \star(\nabla\wedge\omega) = \nabla\times\omega, & \omega\cdot\nabla &= \omega\vee\star\nabla = \partial\omega =-\delta\omega, 
+		\star d\omega &= \star(\nabla\wedge\omega) = \nabla\times\omega, & \omega\cdot\nabla &= \omega\vee\star\nabla = \partial\omega =-\delta\omega.
 	\end{align*}
 	These two maps have the special properties $d\circ d=0$ and $\partial\circ\partial = 0$ for any form $\omega$ and vector field $\nabla$. 
-	In topology there is \textit{boundary} operator $\partial$ that can be defined by $\partial\epsilon = \epsilon\cdot\nabla = \sum_k\partial_k\epsilon_k$ and is commonly discussed in terms the limit $\epsilon(x)\cdot\nabla\omega(x) = \lim_{h\ra0} \frac{\omega(x+h\epsilon)-\omega(x)}{h}$, which is the directional derivative \cite{sobczyk}.
+	In topology there is \textit{boundary} operator $\partial$ defined by $\partial\epsilon = \epsilon\cdot\nabla = \sum_k\partial_k\epsilon_k$ and is commonly discussed in terms the limit $\epsilon(x)\cdot\nabla\omega(x) = \lim_{h\ra0} \frac{\omega(x+h\epsilon)-\omega(x)}{h}$, which is the directional derivative \cite{sobczyk}.
 \end{definition}
@@
 	[Boundary of 3-simplex]
-	Faces as oriented \verb`Chain`: $\partial(w_{1234}) = -\partial_4w_{123}+\partial_3w_{124}-\partial_2w_{134}+\partial_1w_{234}$.
+	Faces of $n$-\verb`Chain` (oriented): $\partial(w_{1234}) = -\partial_4w_{123}+\partial_3w_{124}-\partial_2w_{134}+\partial_1w_{234}$.
 \end{example}
 \begin{theorem}[Leibniz-Taylor series]
-	Let $\partial_X=\bigominus_k\partial_k^{\mu_k}$ be defined so that $|X|=\sum_k\mu_k$, then $e^{\partial\epsilon}\omega(x)$ is
+	$\partial_X=\bigominus_k\partial_k^{\mu_k}$ is defined so that $|X|=\sum_k\mu_k$, then $e^{\partial\epsilon}\omega(x)$ is
 	\begin{align*}
+		e^{\partial\epsilon}\omega(x) =
 		\sum_{j=0}^\mu \frac{(\partial\epsilon)^{\ominus j}}{j!}\omega(x)
-		= \sum_{j=0}^\mu\sum_{|X|=j} \bigominus_k \frac{(\partial_{k}\epsilon_k(x))^{\mu_{k}}}{\mu_k!}\omega(x)
-		+ (\mu+1)\sum_{|X|=\mu+1}\int_0^1(1-t)^\mu\bigominus_k\frac{(\partial_k\epsilon_k(x))^{\mu_k}}{\mu_k!}\omega(x+t\epsilon)\,dt.
+		= \sum_{j=0}^\mu\sum_{|X|=j} \bigominus_k \frac{(\partial_{k}\epsilon_k(x))^{\mu_{k}}}{\mu_k!}\omega(x).
+		%+ (\mu+1)\sum_{|X|=\mu+1}\int_0^1(1-t)^\mu\bigominus_k\frac{(\partial_k\epsilon_k(x))^{\mu_k}}{\mu_k!}\omega(x+t\epsilon)\,dt.
 	\end{align*}
@@
 
-\begin{theorem}[Hilbert adjoint Hodge-DeRahm operators]
+\begin{theorem}[Integration by parts \& Stokes]
 	Let $ \nabla \in\Omega_1 V $ be a Leibnizian vector field operator, then $d,-\partial$ are Hilbert adjoint Hodge-DeRahm operators with $\gen{\,\ast\,}$
 	\begin{align*}
-		\int_M d\omega\wedge\star\eta +\int_M \omega\wedge\star\partial\eta &= 0, & \gen{d\omega\ast\eta} &=\gen{\omega\ast-\partial\eta}
+		\int_M d\omega\wedge\star\eta +\int_M \omega\wedge\star\partial\eta &= 0, & \gen{d\omega\ast\eta} &=\gen{\omega\ast-\partial\eta}.
 	\end{align*}
@@
 \begin{proof}
-	Observe that $\partial\omega = \omega\cdot\nabla = \star(\star\omega\wedge\star^2\nabla) = (-1)^n(-1)^{nk}\star d\star\omega$.
-	Then  substitute this into the integral $\int_M \omega\wedge(-1)^{mk+m+1}\star\star d\star\eta = (-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}\int_M\omega\wedge d\star\eta$,
-	with $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and also
+	$\partial\omega = \omega\cdot\nabla = \star(\star\omega\wedge\star^2\nabla) = (-1)^n(-1)^{nk}\star d\star\omega$.
+
+	Then  substitute this into $\int_M \omega\wedge(-1)^{mk+m+1}\star\star d\star\eta = (-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}\int_M\omega\wedge d\star\eta$,
+	with identity $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and
 	$ (-1)^k\int_M\omega\wedge d\star\eta = \int_M d(\omega\wedge\star\eta) - (-1)^{k-1}\omega\wedge d\star\eta = \int_M d\omega\wedge\star\eta$.
-	The other identity can be proved by relying on a variant of the \textit{common factor theorem} by Browne \cite{browne}.
+	Stokes identity can be proved by relying on a variant of the \textit{common factor theorem} by Browne \cite{browne}.
 \end{proof}
 \begin{theorem}[Clifford-Dirac-Laplacian]
-	Dirac operator $ \Delta^\frac12\omega = \mp\omega\ominus\nabla = \pm\nabla\wedge\omega \mp \omega\llcorner\nabla  = \pm d\omega\mp\partial\omega$ \cite{garling}.
+	The Dirac operator is $ \Delta^\frac12\omega = \mp\omega\ominus\nabla = \pm\nabla\wedge\omega \mp \omega\llcorner\nabla  = \pm d\omega\mp\partial\omega$ \cite{garling}.
 	\begin{align*}
-		\Delta\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \pm(\pm\omega\ominus\nabla)\ominus\nabla), & \mc H^p M = \setc{\Delta\omega = 0}{\omega\in \Omega^pM}
+		\Delta\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \pm(\pm\omega\ominus\nabla)\ominus\nabla).
 	\end{align*}
-	Elements $\omega$ are \textit{harmonic} if $\Delta\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, Hodge decomposition \cite{ivancevic}:
+	Elements $\omega$ are \textit{harmonic} if $\Delta\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, such that $\mc H^p M = \setc{\Delta\omega = 0}{\omega\in \Omega^pM}$.
+	Hodge \cite{ivancevic}:
 	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\delta\Omega^{p+1}M}$.
-	Warning $\nabla\omega\neq\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
+	Note: $\nabla\omega\neq\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
 \end{theorem}
@@
 \begin{align*}
-	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, &
+	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, \\
 	v_\infty\ominus v_\emptyset &= -1 + v_{\infty\emptyset}, & v_\emptyset\ominus v_\infty &=  -1 - v_{\infty\emptyset}
@@
 \begin{align*}
-	0 &\os d{\us\partial\rightleftarrows} \Omega^0(M) \os d{\us\partial\rightleftarrows} \Omega^1(M) \os d{\us\partial\leftrightarrows} \cdots \os d{\us\partial\rightleftarrows} \Omega^n(M) \os d{\us\partial\rightleftarrows} 0, & \mc H^pM &\cong \frac{\ker(d\Omega^pM)}{\im{d\Omega^{p-1}M}}, & \dim\mc H^pM &= \dim\frac{\ker(\delta\Omega^pM)}{\im{\delta\Omega^{p+1}M}}
+	0 &\os d{\us\partial\rightleftarrows} \Omega^0(M) \os d{\us\partial\rightleftarrows} \Omega^1(M) \os d{\us\partial\leftrightarrows} \cdots \os d{\us\partial\rightleftarrows} \Omega^n(M) \os d{\us\partial\rightleftarrows} 0,
+\end{align*}
+\begin{align*}
+	\mc H^pM &\cong \frac{\ker(d\Omega^pM)}{\im{d\Omega^{p-1}M}}, & \dim\mc H^pM &= \dim\frac{\ker(\delta\Omega^pM)}{\im{\delta\Omega^{p+1}M}}
 \end{align*}

### 2019-09-19 src/algebra.jl

@@ -522,8 +522,8 @@ function generate_product_algebra(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CON
         end
         *(a::F,b::Basis{V}) where {F<:$EF,V} = SBlade{V}(a,b)
         *(a::Basis{V},b::F) where {F<:$EF,V} = SBlade{V}(b,a)
-        *(a::F,b::MultiVector{T,V}) where {F<:$Field,T<:$Field,V} = MultiVector{promote_type(T,F),V}(broadcast($MUL,a,b.v))
-        *(a::MultiVector{T,V},b::F) where {F<:$Field,T<:$Field,V} = MultiVector{promote_type(T,F),V}(broadcast($MUL,a.v,b))
+        *(a::F,b::MultiVector{T,V}) where {F<:$Field,T,V} = MultiVector{promote_type(T,F),V}(broadcast($Sym.∏,a,b.v))
+        *(a::MultiVector{T,V},b::F) where {F<:$Field,T,V} = MultiVector{promote_type(T,F),V}(broadcast($Sym.∏,a.v,b))
         *(a::F,b::MultiGrade{V}) where {F<:$EF,V} = MultiGrade{V}(broadcast($MUL,a,b.v))
         *(a::MultiGrade{V},b::F) where {F<:$EF,V} = MultiGrade{V}(broadcast($MUL,a.v,b))
         ∧(a::$Field,b::$Field) = $MUL(a,b)

### 2019-09-19 src/multivectors.jl

@@ -8,6 +8,16 @@ abstract type GradedAlgebra{V,G} <: TensorAlgebra{V} end
 abstract type TensorTerm{V,G} <: GradedAlgebra{V,G} end
 abstract type TensorMixed{T,V} <: TensorAlgebra{V} end
 
+function Base.show_unquoted(io::IO, z::T, ::Int, prec::Int) where T<:TensorAlgebra
+    if T<:TensorMixed && Base.operator_precedence(:+) <= prec
+        print(io, "(")
+        show(io, z)
+        print(io, ")")
+    else
+        show(io, z)
+    end
+end
+
 # number fields
 
 Fields = (Real,Complex)
@@ -89,6 +99,8 @@ const MSB = (:MBlade,:SBlade)
 for Blade ∈ MSB
     eval(Expr(:struct,Blade ≠ :SBlade,:($Blade{V,G,B,T} <: TensorTerm{V,G}),quote
         v::T
+        $Blade{A,B,C,D}(t::E) where E<:D where {A,B,C,D} = new{A,B,C,D}(t)
+        $Blade{A,B,C,D}(t::E) where E<:TensorAlgebra{A} where {A,B,C,D} = new{A,B,C,D}(t)
     end))
 end
 for Blade ∈ MSB
@@ -229,8 +241,9 @@ end
 struct MultiVector{T,V,E} <: TensorMixed{T,V}
     v::Union{MArray{Tuple{E},T,1,E},SArray{Tuple{E},T,1,E}}
 end
-MultiVector{T,V}(v::MArray{Tuple{E},T,1,E}) where {T,V,E} = MultiVector{T,V,E}(v)
-MultiVector{T,V}(v::SArray{Tuple{E},T,1,E}) where {T,V,E} = MultiVector{T,V,E}(v)
+MultiVector{T,V}(v::MArray{Tuple{E},S,1,E}) where S<:T where {T,V,E} = MultiVector{S,V,E}(v)
+MultiVector{T,V}(v::SArray{Tuple{E},S,1,E}) where S<:T where {T,V,E} = MultiVector{S,V,E}(v)
+
 
 function getindex(m::MultiVector{T,V},i::Int) where {T,V}
     N = ndims(V)

### 2019-09-20 src/Grassmann.jl
improved arbitrary precision dispatch and SymEngine compat

@@ -439,6 +439,7 @@ function __init__()
         parsym = (parsym...,RExpr)
     end
     @require SymPy="24249f21-da20-56a4-8eb1-6a02cf4ae2e6" generate_product_algebra(:(SymPy.Sym),:svec,:(SymPy.:*),:(SymPy.:+),:(SymPy.:-),:(SymPy.conj))
+    @require SymEngine="123dc426-2d89-5057-bbad-38513e3affd8" generate_product_algebra(:(SymEngine.Basic),:svec,:(SymEngine.:*),:(SymEngine.:+),:(SymEngine.:-),:(SymEngine.conj))
 end
 
 end # module

### 2019-09-20 src/algebra.jl

@@ -482,7 +482,7 @@ function generate_product_algebra(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CON
     elseif Field ∈ (SymField,:(SymPy.Sym))
         declare_mutating_operations(:(SizedArray{Tuple{M},T,1,1}),Field,set_val,SUB,MUL)
     end
-    Field == :(SymPy.Sym) && for par ∈ (:parany,:parval,:parsym)
+    Field ∈ (:(SymPy.Sym),:(SymEngine.Basic)) && for par ∈ (:parany,:parval,:parsym)
         @eval $par = ($par...,$Field)
     end
     TF = Field ∉ Fields ? :Any : :T
@@ -1273,6 +1273,11 @@ end
 
 generate_product_algebra()
 generate_product_algebra(Complex)
+generate_product_algebra(Rational{BigInt},:svec)
+for Big ∈ (BigFloat,BigInt)
+    generate_product_algebra(Big,:svec)
+    generate_product_algebra(Complex{Big},:svec)
+end
 generate_product_algebra(SymField,:svec,:($Sym.:∏),:($Sym.:∑),:($Sym.:-),:($Sym.conj))
 
 const NSE = Union{Symbol,Expr,<:Real,<:Complex}

### 2019-09-21 src/Grassmann.jl
implemented support for AbstractAlgebra and GaloisFields

@@ -438,8 +438,10 @@ function __init__()
         parval = (parval...,RExpr)
         parsym = (parsym...,RExpr)
     end
-    @require SymPy="24249f21-da20-56a4-8eb1-6a02cf4ae2e6" generate_product_algebra(:(SymPy.Sym),:svec,:(SymPy.:*),:(SymPy.:+),:(SymPy.:-),:(SymPy.conj))
-    @require SymEngine="123dc426-2d89-5057-bbad-38513e3affd8" generate_product_algebra(:(SymEngine.Basic),:svec,:(SymEngine.:*),:(SymEngine.:+),:(SymEngine.:-),:(SymEngine.conj))
+    @require SymPy="24249f21-da20-56a4-8eb1-6a02cf4ae2e6" generate_product_algebra_svec(:SymPy,:Sym)
+    @require SymEngine="123dc426-2d89-5057-bbad-38513e3affd8" generate_product_algebra_svec(:SymEngine,:Basic)
+    @require AbstractAlgebra="c3fe647b-3220-5bb0-a1ea-a7954cac585d" generate_product_algebra_svec(:AbstractAlgebra,:SetElem)
+    @require GaloisFields="8d0d7f98-d412-5cd4-8397-071c807280aa" generate_product_algebra_svec(:GaloisFields,:AbstractGaloisField)
 end
 
 end # module

### 2019-09-21 src/algebra.jl

@@ -476,13 +476,13 @@ Sandwich product: ω>>>η = ω⊖η⊖(~ω)
 
 ### Product Algebra Constructor
 
-function generate_product_algebra(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj)
+function generate_product_algebra(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj,PAR=false)
     if Field == Grassmann.Field
         declare_mutating_operations(:(MArray{Tuple{M},T,1,M}),Number,Expr,:-,:*)
     elseif Field ∈ (SymField,:(SymPy.Sym))
         declare_mutating_operations(:(SizedArray{Tuple{M},T,1,1}),Field,set_val,SUB,MUL)
     end
-    Field ∈ (:(SymPy.Sym),:(SymEngine.Basic)) && for par ∈ (:parany,:parval,:parsym)
+    PAR && for par ∈ (:parany,:parval,:parsym)
         @eval $par = ($par...,$Field)
     end
     TF = Field ∉ Fields ? :Any : :T
@@ -1279,6 +1279,7 @@ for Big ∈ (BigFloat,BigInt)
     generate_product_algebra(Complex{Big},:svec)
 end
 generate_product_algebra(SymField,:svec,:($Sym.:∏),:($Sym.:∑),:($Sym.:-),:($Sym.conj))
+generate_product_algebra_svec(m,t) = generate_product_algebra(:($m.$t),:svec,:($m.:*),:($m.:+),:($m.:-),:($m.conj),true)
 
 const NSE = Union{Symbol,Expr,<:Real,<:Complex}
 

### 2019-09-22 src/Grassmann.jl
revised ∇ Derivation promotion and bug fix

@@ -414,9 +414,15 @@ import Leibniz: ∂, d
 
 generate_product_algebra(:(Leibniz.Operator),:svec)
 
-function (V::Signature{N})(d::Leibniz.Derivation{T,O}) where {N,T,O}
-    x=sum([(∂(V,k)^2) for k ∈ 1:N])^div(isodd(O) ? O-1 : O,2)
-    isodd(O) ? sum([(x*∂(V,k))*getbasis(V,1<<(k-1)) for k ∈ 1:N]) : x*getbasis(V,0)
+@pure function (W::Signature{N})(d::Leibniz.Derivation{T,O}) where {N,T,O}
+    C = mixedmode(W)<0
+    V = diffvars(W)≠0 ? W : tangent(W,O<2 ? 2 : O,C ? Int(ndims(W)/2) : ndims(W))
+    G = grade(V)
+    G2 = (C ? Int(G/2) : G)-1
+    ∇ = sum([getbasis(V,1<<(k+G))*getbasis(V,1<<k) for k ∈ 0:G2])
+    isone(O) && (return ∇)
+    x = (∇⋅∇)^div(isodd(O) ? O-1 : O,2)
+    isodd(O) ? sum([x*(getbasis(V,1<<(k+G))*getbasis(V,1<<k)) for k ∈ 0:G2]) : x
 end
 
 ∂(ω::T) where T<:TensorAlgebra{V} where V = ω⋅V(∇)

### 2019-09-22 src/algebra.jl

@@ -89,8 +89,8 @@ function declare_mutating_operations(M,F,set_val,SUB,MUL)
                                     T≠Any && (return true)
                                     _,_,Q,_ = symmetricmask(V,A,B)
                                     v *= getbasis(V,Z)
+                                    count_ones(Q)+order(v)>diffmode(V) && (return false)
                                 end
-                                count_ones(Q)+order(v)>diffmode(V) && (return false)
                             end
                             t && $s(m,typeof(V) <: Signature ? g ? $SUB(v) : v : $MUL(g,v),C,Dimension{N}())
                         end
@@ -1441,6 +1441,7 @@ function ^(v::T,i::Integer) where T<:TensorTerm
 end
 
 function Base.:^(v::T,i::S) where {T<:TensorAlgebra{V},S<:Integer} where V
+    isone(i) && (return v)
     out = one(V)
     if i < 8 # optimal choice ?
         for k ∈ 1:i

### 2019-09-22 src/multivectors.jl

@@ -481,6 +481,7 @@ MultiVector(v::MultiGrade{V}) where V = MultiVector{promote_type(typeval.(v.v)..
 ## Generic
 
 import Base: isinf, isapprox
+import DirectSum: grade
 import AbstractTensors: scalar, involute, unit, even, odd
 export basis, grade, hasinf, hasorigin, isorigin, scalar, norm
 

### 2019-09-22 src/parity.jl

@@ -53,7 +53,8 @@ end
 end
 
 @pure function parityregressive(V::Signature{N,M,S},a,b,::Grade{skew}=Grade{false}()) where {N,M,S,skew}
-    (A,B,Q,Z),NG,D = symmetricmask(V,a,b),N-diffvars(V),diffvars(V)
+    dv = diffvars(V)
+    (A,B,Q,Z),NG,D = symmetricmask(V,a,b),N-dv,dv
     α,β = complement(N,A,D),complement(N,B,D)
     cc = skew && (hasinforigin(V,A,β) || hasorigininf(V,A,β))
     if ((count_ones(α&β)==0) && !diffcheck(V,α,β)) || cc
@@ -66,7 +67,7 @@ end
             false, A+B≠0 ? complement(N,C,D) : g_zero(UInt)
         end
         par = parityright(S,A,N)⊻parityright(S,B,N)⊻parityright(S,C,N)
-        return (isodd(L*(L-N))⊻par⊻parity(N,S,α,β)⊻pcc)::Bool, bas|Q, true, Z
+        return (isodd(L*(L-grade(V)))⊻par⊻parity(N,S,α,β)⊻pcc)::Bool, bas|Q, true, Z
     else
         return false, g_zero(UInt), false, Z
     end

### 2019-10-16 src/Grassmann.jl
revised 𝒫, skeleton, subcomplex, and chain

@@ -455,9 +455,9 @@ function ↓(ω::T) where T<:TensorAlgebra{V} where V
     end
 end
 
-## skeleton
+## skeleton / subcomplex
 
-export skeleton
+export skeleton, 𝒫, collapse, subcomplex, chain
 
 absym(t) = abs(t)
 absym(t::Basis) = t
@@ -466,30 +466,45 @@ absym(t::SChain{T,V,G}) where {T,V,G} = SChain{T,V,G}(absym.(value(t)))
 absym(t::MChain{T,V,G}) where {T,V,G} = MChain{T,V,G}(absym.(value(t)))
 absym(t::MultiVector{T,V}) where {T,V} = MultiVector{T,V}(absym.(value(t)))
 
-function skeleton(x::T) where T<:TensorTerm{V} where V
-    X,B = absym(x),bits(basis(x))
-    count_ones(symmetricmask(V,B,B)[1])>1 ? X + subcomplex(absym(∂(X))) : X
+collapse(a,b) = a⋅absym(∂(b))
+
+function chain(t::T) where T<:TensorTerm{V} where V
+    N,B = ndims(V),bits(basis(t))
+    C = symmetricmask(V,B,B)[1]
+    G = count_ones(C)
+    G < 2 && (return t)
+    out,ind = zeros(mvec(N,2,Int)), indices(C,N)
+    setblade!(out,G==2 ? 1 : -1,bit2int(indexbits(N,[ind[1],ind[end]])),Dimension{N}())
+    for k ∈ 2:G
+        setblade!(out,1,bit2int(indexbits(N,ind[[k-1,k]])),Dimension{N}())
+    end
+    return MChain{Int,V,2}(out)
 end
-skeleton(x::S) where {S<:TensorMixed{T,V} where T} where V = absym(x) + subcomplex(absym(∂(x)))
-function subcomplex(x::S) where {S<:TensorMixed{T,V} where T} where V
+
+𝒫(t::T) where T<:TensorAlgebra = skeleton(t,Val{false}())
+skeleton(x::S,v=Val{true}()) where S<:TensorAlgebra = absym(x) + subcomplex(absym(∂(x)),v)
+function subcomplex(x::S,v::Val{T}=Val{true}()) where S<:TensorTerm{V} where {V,T}
+    B = bits(basis(x))
+    count_ones(symmetricmask(V,B,B)[1])>0 ? subcomplex(absym(∂(x)),v) : (T ? g_zero(V) : absym(x))
+end
[…]

### 2019-10-18 src/Grassmann.jl
improved ∇, ∂, subcomplex graphs, and symbolic compatibility

@@ -415,11 +415,9 @@ export ∇, Δ, ∂, d, ↑, ↓
 
 generate_products(:(Leibniz.Operator),:svec)
 
-@pure function (W::Signature{N})(d::Leibniz.Derivation{T,O}) where {N,T,O}
-    O < 1 && (return SChain{Int,W,1}(ones(Int,grade(W))))
-    C = mixedmode(W)<0
-    V = diffvars(W)≠0 ? W : tangent(W,O,C ? Int(ndims(W)/2) : ndims(W))
-    G,D = grade(V),diffvars(V)==1
+@pure function (V::Signature{N})(d::Leibniz.Derivation{T,O}) where {N,T,O}
+    (O<1||diffvars(V)==0) && (return SChain{Int,V,1}(ones(Int,ndims(V))))
+    G,D,C = grade(V),diffvars(V)==1,mixedmode(V)<0
     G2 = (C ? Int(G/2) : G)-1
     ∇ = sum([getbasis(V,1<<(D ? G : k+G))*getbasis(V,1<<k) for k ∈ 0:G2])
     isone(O) && (return ∇)
@@ -443,6 +441,16 @@ function ↑(ω::T) where T<:TensorAlgebra{V} where V
         (hasinf(PV) ? G.v∞ : G.v∅)*(ω2-1)*iω2 + 2*iω2*ω
     end
 end
+function ↑(ω,b)
+    ω2 = ω^2
+    iω2 = inv(ω2+1)
+    2*iω2*ω + (ω2-1)*iω2*b
+end
+function ↑(ω,p,m)
+    ω2 = ω^2
+    iω2 = inv(ω2+1)
+    2*iω2*ω + (ω2-1)*iω2*p + (ω2+1)*iω2*m
+end
 
 function ↓(ω::T) where T<:TensorAlgebra{V} where V
     PV = ℙ(V)
@@ -454,10 +462,12 @@ function ↓(ω::T) where T<:TensorAlgebra{V} where V
         ((ω∧b)*b)/(1-b⋅ω)
     end
 end
+↓(ω,b) = ((b∧ω)*b)/(1-ω⋅b)
+↓(ω,∞,∅) = (m=∞∧∅;inv(m)*(m∧ω)/(-ω⋅∞))
 
 ## skeleton / subcomplex
 
-export skeleton, 𝒫, collapse, subcomplex, chain
+export skeleton, 𝒫, collapse, subcomplex, chain, path
 
 absym(t) = abs(t)
[…]

### 2019-10-18 src/algebra.jl

@@ -1601,14 +1601,25 @@ for (nv,d) ∈ ((:inv,:/),(:inv_rat,://))
             end
             throw(error("inv($m) is undefined"))
         end
+        function $nv(m::MultiVector{Any,V}) where V
+            rm = ~m
+            d = rm*m
+            fd = $Sym.:∑([$Sym.:∏(a,a) for a ∈ value(d)]...)
+            sd = scalar(d)
+            $Sym.:∏(value(sd),value(sd)) == fd && (return $d(rm,sd))
+            for k ∈ 1:ndims(V)
+                @inbounds $Sym.:∑([$Sym.:∏(a,a) for a ∈ value(d[k])]...) == fd && (return $d(rm,d(k)))
+            end
+            throw(error("inv($m) is undefined"))
+        end
     end
     for Blade ∈ MSB
         @eval begin
             function $nv(b::$Blade{V,G,B,T}) where {V,G,B,T}
-                $Blade{V,G,B}($d(parityreverse(grade(V,B)) ? -one(T) : one(T),value(abs2_inv(B))*value(b)))
+                $Blade{V,G,B}($d(parityreverse(grade(V,B)) ? -one(T) : one(T),value(abs2_inv(B)*value(b))))
             end
             function $nv(b::$Blade{V,G,B,Any}) where {V,G,B}
-                $Blade{V,G,B}($d(parityreverse(grade(V,B)) ? -1 : 1,value(abs2_inv(B))*value(b)))
+                $Blade{V,G,B}($Sym.$d(parityreverse(grade(V,B)) ? -1 : 1,value($Sym.:∏(abs2_inv(B),value(b)))))
             end
         end
     end
@@ -1623,10 +1634,15 @@ for (nv,d) ∈ ((:inv,:/),(:inv_rat,://))
     end
 end
 
-function generate_inverses(Sym,T)
+function generate_inverses(Mod,T)
     for (nv,d,ds) ∈ ((:inv,:/,:($Sym.:/)),(:inv_rat,://,:($Sym.://)))
         for Term ∈ (:TensorTerm,MSC...,:MultiVector,:MultiGrade)
-            @eval $d(a::S,b::T) where {S<:$Term,T<:$Sym.$T} = a*$ds(1,b)
+            @eval $d(a::S,b::T) where {S<:$Term,T<:$Mod.$T} = a*$ds(1,b)
+        end
+        for Blade ∈ MSB
[…]

### 2019-10-19 paper/paper.tex
revised JuliaCon paper with some new examples

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 %\usepackage[left=1.00in, right=1.00in, top=1.00in, bottom=1.00in]{geometry}
@@
 \maketitle
-
+\begin{figure}[ht]
+\centerline{\includegraphics[width=4cm]{grassmann.png}}
+\caption*{github.com/chakravala/Grassmann.jl}
+\end{figure}
+\begin{itemize}
+	\item \textbf{DirectSum.jl}: Abstract tangent bundle vector space types (unions, intersections, sums, etc.)
+	\item \textbf{AbstractTensors.jl}: Tensor algebra abstract type interoperability with vector bundle parameter	
+	\item \textbf{Grassmann.jl}: $\langle$Leibniz+Grassmann-Clifford-Hestenes$\rangle$ differential geometric algebra of multivector forms
+	\item \textbf{Leibniz.jl}: Derivation operator algebras for tensor fields
+	\item \textbf{Reduce.jl}: Symbolic parser generator for Julia expressions using REDUCE algebra term rewriter
+\end{itemize}
 \begin{abstract}
 	The \textit{Grassmann.jl}
-	package provides tools for computations based on multi-linear algebra and spin groups using the extended geometric algebra known as Grassmann-Clifford-Hestenes-Leibniz algebra.
-	The primary operations are
-	outer, regressive, inner, geometric, and cross products along with the Hodge star, adjoint, and multivector reversal operations. 
+	package provides tools for computations based on multi-linear algebra and spin groups using the extended geometric algebra known as Leibniz-Grassmann-Clifford-Hestenes algebra.
+	Combinatorial products include
+	exterior, regressive, inner, and geometric; along with the Hodge star, adjoint, reversal, and boundary operators.
 	The kernelized operations are built up from composite sparse tensor products and Hodge duality, with high dimensional support for up to 62 indices using staged caching and precompilation.
-Code generation enables concise and also extensible definitions.
-	The \textit{DirectSum.jl}
+Code generation enables concise with highly extensible definitions.
+	\textit{DirectSum.jl}
 	multivector parametric type polymorphism is based on tangent vector spaces and conformal projective geometry.
-	Additionally, universal interoperability between different sub-algebras is enabled by \textit{AbstractTensors.jl},
+	Additionally, the universal interoperability between different sub-algebras is enabled by \textit{AbstractTensors.jl},
 	on which the type system is built.
@@
 \end{abstract}
-
 Mathematical foundations and some of the nuances in the definitions specific to the \textit{Grassmann.jl} implementation are concisely described, along with the accompanying support packages that provide an extensible platform for computing with geometric algebra at high dimensions.
@@
 Abstract vector space type operations happen at compile-time, resulting in a differential conformal geometric algebra of hyper-dual multivector forms.
-
-\begin{itemize}
-	\item \textbf{DirectSum.jl}: Abstract tangent bundle vector space types (unions, intersections, sums, etc.)
-	\item \textbf{AbstractTensors.jl}: Tensor algebra abstract type interoperability with vector bundle parameter	
-	\item \textbf{Grassmann.jl}: $\langle$Leibniz+Grassmann-Clifford-Hestenes$\rangle$ differential conformal geometric algebra
-	\item \textbf{Leibniz.jl}: Derivation operator algebras for tensor fields
-	\item \textbf{Reduce.jl}: Symbolic parser generator for Julia expressions using REDUCE algebra term rewriter
-\end{itemize}
 
@@
 	The type \verb+VectorBundle{n,+$\mb P$\verb+,g,+$\nu,\mu$\verb+}+ uses \textit{byte-encoded} data available at pre-compilation, where
-	$\mb P$ specifies the null-basis from the projective split,
+	$\mb P$ specifies the basis for up and down projection,
 	$g$ is a bilinear form that specifies the metric of the space,
@@
 \end{definition}
-	The metric signature of the \verb+Basis{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the \verb+Basis{V,1}+ element of the corresponding index squares to \verb`+1` or \verb`-1`.
-	For example, \verb`V"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
-	It is also possible to specify an arbitrary \verb`DiagonalForm` having numerical values for the basis with \verb`V"0,0,0"` or \verb`V"-1,1,1,1"`, although the $\pm$ format provides better performance.
-	Further development will result in more metric types.
-
-	The \verb`tangent(V,`$\mu$\verb`,`$\nu$\verb`)` map can be used to specify $\mu$ and $\nu$.
-
 The dual space functor $(\cdot)':\text{Vect}_{\mb K}^\text{op}\ra\text{Vect}_{\mb K}$
@@
 $$\gen{v_1,\dots,v_{n-\nu},\partial_1,\dots,\partial_\nu}=M\leftrightarrow M' = \gen{w_1,\dots,w_{n-\nu},\epsilon_1,\dots,\epsilon_\nu}$$
+where $v_i,w_i$ are a basis for the vectors and covectors, while $\partial_j,\epsilon_j$ are a basis for differential operators and tensor fields.
 
@@
 $$T^eV \subset T^\mu W \iff \exists Z\in\text{Vect}_{\mb K}(T^e(V\oplus Z) = T^{e\leq \mu}W,\,V\perp Z),$$
-such that computing unions of submanifolds is done by inspecting the parameter $s\in V\subseteq W$ and $s\notin Z$.
+such that computing unions of submanifolds is done by inspecting the parameter $s\in V\subseteq W$ and $s\notin Z$. Operations on \verb`Manifold` types is automatically handled at compile time.
+
+The metric signature of the \verb+Basis{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the \verb+Basis{V,1}+ element of the corresponding index squares to \verb`+1` or \verb`-1`.
+For example, \verb`S"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
+It is also possible to specify an arbitrary \verb`DiagonalForm` having numerical values for the basis with \verb`D"0,0,0"` or \verb`D"-1,1,1,1"`, although the $\pm$ format provides better performance.
+Further development will result in more metric types.
+
+Declaring an additional plane at infinity is done by specifying it in the string constructor with \verb`∞` at the first index (i.e.
+Riemann sphere \verb`S"∞+++"`).
+The hyperbolic geometry can be declared by \verb`∅` subsequently (i.e.
+Minkowski spacetime \verb`S"∅+++"`).
+Additionally, the \textit{null-basis} based on the projective split for confromal geometric algebra would be specified with \verb`∞∅` initially (i.e.
+5D CGA \verb`S"∞∅+++"`).
+These two declared basis elements are interpreted in the type system.
+%such that they are automatically selected for up and down projection.
+%propagate under transformations when combining mixed index sets (provided the \verb`Signature` is compatible).
+
+The \verb`tangent(V,`$\mu$\verb`,`$\nu$\verb`)` map can be used to specify $\mu$ and $\nu$.
 
@@
 
-Grassmann's exterior algebra is fundamentally simpler in structure than the symmetric generated algebra, as it doesn't invoke the properties of multi-sets.
-The exterior Grassmann algebra is related to the algebra of oriented sets and the Leibniz symmetric algebra is that of unoriented multi-sets.
+The Grassmann \verb`Basis` elements $v_k\in\Lambda_1V$ and $w^k\in\Lambda^1V$ are linearly independent vector and covector elements of $V$, while the Leibniz \verb`Operator` elements $\partial_k\in L_1V$ are partial tangent derivations and $\epsilon_k(x)\in L^1V$ are dependent functions of the \verb`tangent` manifold.
+Higher \verb`grade` elements of $\Lambda V$ correspond to \verb`SubManifold` subspaces, while higher \verb`order` function elements of $LV$ become homogenous polynomials and Taylor series.
+
+%Grassmann's exterior algebra is fundamentally simpler in structure than the symmetric generated algebra,
+Grassmann's exterior algebra doesn't invoke the properties of multi-sets, as it is related to the algebra of oriented sets; while the Leibniz symmetric algebra is that of unoriented multi-sets.
 Combined, the mixed-symmetry algebra yield a multi-linear propositional lattice.
-The formal sum of equal \verb`grade` elements is an oriented \verb`Chain` and with mixed \verb`grade` it is a \verb`MultiVector`.
-Thus, various standard operations on the oriented multi-sets are possible including $\cup,\cap,\oplus$ and most importantly the index operation $X\ominus Y=(X\cup Y)\bs(X\cap Y)$, which is symmetric difference operation $\veebar$.
+The formal sum of equal \verb`grade` elements is an oriented \verb`Chain` and with mixed \verb`grade` it is a \verb`MultiVector` simplicial complex.
+Thus, various standard operations on the oriented multi-sets are possible including $\cup,\cap,\oplus$ and the index operation $X\ominus Y=(X\cup Y)\bs(X\cap Y)$, which is symmetric difference operation $\veebar$.
 
@@
 
-While oriented sets of the Grassmann exterior algebra are simpler, the parity of $(-1)^\Pi$ is factored into transposition compositions when interchanging ordering of the tensor product argument permutations \cite{artin}.
-However, symmetrical algebra does not need to track this parity but has higher multiplicities in its indices.
+For the oriented sets of the Grassmann exterior algebra, the parity of $(-1)^\Pi$ is factored into transposition compositions when interchanging ordering of the tensor product argument permutations \cite{artin}.
+The symmetrical algebra does not need to track this parity, but has higher multiplicities in its indices.
 Symmetric differential function algebra of Leibniz trivializes the orientation into a single class of index multi-sets, while Grassmann's exterior algebra is partitioned into two oriented equivalence classes by anti-symmetry.
-The full tensor algebra can be sub-partitioned into equivalence classes in multiple ways based on element symmetry, grade, and metric signature composite properties.
+Full tensor algebra can be sub-partitioned into equivalence classes in multiple ways based on the element symmetry, grade, and metric signature composite properties.
 %It can be said that the Leibniz symmetry class has a neutral orientation, while Grassmann's anti-symmetric class is partitinoned into positive and negative orientation.
-Both of the symmetry classes can be characterized by the same geometric product, which is typically written as multiplication but explicitly denoted by $\ominus$ for clarity here.
+Both symmetry classes can be characterized by the same geometric product, which is typically written as multiplication but explicitly denoted by $\ominus$ for clarity here.
 %It is possible to express this universal product in terms of ordered-multi-set operations.
@@
 \begin{definition}
+	[Null-basis of projective split]
+	Let $v_\pm^2 = \pm1$ be a basis with $v_\infty = v_++v_-$ and $v_\emptyset = (v_--v_+)/2$
+\end{definition}
+An embedding space $\mb R^{n+1,1}$ carrying the action from the group $SO(n+1,1)$ then has
+$v_\infty^2 =0$, $v_\emptyset^2 =0$,
+$v_\infty \cdot v_\emptyset = 1$,  and $v_{\infty\emptyset}^2 = 1$ with
+Minkowski plane $v_{\infty\emptyset}$ having the Hestenes-Dirac-Clifford product properties
+\begin{align*}
+	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, \\
+	v_\infty\ominus v_\emptyset &= -1 + v_{\infty\emptyset}, & v_\emptyset\ominus v_\infty &=  -1 - v_{\infty\emptyset}
+\end{align*}
+
+\begin{definition}
 	Symmetry properties of the tensor algebra can be characterized in terms of the geometric product by two averaging operations, which are the symmetrization $\odot$ and anti-symmetrization $\boxtimes$ operators:
@@
 	Let $w_k\in\Lambda^{p_k}V$, then for all $\sigma\in S_{\sum p_k}$ define an equivalence relation $\sim$ such that
-	$$ (-1)^{\Pi(\sigma)}(\bigotimes_k \omega_k)(v_{\sigma(1)},\dots,v_{\sigma(\sum p_k)}) \sim \bigwedge_k \omega_k(v_{1},\dots,v_{p_k}) $$
+	$$ \bigwedge_k \omega_k(v_{1},\dots,v_{p_k}) \sim (-1)^{\Pi(\sigma)}(\bigotimes_k \omega_k)(v_{\sigma(1)},\dots,v_{\sigma(\sum p_k)}) $$
 	if and only if $ \bigominus_k\omega_k = \bigboxtimes_k\omega_k$ holds.
@@
 	\begin{align*}
-		(\bigotimes_k \partial_{\sigma(k)})\omega &\asymp (\partial_p \circ \dots\circ  \partial_1)\omega \iff \bigominus_k\partial_k = \bigodot_k\partial_k,
+		(\partial_p \circ \dots\circ  \partial_1)\omega &\asymp(\bigotimes_k \partial_{\sigma(k)})\omega  \iff \bigominus_k\partial_k = \bigodot_k\partial_k,
 	\end{align*}
@@
 \end{definition}
+
+%The dual $\epsilon$ notation is used to help unify geometric algebra with differential geometry. 
+Multiplication with an $\epsilon_i$ element is used help signify tensor fields so that differential operators are automatically applied in the \verb`Basis` algebra as $\partial_j\ominus (\omega\otimes\epsilon_i) = \partial_j(\omega\epsilon_i) \neq (\partial_j\otimes\omega)\ominus\epsilon_i$.
+%The meaning of differential operators and tensor fields is built into the \verb`Basis` algebra to make usage intuitive:
+\begin{lstlisting}[language = Julia]
+julia> using Reduce, Grassmann; @mixedbasis tangent(ℝ^2,3,2);
+julia> (∂1+∂12) * (:(x1^2*x2^2)*ϵ1 + :(sin(x1))*ϵ2)
+0.0 + (2 * x1 * x2 ^ 2)∂₁ϵ¹ + (cos(x1))∂₁ϵ² + (4 * x1 * x2)∂₁₂ϵ¹
+\end{lstlisting}
 
@@
 
-The Grassmann \verb`Basis` elements $v_k\in\Lambda_1V$ and $w^k\in\Lambda^1V$ are linearly independent vector and covector elements of $V$, while the Leibniz \verb`Operator` elements $\partial_k\in L_1V$ are partial tangent derivations and $\epsilon_k(x)\in L^1V$ are dependent functions of the \verb`tangent` manifold.
-Higher \verb`grade` elements of $\Lambda V$ correspond to \verb`SubManifold` subspaces, while higher \verb`order` function elements of $LV$ become homogenous polynomials and Taylor series.
+%\subsection{Grassmann's duality via Hodge complement}
 
-%\subsection{Grassmann's duality via Hodge complement}
+\newpage
+
+\section{Leibniz operators and Grassmann's Hodge-DeRahm theory}
 
@@
 \end{remark}
-
-\section{Leibniz operators and Grassmann's Hodge-DeRahm theory}
-
-John Browne has discussed the Grassmann duality principle in book \cite{browne}, stating that every theorem (involving exterior and regressive products) can be translated into its dual theorem by replacing the $\wedge$ and $\vee$ operations and applying \textit{Poincare duality} (homology).
+\begin{lstlisting}[language = Julia]
+using Grassmann, Compose
+x = Grassmann.Algebra(ℝ^7).v123
+Grassmann.graph(⋆(x)+x)
+draw(PDF("simplex.pdf",16cm,16cm),⋆(x)+x)
+\end{lstlisting}
+\begin{figure}[ht]
+\centerline{\includegraphics[width=0.42\textwidth]{triangle-tetrahedron.png}}
+\caption*{Triangle with its tetrahedron complement $\star v_{123} + v_{123}$ in $\mb R^7$}
+\end{figure}
+John Browne has discussed Grassmann duality principle in book \cite{browne}, stating that every theorem (involving either of the exterior and regressive products) can be translated into its dual theorem by replacing the $\wedge$ and $\vee$ operations and applying \textit{Poincare duality} (homology).
 First applying this Grassmann duality principle to the $\wedge$ product alone, let $\set{\omega_k}_k\in\Lambda^{p_k}V, P=\sum_kp_k$, then it is possible to obtain the co-product
@@
 \end{remark}
+
 \begin{definition}
@@
 	[Boundary of 3-simplex]
-	Faces of $n$-\verb`Chain` (oriented): $\partial(w_{1234}) = -\partial_4w_{123}+\partial_3w_{124}-\partial_2w_{134}+\partial_1w_{234}$.
+	Faces of simplex (oriented): $\partial(w_{1234}) = -\partial_4w_{123}+\partial_3w_{124}-\partial_2w_{134}+\partial_1w_{234}$.
 \end{example}
-\begin{theorem}[Leibniz-Taylor series]
-	$\partial_X=\bigominus_k\partial_k^{\mu_k}$ is defined so that $|X|=\sum_k\mu_k$, then $e^{\partial\epsilon}\omega(x)$ is
-	\begin{align*}
-		e^{\partial\epsilon}\omega(x) =
-		\sum_{j=0}^\mu \frac{(\partial\epsilon)^{\ominus j}}{j!}\omega(x)
-		= \sum_{j=0}^\mu\sum_{|X|=j} \bigominus_k \frac{(\partial_{k}\epsilon_k(x))^{\mu_{k}}}{\mu_k!}\omega(x).
-		%+ (\mu+1)\sum_{|X|=\mu+1}\int_0^1(1-t)^\mu\bigominus_k\frac{(\partial_k\epsilon_k(x))^{\mu_k}}{\mu_k!}\omega(x+t\epsilon)\,dt.
-	\end{align*}
-\end{theorem}
-The multivariate \textit{chain rule} is encoded into the geometric algebraic product when using mixed-symmetry.
 
@@
 	Hodge \cite{ivancevic}:
-	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\delta\Omega^{p+1}M}$.
+	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\partial\Omega^{p+1}M}$.
 	Note: $\nabla\omega\neq\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
@@
 
+\begin{lstlisting}[language = Julia]
+julia> using Reduce, Grassmann; @basis tangent(ℝ^2,3,2);
+
+julia> x = :x*v1 + ∂1v1 + ∂1*∂1v1 + ∂1*∂1*∂1v1
+0.0 + xv₁ + (1 + (1 + 1∂₁)∂₁)∂₁v₁
+
+julia> x^8
+x ^ 8 + (8 * x ^ 7 + (4 * (2x + 7) * x ^ 6 + (8 * (x ^ 2 + 7x + 7) * x ^ 5)∂₁)∂₁)∂₁
+\end{lstlisting}
+
 %\subsection{Projective null-cones of Dirac-Clifford-Hestenes}
 
-\begin{definition}
-	[Null-basis of projective split]
-	Let $v_\pm^2 = \pm1$ be a basis with $v_\infty = v_++v_-$ and $v_\emptyset = (v_--v_+)/2$
-\end{definition}
-An embedding space $\mb R^{n+1,1}$ carrying the action from the group $SO(n+1,1)$ then has
-$v_\infty^2 =0$, $v_\emptyset^2 =0$,
-$v_\infty \cdot v_\emptyset = 1$,  and $v_{\infty\emptyset}^2 = 1$ with
-Minkowski plane $v_{\infty\emptyset}$ having the Hestenes-Dirac-Clifford product properties
-\begin{align*}
-	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, \\
-	v_\infty\ominus v_\emptyset &= -1 + v_{\infty\emptyset}, & v_\emptyset\ominus v_\infty &=  -1 - v_{\infty\emptyset}
-\end{align*}
-Declaring an additional \textit{null-basis} is done by specifying it in the string constructor with \verb`∞` at the first index (i.e.
-\verb`S"∞+++"`).
-Likewise, an optional \textit{origin} can be declared by \verb`∅` subsequently (i.e.
-\verb`S"∅+++"` or \verb`S"∞∅+++"`).
-These two basis elements will be interpreted in the type system such that they propagate under transformations when combining a mixed index sets (provided the \verb`Signature` is compatible).
 \begin{example}[\textit{using Leibniz $\bigoplus\,$Grassmann}]
@@
 \end{example}
+For the null-basis, complement operations are different:
+\begin{align*}
+	\star v_\infty &= \star(v_++v_-) = (v_- + v_+)v_{1...n} = v_{\infty1...n} \\
+ 	\star 2v_\emptyset &= \star(v_--v_+) = (v_+ - v_-)v_{1...n} = -2v_{\emptyset1...n}
+\end{align*}
+The Hodge complement satisfies $\gen{\omega\ast\omega}I=\omega\wedge\star\omega$. This property is naturally a result of using the geometric product in the definition.
+An additional metric independent version of the complement operation is available with the \verb`!` operator,
+\begin{align*}
+	!v_\infty &= !(v_++v_-) = (v_- - v_+)v_{1...n} = 2v_{\emptyset1...n} \\
+ 	!2v_\emptyset &= !(v_--v_+) = (v_+ + v_-)v_{1...n} = -v_{\infty1...n}
+\end{align*}
+That variation of complement satisfies $\lambda I = \omega\,\wedge\,!\omega$ instead.
+
+\begin{theorem}[Leibniz-Taylor series]
+	$\partial_X=\bigominus_k\partial_k^{\mu_k}$ is defined so that $|X|=\sum_k\mu_k$, then $e^{\partial\epsilon}\omega(x)$ is
+	\begin{align*}
+		e^{\partial\epsilon}\omega(x) =
+		\sum_{j=0}^\mu \frac{(\partial\epsilon)^{\ominus j}}{j!}\omega(x)
+		= \sum_{j=0}^\mu\sum_{|X|=j} \bigominus_k \frac{(\partial_{k}\epsilon_k(x))^{\mu_{k}}}{\mu_k!}\omega(x).
+		%+ (\mu+1)\sum_{|X|=\mu+1}\int_0^1(1-t)^\mu\bigominus_k\frac{(\partial_k\epsilon_k(x))^{\mu_k}}{\mu_k!}\omega(x+t\epsilon)\,dt.
+	\end{align*}
+\end{theorem}
+The multivariate \textit{chain rule} is encoded into the geometric algebraic product when using mixed-symmetry.
+
+In the following examples, different possible discrete bivector topologies in a projective Riemann sphere setting are examined. 
+The figure below is based on the product topology of two rotation bivectors.
+When the standard $\mb R^4$ basis is used with projective geometric algebra, the one parameter Lie group can be visualized in the form of a torus in $\mb R^3$.
+When the fourth $v_\infty$ basis direction is rotated into the Minkowski plane, the double rotation becomes a helix with translational single rotation.
+
+\begin{lstlisting}[language = Julia]
+using Grassmann, Makie; @basis S"∞+++"
+f(t) = (↓(exp(π*t*((3/7)*v12+v∞3))>>>↑(v1+v2+v3)))
+lines(points(f,V(2,3,4)))
+\end{lstlisting}
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{0.3\textwidth}
+		\includegraphics[width=\textwidth]{torus.png}
+		\caption{Projective double rotation orbit}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.15\textwidth}
+		\includegraphics[width=\textwidth]{helix.png}
+		\caption{Period translation}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\caption{Different variations of bivectors in $\mb R^4$ discrete topology.}
+	\begin{subfigure}[b]{0.14\textwidth}
+		\includegraphics[width=\textwidth]{product.png}
+		\caption{v_{12}+v_{34}}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.14\textwidth}
+		\includegraphics[width=\textwidth]{strange.png}
+		\caption{v_{14}+v_{24}+v_{34}}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.14\textwidth}
+		\includegraphics[width=\textwidth]{toroid-modulation.png}
+		\caption{v_{124}+v_{34}}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+\end{figure}
+
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.45\textwidth]{orbit-3.png}}
+%\caption*{$\downarrow(e^{t(v_{12}+v_\infty(sin(3t)3v_1+cos(2t)7v_2-sin(5t)4v_3)/2)}\obackslash\uparrow(v_1+v_2-v_3))$}
+\caption{Modulated bivector group on Riemann sphere S"∞+++"}
+\end{figure}
 
@@
 
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.42\textwidth]{orbit-2.png}}
+\caption*{$\downarrow(e^{tv_\infty(sin(3t)3v_1+cos(2t)7v_2-sin(5t)4v_3)/2}\obackslash\uparrow(v_1+v_2-v_3))$}
+\end{figure}
+
+\iffalse
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.42\textwidth]{orbit-1.png}}
+\caption{Modulated bivector group on Riemann sphere S"∞+++"}
+\end{figure}
+\fi
+
+\begin{lstlisting}[language = Julia]
+skeleton(v123)
+betti(ans)
+subcomplex(v123)
+\end{lstlisting}
+
 \input{bib.tex}

### 2019-10-19 src/Grassmann.jl

@@ -495,12 +495,12 @@ end
 path(t) = chain(t,Val{false}())
 
 𝒫(t::T) where T<:TensorAlgebra = skeleton(t,Val{false}())
-skeleton(x::S,v=Val{true}()) where S<:TensorAlgebra = absym(x) + subcomplex(absym(∂(x)),v)
-function subcomplex(x::S,v::Val{T}=Val{true}()) where S<:TensorTerm{V} where {V,T}
+subcomplex(x::S,v=Val{true}()) where S<:TensorAlgebra = skeleton(absym(∂(x)),v)
+function skeleton(x::S,v::Val{T}=Val{true}()) where S<:TensorTerm{V} where {V,T}
     B = bits(basis(x))
-    count_ones(symmetricmask(V,B,B)[1])>0 ? subcomplex(absym(∂(x)),v) : (T ? g_zero(V) : absym(x))
+    count_ones(symmetricmask(V,B,B)[1])>0 ? absym(x)+skeleton(absym(∂(x)),v) : (T ? g_zero(V) : absym(x))
 end
-function subcomplex(x::S,v::Val{T}=Val{true}()) where {S<:TensorMixed{Q,V} where Q} where {V,T}
+function skeleton(x::S,v::Val{T}=Val{true}()) where {S<:TensorMixed{Q,V} where Q} where {V,T}
     N,G,g = ndims(V),grade(x),0
     ib = indexbasis(N,G)
     for k ∈ 1:binomial(N,G)
@@ -510,7 +510,7 @@ function subcomplex(x::S,v::Val{T}=Val{true}()) where {S<:TensorMixed{Q,V} where
     end
     return g
 end
-function subcomplex(x::MultiVector{S,V} where S,v::Val{T}=Val{true}()) where {V,T}
+function skeleton(x::MultiVector{S,V} where S,v::Val{T}=Val{true}()) where {V,T}
     N,g = ndims(V),0
     for i ∈ 0:N
         R = binomsum(N,i)
@@ -602,7 +602,7 @@ function __init__()
         Base.convert(::Type{GeometryTypes.Point},t::SChain{T,V,G}) where {T,V,G} = G == 1 ? GeometryTypes.Point(value(vector(t))) : GeometryTypes.Point(zeros(T,ndims(V))...)
         GeometryTypes.Point(t::T) where T<:TensorAlgebra = convert(GeometryTypes.Point,t)
         export points
[…]

### 2019-10-27 paper/paper.tex
improved Betti numbers, paper revisions, changed Blade to Simplex

@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=4cm]{grassmann.png}}
+%\centerline{\includegraphics[width=4cm]{grassmann.png}}
+\centerline{\includegraphics[width=4cm]{../docs/src/assets/logo.png}}
 \caption*{github.com/chakravala/Grassmann.jl}
 \end{figure}
-\begin{itemize}
-	\item \textbf{DirectSum.jl}: Abstract tangent bundle vector space types (unions, intersections, sums, etc.)
-	\item \textbf{AbstractTensors.jl}: Tensor algebra abstract type interoperability with vector bundle parameter	
-	\item \textbf{Grassmann.jl}: $\langle$Leibniz+Grassmann-Clifford-Hestenes$\rangle$ differential geometric algebra of multivector forms
-	\item \textbf{Leibniz.jl}: Derivation operator algebras for tensor fields
-	\item \textbf{Reduce.jl}: Symbolic parser generator for Julia expressions using REDUCE algebra term rewriter
-\end{itemize}
 \begin{abstract}
@@
 \end{abstract}
+\begin{itemize}
+	\item \textbf{DirectSum.jl}: Abstract tangent bundle vector space types (unions, intersections, sums, etc.)
+	\item \textbf{AbstractTensors.jl}: Tensor algebra abstract type interoperability with vector bundle parameter
+	\item \textbf{Grassmann.jl}: $\langle$Leibniz+Grassmann-Clifford-Hestenes$\rangle$ differential geometric algebra of multivector forms
+	\item \textbf{Leibniz.jl}: Derivation operator algebras for tensor fields
+	\item \textbf{Reduce.jl}: Symbolic parser generator for Julia expressions using REDUCE algebra term rewriter
+\end{itemize}
 Mathematical foundations and some of the nuances in the definitions specific to the \textit{Grassmann.jl} implementation are concisely described, along with the accompanying support packages that provide an extensible platform for computing with geometric algebra at high dimensions.
@@
 
-It is possible to reach \verb`Basis` elements with up to $n=62$ indices, % with \verb`TensorAlgebra` having higher maximum dimensions than supported by Julia natively.
+It is possible to reach \verb`Simplex` elements with up to $n=62$ vertices, % with \verb`TensorAlgebra` having higher maximum dimensions than supported by Julia natively.
 requiring full alpha-numeric labeling with lower-case and capital letters. 
@@
 	Let $v_\pm^2 = \pm1$ be a basis with $v_\infty = v_++v_-$ and $v_\emptyset = (v_--v_+)/2$
-\end{definition}
-An embedding space $\mb R^{n+1,1}$ carrying the action from the group $SO(n+1,1)$ then has
+An embedding space $\mb R^{p+1,q+1}$ carrying the action from the group $O(p+1,q+1)$ then has
 $v_\infty^2 =0$, $v_\emptyset^2 =0$,
@@
 \end{align*}
-
+\end{definition}
 \begin{definition}
@@
 \begin{definition}[Reverse, involute, conjugate]
-	The \verb`reverse` of $\gen{\omega}_r$ is defined as $\gen{\tilde\omega}_r = (-1)^{(r-1)r/2}\gen{\omega}_r$, while the \verb`involute` is $(-1)^r\gen{\omega}_r$ and Clifford \verb`conj`  $\gen{\omega}_r^\ddagger$ is the composition of \verb`involute` and \verb`reverse`.
+	The \verb`reverse` of $\gen{\omega}_r$ is defined as $\gen{\tilde\omega}_r = (-1)^{(r-1)r/2}\gen{\omega}_r$, while the \verb`involute` is $\gen{\omega}_r^\times=(-1)^r\gen{\omega}_r$ and Clifford \verb`conj`  $\gen{\omega}_r^\ddagger$ is the composition of \verb`involute` and \verb`reverse`.
 \end{definition}
@@
 \end{definition}
+\begin{remark}
+	Observe that $\ast$ and $\ast'$ could both be exchanged in \verb`abs`, \verb`abs2`, and \verb`norm`; however, these are different products.
+	The \textit{scalar product} $\circledast$ is the scalar part, so $\eta\circledast\omega = \gen{\eta\ast\omega}$.
+	In general $\sqrt\omega = e^{(\log\omega)/2}$ is valid for invertible $\omega$.
+\end{remark}
+\begin{definition}[Inverse]
+	$\omega\inv = \omega\ast(\omega\ast\omega)\inv = \tilde\omega/|\omega|^2$, with $\eta/\omega = \eta\ominus\omega\inv$ and % = \eta\ominus(\tilde\omega/(1\oslash\omega))$.
+	$\eta\bs\omega = \eta\inv\ominus\omega$.
+\end{definition}
 \begin{definition}[Sandwich product]
-	This product can be defined as $\eta\oslash\omega = (\eta\ast\omega)\ominus\eta$.
-Alternatively, the reversed definition is $\eta\obackslash\omega = \eta\ominus(\omega\ast'\eta)$ or in Julia $\eta\,$\verb`>>>`$\,\omega$, which is often found in literature.
+	This product can be defined as $\eta\oslash\omega = \omega\bs\eta\ominus\omega^\times$.
+Alternatively, the reversed definition is $\eta\obackslash\omega = \eta^\times\ominus\omega/\eta$ or in Julia $\eta\,$\verb`>>>`$\,\omega$, which is often found in literature.
 \end{definition}
 \begin{remark}
-	Observe that $\ast$ and $\ast'$ could both be exchanged in \verb`abs`, \verb`abs2`, and \verb`norm`; however, these are different products.
-	The \textit{scalar product} $\circledast$ is the scalar part of the reversed product $\eta\circledast\omega = \gen{\eta\ast\omega}$.
-	In general $\sqrt\omega = e^{(\log\omega)/2}$ is valid for \verb`inv`ertible multivectors $\omega\inv = \omega\ast|\omega|^{-2} = \tilde\omega/|\omega|^2$, where $\eta/\omega = \eta\ominus\omega\inv = \eta\ominus(\tilde\omega/(\omega\oslash1))$.
-	Observe that it is overall more simple and consistent to use the $\ast$ and $\oslash$ operations instead of the $\ast'$ and $\obackslash$ variations.
+	Observe that it is overall more simple and consistent to use $\set{\ast,\oslash}$ operations instead of $\set{\ast',\obackslash}$.
 \end{remark}
-The \verb`real` part $\Re\omega = (\omega+\tilde\omega)/2$ is defined by $|\Re\omega|^2 = (\Re\omega)^{\ominus2}$ and the \verb`imag` part $\Im\omega = (\omega-\tilde\omega)/2$ by $|\Im\omega|^2 = -(\Im\omega)^{\ominus2}$, such that for any multivector $\omega = \Re\omega+\Im\omega$ has real and imaginary partitioned by
+The \verb`real` part $\Re\omega = (\omega+\tilde\omega)/2$ is defined by $|\Re\omega|^2 = (\Re\omega)^{\ominus2}$ and the \verb`imag` part $\Im\omega = (\omega-\tilde\omega)/2$ by $|\Im\omega|^2 = -(\Im\omega)^{\ominus2}$, such that $\omega = \Re\omega+\Im\omega$ has real and imaginary partitioned by
 \begin{align*}
@@
 x = Grassmann.Algebra(ℝ^7).v123
-Grassmann.graph(⋆(x)+x)
-draw(PDF("simplex.pdf",16cm,16cm),⋆(x)+x)
+Grassmann.graph(x+!x)
+draw(PDF("simplex.pdf",16cm,16cm),x+!x)
 \end{lstlisting}
@@
 \centerline{\includegraphics[width=0.42\textwidth]{triangle-tetrahedron.png}}
-\caption*{Triangle with its tetrahedron complement $\star v_{123} + v_{123}$ in $\mb R^7$}
+\caption*{Triangle with its tetrahedron complement $v_{123} + \star v_{123}$ in $\mb R^7$}
 \end{figure}
@@
 \begin{definition}
-	The left $\lrcorner$ and right $\llcorner$ contraction are symmetrically defined
+	Skew left $\lrcorner$ and right $\llcorner$ contractions are symmetrically defined
 	$ \gen{\omega}_r\cdot\gen{\eta}_s = \begin{cases} \omega\llcorner\eta=\omega\vee\star\eta & r\geq s \\ \omega\lrcorner\eta=\eta\vee\star\omega & r\leq s \end{cases} $.
 	Note for $\omega,\eta$ of equal grade, $\omega\circledast\eta = \omega\odot\eta = \omega\cdot\eta = \omega\llcorner\eta = \omega\lrcorner\eta$ are all symmetric operations.
+In Julia, $\lrcorner$ is $<$ and $\llcorner$ is $>$.
 \end{definition}
@@
 \begin{theorem}[Clifford-Dirac-Laplacian]
-	The Dirac operator is $ \Delta^\frac12\omega = \mp\omega\ominus\nabla = \pm\nabla\wedge\omega \mp \omega\llcorner\nabla  = \pm d\omega\mp\partial\omega$ \cite{garling}.
+	The Dirac operator \cite{garling} is $ \Delta^\frac12\omega = \pm\nabla\ominus\omega = \pm\nabla\wedge\omega \pm \nabla\cdot\omega  = \pm d\omega\pm\partial\omega$.
 	\begin{align*}
@@
 	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\partial\Omega^{p+1}M}$.
-	Note: $\nabla\omega\neq\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
+	Note: $\nabla\omega=-\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
 \end{theorem}

### 2019-10-27 src/Grassmann.jl

@@ -97,11 +97,11 @@ macro mixedbasis_str(str)
     Expr(:block,bases,basis(V',vsn[2]),basis(V),bases.args[end])
 end
 
-@inline function lookup_basis(V::Manifold,v::Symbol)::Union{SBlade,Basis}
+@inline function lookup_basis(V::Manifold,v::Symbol)::Union{Simplex,Basis}
     p,b,w,z = DirectSum.indexparity(V,v)
     z && return g_zero(V)
     d = Basis{w}(b)
-    return p ? SBlade(-1,d) : d
+    return p ? Simplex(-1,d) : d
 end
 
 ## fundamentals
@@ -471,7 +471,7 @@ export skeleton, 𝒫, collapse, subcomplex, chain, path
 
 absym(t) = abs(t)
 absym(t::Basis) = t
-absym(t::T) where T<:TensorTerm{V,G} where {V,G} = SBlade{V,G}(absym(value(t)),basis(t))
+absym(t::T) where T<:TensorTerm{V,G} where {V,G} = Simplex{V,G}(absym(value(t)),basis(t))
 absym(t::SChain{T,V,G}) where {T,V,G} = SChain{T,V,G}(absym.(value(t)))
 absym(t::MChain{T,V,G}) where {T,V,G} = MChain{T,V,G}(absym.(value(t)))
 absym(t::MultiVector{T,V}) where {T,V} = MultiVector{T,V}(absym.(value(t)))
@@ -505,7 +505,7 @@ function skeleton(x::S,v::Val{T}=Val{true}()) where {S<:TensorMixed{Q,V} where Q
     ib = indexbasis(N,G)
     for k ∈ 1:binomial(N,G)
         if !iszero(x.v[k]) && (!T || count_ones(symmetricmask(V,ib[k],ib[k])[1])>0)
-            g += skeleton(SBlade{V,G}(x.v[k],getbasis(V,ib[k])),v)
+            g += skeleton(Simplex{V,G}(x.v[k],getbasis(V,ib[k])),v)
         end
     end
     return g
@@ -517,7 +517,7 @@ function skeleton(x::MultiVector{S,V} where S,v::Val{T}=Val{true}()) where {V,T}
         ib = indexbasis(N,i)
         for k ∈ 1:binomial(N,i)
[…]

### 2019-10-27 src/algebra.jl

@@ -186,7 +186,7 @@ for side ∈ (:left,:right)
             d = getbasis(V,complement(ndims(V),B,diffvars(V),$(c≠h ? 0 : :(hasinf(V)+hasorigin(V)))))
             mixedmode(V)<0 && throw(error("Complement for mixed tensors is undefined"))
             v = $(c≠h ? :($pn(V,B,value(d))) : :(value(d)))
-            typeof(V)<:Signature ? ($p(b) ? SBlade{V}(-v,d) : isone(v) ? d : SBlade{V}(v,d)) : SBlade{V}($p(b)*v,d)
+            typeof(V)<:Signature ? ($p(b) ? Simplex{V}(-v,d) : isone(v) ? d : Simplex{V}(v,d)) : Simplex{V}($p(b)*v,d)
         end
         for B ∈ MSB
             @eval $c(b::$B) = value(b)≠0 ? value(b)*$c(basis(b)) : g_zero(vectorspace(b))
@@ -219,10 +219,10 @@ export involute
 for r ∈ (:reverse,:involute,:conj)
     p = Symbol(:parity,r)
     @eval @pure function $r(b::Basis{V,G,B}) where {V,G,B}
-        $p(grade(V,B)) ? SBlade{V}(-value(b),b) : b
+        $p(grade(V,B)) ? Simplex{V}(-value(b),b) : b
     end
-    for Blade ∈ MSB
-        @eval $r(b::$Blade) = value(b) ≠ 0 ? value(b) * $r(basis(b)) : g_zero(vectorspace(b))
+    for implex ∈ MSB
+        @eval $r(b::$implex) = value(b) ≠ 0 ? value(b) * $r(basis(b)) : g_zero(vectorspace(b))
     end
 end
 
@@ -269,22 +269,22 @@ function mul(a::Basis{V},b::Basis{V},der=derive_mul(V,bits(a),bits(b),1,true)) w
     A,B,Q,Z = symmetricmask(V,bits(a),bits(b))
     pcc,bas,cc = (hasinf(V) && hasorigin(V)) ? conformal(A,B,V) : (false,A⊻B,false)
     d = getbasis(V,bas|Q)
-    out = (typeof(V)<:Signature || count_ones(A&B)==0) ? (parity(a,b)⊻pcc ? SBlade{V}(-1,d) : d) : SBlade{V}((pcc ? -1 : 1)*parityinner(A,B,V),d)
[…]

### 2019-10-27 src/composite.jl

@@ -6,8 +6,8 @@ export exph, log_fast, logh_fast
 
 ## exponential & logarithm function
 
-@inline Base.expm1(t::Basis{V,0}) where V = SBlade{V}(ℯ-1)
-@inline Base.expm1(t::T) where T<:TensorTerm{V,0} where V = SBlade{V}(expm1(value(t)))
+@inline Base.expm1(t::Basis{V,0}) where V = Simplex{V}(ℯ-1)
+@inline Base.expm1(t::T) where T<:TensorTerm{V,0} where V = Simplex{V}(expm1(value(t)))
 
 function Base.expm1(t::T) where T<:TensorAlgebra{V} where V
     S,term,f = t,(t^2)/2,norm(t)
@@ -27,7 +27,7 @@ end
 @eval function Base.expm1(b::MultiVector{T,V}) where {T,V}
     B = value(b)
     sb,nb = scalar(b),norm(B)
-    sb ≈ nb && (return SBlade{V}(expm1(sb)))
+    sb ≈ nb && (return Simplex{V}(expm1(sb)))
     $(insert_expr((:N,:t,:out,:bs,:bn),:mvec,:T,Float64)...)
     S = zeros(mvec(N,t))
     term = zeros(mvec(N,t))
@@ -126,7 +126,7 @@ end
 for (qrt,n) ∈ ((:sqrt,2),(:cbrt,3))
     @eval begin
         @inline Base.$qrt(t::Basis{V,0} where V) = t
-        @inline Base.$qrt(t::T) where T<:TensorTerm{V,0} where V = SBlade{V}($qrt(value(t)))
+        @inline Base.$qrt(t::T) where T<:TensorTerm{V,0} where V = Simplex{V}($qrt(value(t)))
         @inline function Base.$qrt(t::T) where T<:TensorAlgebra
             isscalar(t) ? $qrt(scalar(t)) : exp(log(t)/$n)
         end
@@ -135,7 +135,7 @@ end
 
 ## trigonometric
 
-@inline Base.cosh(t::T) where T<:TensorTerm{V,0} where V = SBlade{V}(cosh(value(t)))
+@inline Base.cosh(t::T) where T<:TensorTerm{V,0} where V = Simplex{V}(cosh(value(t)))
 
 function Base.cosh(t::T) where T<:TensorAlgebra{V} where V
     τ = t^2
@@ -156,7 +156,7 @@ end
 
[…]

### 2019-10-27 src/forms.jl

@@ -72,26 +72,26 @@ function (a::Basis{V,2,A})(b::Basis{V,1,B}) where {V,A,B}
     @inbounds t ? zero(V) : ((V[intlog(v)+1] ? -one(T) : one(T))*getbasis(V,ib[bi[1]]))
 end
 
-# Blade forms
+# implex forms
 
-for Blade ∈ MSB
+for implex ∈ MSB
     @eval begin
-        (a::$Blade)(b::T) where {T<:TensorAlgebra} = interform(a,b)
-        function (a::Basis{V,1,A})(b::$Blade{V,1,X,T} where X) where {V,A,T}
+        (a::$implex)(b::T) where {T<:TensorAlgebra} = interform(a,b)
+        function (a::Basis{V,1,A})(b::$implex{V,1,X,T} where X) where {V,A,T}
             x = bits(a)
             X = mixedmode(V)<0 ? x>>Int(ndims(V)/2) : x
             Y = bits(basis(b))
             Y∉(x,X) && (return zero(V))
             (V[intlog(Y)+1] ? -(b.v) : b.v) * Basis{V}()
         end
-        function (a::$Blade{V,1,X,T} where X)(b::Basis{V,1,B}) where {V,T,B}
+        function (a::$implex{V,1,X,T} where X)(b::Basis{V,1,B}) where {V,T,B}
             x = bits(basis(a))
             X = mixedmode(V)<0 ? x>>Int(ndims(V)/2) : x
             Y = bits(b)
             Y∉(x,X) && (return zero(V))
             (V[intlog(Y)+1] ? -(a.v) : a.v) * Basis{V}()
         end
-        function (a::$Blade{V,2,A,T})(b::Basis{V,1,B}) where {V,A,T,B}
+        function (a::$implex{V,2,A,T})(b::Basis{V,1,B}) where {V,A,T,B}
             C = mixedmode(V)
             (C ≥ 0) && throw(error("wrong basis"))
             $(insert_expr((:N,:M))...)
@@ -101,7 +101,7 @@ for Blade ∈ MSB
             t = bits(b)≠v
             @inbounds t ? zero(V) : ((V[intlog(v)+1] ? -(a.v) : a.v)*getbasis(V,ib[bi[1]]))
         end
-        function (a::$Basis{V,2,A})(b::$Blade{V,1,B,T}) where {V,A,B,T}
+        function (a::$Basis{V,2,A})(b::$implex{V,1,B,T}) where {V,A,B,T}
             C = mixedmode(V)
[…]

### 2019-10-27 src/multivectors.jl

@@ -92,50 +92,50 @@ end
 
 @inline show(io::IO, e::Basis) = DirectSum.printindices(io,vectorspace(e),bits(e))
 
-## S/MBlade{N}
+## S/MSimplex{N}
 
-const MSB = (:MBlade,:SBlade)
+const MSB = (:MSimplex,:Simplex)
 
-for Blade ∈ MSB
-    eval(Expr(:struct,Blade ≠ :SBlade,:($Blade{V,G,B,T} <: TensorTerm{V,G}),quote
+for implex ∈ MSB
+    eval(Expr(:struct,implex ≠ :Simplex,:($implex{V,G,B,T} <: TensorTerm{V,G}),quote
         v::T
-        $Blade{A,B,C,D}(t::E) where E<:D where {A,B,C,D} = new{A,B,C,D}(t)
-        $Blade{A,B,C,D}(t::E) where E<:TensorAlgebra{A} where {A,B,C,D} = new{A,B,C,D}(t)
+        $implex{A,B,C,D}(t::E) where E<:D where {A,B,C,D} = new{A,B,C,D}(t)
+        $implex{A,B,C,D}(t::E) where E<:TensorAlgebra{A} where {A,B,C,D} = new{A,B,C,D}(t)
     end))
 end
-for Blade ∈ MSB
+for implex ∈ MSB
     @eval begin
-        export $Blade
-        @pure $Blade(b::Basis{V,G}) where {V,G} = $Blade{V}(b)
-        @pure $Blade{V}(b::Basis{V,G}) where {V,G} = $Blade{V,G,b,Int}(1)
-        $Blade{V}(v::T) where {V,T} = $Blade{V,0,Basis{V}(),T}(v)
-        $Blade{V}(v::S) where S<:TensorTerm where V = v
-        $Blade{V,G,B}(v::T) where {V,G,B,T} = $Blade{V,G,B,T}(v)
-        $Blade(v,b::S) where S<:TensorTerm{V} where V = $Blade{V}(v,b)
-        $Blade{V}(v,b::S) where S<:TensorAlgebra where V = v*b
-        $Blade{V}(v,b::Basis{V,G}) where {V,G} = $Blade{V,G}(v,b)
-        $Blade{V}(v,b::Basis{W,G}) where {V,W,G} = $Blade{V,G}(v,b)
-        function $Blade{V,G}(v::T,b::Basis{V,G}) where {V,G,T}
[…]

### 2019-10-27 src/utilities.jl

@@ -160,7 +160,7 @@ Base.@pure promote_type(t...) = Base.promote_type(t...)
     assign_expr!(e,x,:M,:(Int(N/2)))
     assign_expr!(e,x,:t,vec≠:mvec ? :Any : :(promote_type($T,$S)))
     assign_expr!(e,x,:out,mv≠0 ? :(t=Any;convert(svec(N,Any),out)) : :(zeros($vec(N,t))))
-    assign_expr!(e,x,:mv,:(MBlade{V,0,getbasis(V,0),$(mv≠0 ? Any : :t)}(convert($(mv≠0 ? Any : :t),$mv))))
+    assign_expr!(e,x,:mv,:(MSimplex{V,0,getbasis(V,0),$(mv≠0 ? Any : :t)}(convert($(mv≠0 ? Any : :t),$mv))))
     assign_expr!(e,x,:r,:(binomsum(N,G)))
     assign_expr!(e,x,:bng,:(binomial(N,G)))
     assign_expr!(e,x,:bnl,:(binomial(N,L)))

### 2019-10-27 test/generictests.jl

@@ -18,7 +18,7 @@ using LinearAlgebra
     @test v1 ≈ v1
     @test v2 ≈ v2
     @test v12 ≈ v12
-    # S/MBlade
+    # simplex
     @test 2v ≈ 2v
     @test 2v1 ≈ 2v1
     # chain
@@ -36,7 +36,7 @@ using LinearAlgebra
     @test !(v ≈ v1+v12)
     @test !(v ≈ v+v1+v12)
 
-    # S/MBlade and others
+    # simplex and others
     @test !(2v ≈ v1)
     @test !(2v ≈ v12)
     @test !(2v ≈ v1+v2)
@@ -44,7 +44,7 @@ using LinearAlgebra
     @test !(2v ≈ v1+v12)
     @test !(2v ≈ v+v1+v12)
 
-    # Chain and others
+    # chain and others
     @test !(v1 + v2 ≈ v1)
     @test !(v1 + v2 ≈ v12)
     @test !(v1 + v2 ≈ v1+v)

### 2019-10-27 test/issuestests.jl

@@ -68,7 +68,7 @@ end
     
     a = v∅*basis(-v∞)
     @test a == -1 - v∞∅
-    @test SBlade{V}(-1, a) == -a
+    @test Simplex{V}(-1, a) == -a
 end
 
 @testset "Issue #22: Error in MultiVector constructor for Chains" begin

### 2019-10-29 src/Grassmann.jl
introduced vectorfield SubManifold interoperability for GeometryTypes.Point visualization

@@ -601,8 +601,10 @@ function __init__()
         Base.convert(::Type{GeometryTypes.Point},t::MChain{T,V,G}) where {T,V,G} = G == 1 ? GeometryTypes.Point(value(vector(t))) : GeometryTypes.Point(zeros(T,ndims(V))...)
         Base.convert(::Type{GeometryTypes.Point},t::SChain{T,V,G}) where {T,V,G} = G == 1 ? GeometryTypes.Point(value(vector(t))) : GeometryTypes.Point(zeros(T,ndims(V))...)
         GeometryTypes.Point(t::T) where T<:TensorAlgebra = convert(GeometryTypes.Point,t)
-        export points
-        points(f,V=identity;r=-2π:0.0001:2π) = [GeometryTypes.Point(V(Grassmann.vector(f(t)))) for t ∈ r]
+        @pure ptype(::Point{N,T} where N) where T = T
+        export points, vectorfield
+        points(f,V=identity;r=-2π:0.0001:2π) = [GeometryTypes.Point(V(vector(f(t)))) for t ∈ r]
+        vectorfield(t,V=vectorspace(t)) = p->GeometryTypes.Point(V(vector(SChain{ptype(p),V,1}(p.data)⊘t)))
     end
     #@require AbstractPlotting="537997a7-5e4e-5d89-9595-2241ea00577e" nothing
     #@require Makie="ee78f7c6-11fb-53f2-987a-cfe4a2b5a57a" nothing

### 2019-10-29 src/algebra.jl

@@ -526,14 +526,15 @@ export ⊘
 
 Sandwich product: ω⊘η = (~ω)⊖η⊖ω
 """
-⊘(x::TensorAlgebra{V},y::TensorAlgebra{V}) where V = (y)ˣ \ x * y
+⊘(x::TensorAlgebra{V},y::TensorAlgebra{V}) where V = inv(y) * x * involute(y)
+⊘(x::TensorAlgebra{V},y::TensorAlgebra{W}) where {V,W} = interop(⊘,x,y)
 
 """
     ⊘(ω::TensorAlgebra,η::TensorAlgebra)
 
 Sandwich product: ω>>>η = ω⊖η⊖(~ω)
 """
->>>(x::TensorAlgebra{V},y::TensorAlgebra{V}) where V = x * y / (x)ˣ
+>>>(x::TensorAlgebra{V},y::TensorAlgebra{V}) where V = x * y * ~x
 
 ## linear algebra
 

### 2019-10-31 paper/paper.tex
improved vectorfield and finalized JuliaCon paper, fixed #37

@@
 
-The nature of the geometric algebra code generation enables one to easily extend the abstract product operations to any specific number field type (including Leibniz differentials with \textit{Leibniz.jl} or symbolic coefficients with \textit{Reduce.jl}), by making use of Julia's type system.
+The nature of the geometric algebra code generation enables one to easily extend the abstract product operations to any specific number field type (including differential operators with \textit{Leibniz.jl} or symbolic coefficients with \textit{Reduce.jl}), by making use of Julia's type system.
 Mixed tensor products with their coefficients are constructed from these operations to work with bivector elements of Lie groups \cite{hestenes}\cite{shahshahani}.
@@
 For example, \verb`S"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
-It is also possible to specify an arbitrary \verb`DiagonalForm` having numerical values for the basis with \verb`D"0,0,0"` or \verb`D"-1,1,1,1"`, although the $\pm$ format provides better performance.
+It is also possible to specify an arbitrary \verb`DiagonalForm` having numerical values for the basis with degenracy \verb`D"1,1,1,0"`, although the $\pm$ format has a more compact representation.
 Further development will result in more metric types.
@@
 By itself, this package does not impose any specifications or structure on the \verb`TensorAlgebra{V}` subtypes and elements, aside from requiring $V$ to be a \verb`VectorBundle`.
-This means that different packages can create tensor types having a common underlying \verb`VectorBundle` structure.
+Hence all tensor types share a common underlying \verb`VectorBundle` structure.
+The macro \verb`@basis V` declares a local basis in Julia.
 
@@
 	The Grassmann anti-symmetric exterior basis is denoted by $v_{i_1\dots i_g}\in\Lambda_gV$ with its dual $w^{i_1\cdots i_g}\in\Lambda^gV$, while the Leibniz symmetric basis will be $\partial_{i_1}^{\mu_1}\dots\partial_{i_g}^{\mu_g}\in L_gV$ with $\epsilon_{i_1}^{\mu_1}\dots\epsilon_{i_g}^{\mu_g}\in L^gV$ dual elements.
+Let $\Lambda V = \bigoplus \Lambda^g V$.
 \end{definition}
-Higher-order composite tensor elements will be denoted by an oriented-multi-set $X$ %\in\text{OMSet}$
+A higher-order tensor element is an oriented-multi-set $X$ %\in\text{OMSet}$
 such that $w_X = \bigotimes_k w_{i_k}^{\otimes\mu_k}$ with $X = \plr{(i_1,\mu_1),\dots,(i_g,\mu_g)}$ and $|X|=\sum_k\mu_k$ is \verb`grade`,$\,$ \verb`order`.
 %There are two orientations and higher multiplicities result in zero for anti-symmetric tensors denoted by indices $\Lambda X\subseteq\Lambda V$, so the only interesting multiplicity is $\mu_k\equiv 1$.
-Anti-symmetric ndices $\Lambda X\subseteq\Lambda V$ have two orientations and higher multiplicities of them result in zero values, so the only interesting multiplicity is $\mu_k\equiv 1$.
-Symmetric tensors have an ambiguous multiplicity of nilpotence; decide that $\epsilon_k^{\mu+1}=0$, so $\mu_k\leq\mu$ can be non-trivial, negative, or unbounded.
+Anti-symmetric indices $\Lambda X\subseteq\Lambda V$ have two orientations and higher multiplicities are degenerate, hence the only relevant multiplicity is $\mu_k\equiv 1$.
+%Symmetric tensors have an ambiguous multiplicity of nilpotence; decide that $\epsilon_k^{\mu+1}=0$, so $\mu_k\leq\mu$ can be non-trivial, negative, or unbounded.
+The Leibniz-Taylor algebra \cite{taylor-algebra} is a quotient polynomial ring $LV\cong R[x_1,\dots,x_n]/\{\prod_{k=1}^{\mu+1} x_{p_k}\}$, so that $\epsilon_k^{\mu+1}=0$.
+% is $\mu$ truncated % (e.g.
+Jacobian and Hessian).
 
 The Grassmann \verb`Basis` elements $v_k\in\Lambda_1V$ and $w^k\in\Lambda^1V$ are linearly independent vector and covector elements of $V$, while the Leibniz \verb`Operator` elements $\partial_k\in L_1V$ are partial tangent derivations and $\epsilon_k(x)\in L^1V$ are dependent functions of the \verb`tangent` manifold.
-Higher \verb`grade` elements of $\Lambda V$ correspond to \verb`SubManifold` subspaces, while higher \verb`order` function elements of $LV$ become homogenous polynomials and Taylor series.
+Higher \verb`grade` elements of $\Lambda V$ correspond to \verb`SubManifold` spaces, while higher \verb`order` function elements of $LV$ become homogenous polynomials and Taylor series.
 
@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=0.42\textwidth]{triangle-tetrahedron.png}}
+\centerline{\includegraphics[width=0.42\textwidth]{img/triangle-tetrahedron.png}}
 \caption*{Triangle with its tetrahedron complement $v_{123} + \star v_{123}$ in $\mb R^7$}
@@
 \begin{theorem}[Clifford-Dirac-Laplacian]
-	The Dirac operator \cite{garling} is $ \Delta^\frac12\omega = \pm\nabla\ominus\omega = \pm\nabla\wedge\omega \pm \nabla\cdot\omega  = \pm d\omega\pm\partial\omega$.
+	The Dirac operator \cite{garling} is $ (\nabla^2)^\frac12\omega = \pm\nabla\ominus\omega = \pm\nabla\wedge\omega \pm \nabla\cdot\omega  = \pm d\omega\pm\partial\omega$.
 	\begin{align*}
-		\Delta\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \pm(\pm\omega\ominus\nabla)\ominus\nabla).
+		\nabla^2\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \mp(\mp\omega\ominus\nabla)\ominus\nabla).
 	\end{align*}
-	Elements $\omega$ are \textit{harmonic} if $\Delta\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, such that $\mc H^p M = \setc{\Delta\omega = 0}{\omega\in \Omega^pM}$.
+	Elements $\omega$ are \textit{harmonic} if $\nabla\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, such that $\mc H^p M = \setc{\nabla\omega = 0}{\omega\in \Omega^pM}$.
 	Hodge \cite{ivancevic}:
@@
 
+\iffalse
 \begin{lstlisting}[language = Julia]
@@
 \end{lstlisting}
+\fi
 
@@
 
-\begin{example}[\textit{using Leibniz $\bigoplus\,$Grassmann}]
-	\textbf{julia>} S"$\infty\emptyset\text{+++"}(\nabla)$\verb`^`$2 \,\,  \mapsto\, \, \Delta = (-2\partial_{\infty\emptyset} + \partial_1^2 + \partial_2^2 + \partial_3^2)\vec v $
-\end{example}
 For the null-basis, complement operations are different:
@@
 That variation of complement satisfies $\lambda I = \omega\,\wedge\,!\omega$ instead.
+\begin{example}%[\textit{using Leibniz $\bigoplus\,$Grassmann}]
+	S"$\infty\emptyset\text{+++"}(\nabla$\verb`^`$2) \,\,  \mapsto\, \, -2\partial_{\infty\emptyset} + \partial_1^2 + \partial_2^2 + \partial_3^2 $
+\end{example}
+Let $\nabla\in\Lambda^1V$, then $\omega = (\nabla\bs\nabla)\ominus\omega = \nabla\bs(d\omega + \partial\omega)$ where $\nabla\parallel\partial\omega$ and $\nabla\perp d\omega$.
+Let's reflect across the hyperplane $\star\nabla$,
+\begin{align*}
+	\nabla\bs (d\omega-\partial\omega) &= \nabla\bs(d\omega-\partial\omega)\ominus(\nabla\bs\nabla) \\
+									   &= -\nabla^2\bs(d\omega+\partial\omega)\ominus\nabla = -\nabla\bs\omega\ominus\nabla. %= \omega\oslash\nabla
+\end{align*}
+Hence, reflection by hyperplane $\star\nabla$ has isometry $\omega\oslash\nabla$ which for $\nabla = v_j$ is the map $\mb R^n \ra \mb R_1\times\cdots\times\conj{\mb R}_j\cdots\times\mb R_n$.
 
+\begin{theorem}[Cartan-Dieudonne]
+	Every isometry of $V\ra V$ is the composite of at most $k$ reflections across non-singular hyperplanes. Hence there exist vectors $\nabla_j$ such that
+	$$ (((\omega\oslash\nabla_1)\oslash\nabla_2)\oslash\cdots)\oslash\nabla_k = \omega\oslash(\nabla_1\ominus\nabla_2\ominus\dots\ominus\nabla_k) $$
+	for any isometry element of the orthogonal group $O(p,q)$.
+\end{theorem}
+Note that elements under transformations of this group preserve inner product relations.
+The even grade operators make up the rotational group, where each bivector isometry is a composition of two reflections \cite{artin} \cite{doran-hestenes-sommen-acker}.
+
+Consider the differential equation $ \partial_i\epsilon_j = \epsilon_j\oslash\omega$ with the solution $\epsilon_j(x) = \epsilon_j(0)\oslash e^{x_i\omega} $ where $\theta =2 x_i$ is the parameter of the Lie group.
+Then for a normalized $\omega$,
+$$ e^{\theta\omega} = \sum_k \frac{(\theta\omega)^{\ominus k}}{k!} = \begin{cases} \cosh\theta+\omega\sinh\theta, & \text{if } \omega^2 = 1, \\ \cos\theta + \omega\sin\theta, & \text{if } \omega^2=-1, \\ 1+\theta\omega, & \text{if } \omega^2=0.
+\end{cases} $$
+Note that $\nabla\oslash e^{\theta\omega/2} = \nabla \ominus e^{\theta\omega}$ is a double covering when using the complex numbers in the Euclidean plane.
 \begin{theorem}[Leibniz-Taylor series]
@@
 \end{theorem}
-The multivariate \textit{chain rule} is encoded into the geometric algebraic product when using mixed-symmetry.
-
-In the following examples, different possible discrete bivector topologies in a projective Riemann sphere setting are examined. 
-The figure below is based on the product topology of two rotation bivectors.
-When the standard $\mb R^4$ basis is used with projective geometric algebra, the one parameter Lie group can be visualized in the form of a torus in $\mb R^3$.
-When the fourth $v_\infty$ basis direction is rotated into the Minkowski plane, the double rotation becomes a helix with translational single rotation.
+The multivariate \textit{product rule} is encoded into the geometric algebraic product when using mixed-symmetry.
 
 \begin{lstlisting}[language = Julia]
-using Grassmann, Makie; @basis S"∞+++"
-f(t) = (↓(exp(π*t*((3/7)*v12+v∞3))>>>↑(v1+v2+v3)))
-lines(points(f,V(2,3,4)))
+using Grassmann, Makie
+basis"2" # Euclidean
+streamplot(vectorfield(v1*exp(π*v12/2)),-1.5..1.5,-1.5..1.5)
+streamplot(vectorfield(exp((π/2)*v12/2)),-1.5..1.5,-1.5..1.5)
+streamplot(vectorfield(exp((π/4)*v12/2)),-1.5..1.5,-1.5..1.5)
+streamplot(vectorfield(v1*exp((π/4)*v12/2)),-1.5..1.5,-1.5..1.5)
+@basis S"+-" # Hyperbolic
+streamplot(vectorfield(exp((π/8)*v12/2)),-1.5..1.5,-1.5..1.5)
+streamplot(vectorfield(v1*exp((π/4)*v12/2)),-1.5..1.5,-1.5..1.5)
 \end{lstlisting}
@@
 	\centering
-	\begin{subfigure}[b]{0.3\textwidth}
-		\includegraphics[width=\textwidth]{torus.png}
-		\caption{Projective double rotation orbit}
+	%\caption{Euclidean vector fields based on exponential operator:}
+	\begin{subfigure}[b]{0.23\textwidth}
+		\includegraphics[width=\textwidth]{img/plane-1.png}
+		\caption{$x\oslash e^{\pi v_{12}/2}$, $\mb R^2$}
 		%\label{fig:sample_figure}
@@
 	~
-	\begin{subfigure}[b]{0.15\textwidth}
-		\includegraphics[width=\textwidth]{helix.png}
-		\caption{Period translation}
+	\begin{subfigure}[b]{0.23\textwidth}
+		\includegraphics[width=\textwidth]{img/plane-2.png}
+		\caption{$ x\oslash e^{\frac\pi2 v_{12}/2}$, $\mb R^2$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.23\textwidth}
+		\includegraphics[width=\textwidth]{img/plane-3.png}
+		\caption{$x\oslash e^{\frac\pi4 v_{12}/2}$, $\mb R^2$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.23\textwidth}
+		\includegraphics[width=\textwidth]{img/plane-4.png}
+		\caption{$x\oslash(v_1\ominus e^{\frac\pi4 v_{12}/2})$, $\conj{\mb R}\oplus\mb R$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.23\textwidth}
+		\includegraphics[width=\textwidth]{img/plane-5.png}
+		\caption{$x\oslash e^{\frac\pi8 v_{12}/2}$, $\mb R\oplus\mb R'$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.23\textwidth}
+		\includegraphics[width=\textwidth]{img/plane-6.png}
+		\caption{$x\oslash(v_1\ominus e^{\frac\pi4 v_{12}/2})$, $\conj{\mb R}\oplus\mb R'$}
 		%\label{fig:sample_figure}
@@
 
+As a result of Grassmann's exterior \& interior products, the Hodge-DeRahm chain complex from cohomology theory is
+\begin{align*}
+	0 &\os d{\us\partial\rightleftarrows} \Omega^0(M) \os d{\us\partial\rightleftarrows} \Omega^1(M) \os d{\us\partial\leftrightarrows} \cdots \os d{\us\partial\rightleftarrows} \Omega^n(M) \os d{\us\partial\rightleftarrows} 0,
+\end{align*}
+having dimensional equivalence brought by the Grassmann-Poincare-Hodge complement duality,
+\begin{align*}
+	\mc H^{n-p}M &\cong \frac{\ker(d\Omega^{n-p}M)}{\im{d\Omega^{n-p-1}M}}, & \dim\mc H^pM &= \dim\frac{\ker(\partial\Omega^pM)}{\im{\partial\Omega^{p+1}M}}
+\end{align*}
+The rank of the grade $p$ boundary incidence operator is
+$$ \text{rank}\gen{\partial\gen{M}_{p+1}}_p = \min\set{\dim\gen{\partial\gen{M}_{p+1}}_p,\dim\gen{M}_{p+1}} $$
+Invariant topological information can be computed using the rank of homology groups, where $b_p(M)=\dim\mc H^pM$ are
+$$ b_p(M) = \dim\gen{M}_{p+1} - \text{rank}\gen{\partial\gen{M}_{p+1}}_p - \text{rank}\gen{\partial\gen{M}_{p+2}}_{p+1} $$
+Betti numbers with Euler characteristic $\chi(M) = \sum_p (-1)^pb_p$.
+
+Let's obtain the full \verb`skeleton` of a simplical complex $\Delta(\omega)=\mc P(\omega)\bs\Lambda^0(V)$ from the power set $\mc P(\omega)$ of all vertices with each \verb`subcomplex` $\Delta(\partial(\omega))$ contained in the edge graph:
+$$ \Delta(\omega) =  \sum_{g=1}^n\sum_{k=1}^{n\choose g}\plr{\text{abs}\gen{\omega}_{g,k} + \Delta\plr{\text{abs}\,\partial\gen{\omega}_{g,k}}}. $$
+\begin{example}
+	[Topology] Compute the value $\chi(\Delta(\omega))=1$ and $\chi(\Delta(\partial(\omega))) = \, ?$ for any \verb`Simplex` $\omega$.
+As an exercise, also compute the corresponding \verb`betti` numbers..
+\end{example}
+
+In Fig. 4, different possible discrete bivector topologies in a projective Riemann sphere setting are examined. 
+The figures are based on the product topology of two rotation bivectors.
+When the Euclidean $\mb R^4$ basis is combined with projective geometric algebra, resulting one parameter Lie groups can be visualized in the form of a torus in $\mb R^3$. 
+When the fourth $v_\infty$ basis direction is rotated into the Minkowski plane, the double rotation becomes a helix with translational single rotation.
+In examples (b)$\sim$(c) the bivector is modulated.
+
 \begin{figure}[t]
 	\centering
-	\caption{Different variations of bivectors in $\mb R^4$ discrete topology.}
-	\begin{subfigure}[b]{0.14\textwidth}
-		\includegraphics[width=\textwidth]{product.png}
-		\caption{v_{12}+v_{34}}
+	\caption{Variations of sub-manifold vector field mappings in $\mb R^4$.}
+	\begin{subfigure}[b]{0.23\textwidth}
+		\includegraphics[width=\textwidth]{img/orb.png}
+		\caption{$x\oslash e^{\frac\pi4(v_{12}+v_{\infty3})}$}
 		%\label{fig:sample_figure}
@@
 	~
-	\begin{subfigure}[b]{0.14\textwidth}
-		\includegraphics[width=\textwidth]{strange.png}
-		\caption{v_{14}+v_{24}+v_{34}}
+	\begin{subfigure}[b]{0.23\textwidth}
+		\includegraphics[width=\textwidth]{img/wave.png}
+		\caption{$V_{\infty12}\ra V_{123}$}
 		%\label{fig:sample_figure}
 	\end{subfigure}
-	~
-	\begin{subfigure}[b]{0.14\textwidth}
-		\includegraphics[width=\textwidth]{toroid-modulation.png}
-		\caption{v_{124}+v_{34}}
-		%\label{fig:sample_figure}
-	\end{subfigure}
-\end{figure}
-
-\begin{figure}[t]
-\centerline{\includegraphics[width=0.45\textwidth]{orbit-3.png}}
-%\caption*{$\downarrow(e^{t(v_{12}+v_\infty(sin(3t)3v_1+cos(2t)7v_2-sin(5t)4v_3)/2)}\obackslash\uparrow(v_1+v_2-v_3))$}
-\caption{Modulated bivector group on Riemann sphere S"∞+++"}
 \end{figure}
@@
 %This will enable the usage of many different types of \verb`TensorAlgebra` along with various \verb`VectorBundle` parameters and interoperability for a wide range of scientific and research applications.
-All of the types and operations in this paper are implemented using only a few thousand lines of code with Julia's type polymorphism code generation, although the mixed-symmetry interaction of \verb`Leibniz` and \verb`Grassmann` is still a work in progress.
-The goal is to algebraically define operator actions on groups of \textit{Leibniz.jl} differential function elements. 
-One way is to use \textit{Reduce.jl} for differentiation and \textit{SyntaxTree.jl} to obtain optimal symbolic polynomial forms \cite{optim-poly}.
-
-Thus, these packages provide general rotational algebras and Lie bivector groups with a full trigonometric suite enabled by $ e^{A} = \sum_n \frac{A^n}{n!} $.
+All of the types and operations in this paper are implemented using only a few thousand lines of code with Julia's type polymorphism code generation, with the mixed-symmetry interaction of \verb`Leibniz` and \verb`Grassmann` available for research.
+%The goal is to algebraically define operator actions on groups of \textit{Leibniz.jl} differential function elements. 
+%One way is to use \textit{Reduce.jl} for differentiation and \textit{SyntaxTree.jl} to obtain optimal symbolic polynomial forms \cite{optim-poly}.
+Thus, computations involving fully general rotational algebras and Lie bivector groups are possible with a full trigonometric suite. % enabled by $ e^{A} = \sum_n \frac{A^n}{n!} $.
 Conformal geometric algebra is possible with the Minkowski plane $v_{\infty\emptyset}$, based on the null-basis.
-In general, multivalued quantum logic is enabled by the $\wedge,\vee,\star$ Grassmann-Hodge dual lattice.
+In general, multivalued quantum logic is enabled by the $\wedge,\vee,\star$ Grassmann lattice.
 Mixed-symmetry algebra with \textit{Leibniz.jl} and \textit{Grassmann.jl}, having the geometric algebraic product chain rule, yields automatic differentiation and Hodge-DeRahm co/homology  as unveiled by Grassmann.
-\begin{align*}
-	0 &\os d{\us\partial\rightleftarrows} \Omega^0(M) \os d{\us\partial\rightleftarrows} \Omega^1(M) \os d{\us\partial\leftrightarrows} \cdots \os d{\us\partial\rightleftarrows} \Omega^n(M) \os d{\us\partial\rightleftarrows} 0,
-\end{align*}
-\begin{align*}
-	\mc H^pM &\cong \frac{\ker(d\Omega^pM)}{\im{d\Omega^{p-1}M}}, & \dim\mc H^pM &= \dim\frac{\ker(\delta\Omega^pM)}{\im{\delta\Omega^{p+1}M}}
-\end{align*}
-In conclusion, the Dirac-Clifford product yields generalized Hodge-Laplacian and $b_p=\dim\mc H^pM$ are the Betti numbers with Euler characteristic $\chi = \sum_p (-1)^pb_p$.
-There will be a more detailed follow-up paper.
+Most importantly, the Dirac-Clifford product yields generalized Hodge-Laplacian and the Betti numbers with Euler characteristic \verb`χ`.
 
@@
 \begin{figure}[t]
-\centerline{\includegraphics[width=0.42\textwidth]{orbit-2.png}}
-\caption*{$\downarrow(e^{tv_\infty(sin(3t)3v_1+cos(2t)7v_2-sin(5t)4v_3)/2}\obackslash\uparrow(v_1+v_2-v_3))$}
+	\centering
+	\caption{Different variations of bivectors in $\mb R^4$ discrete topology.}
+	\begin{subfigure}[b]{0.14\textwidth}
+		\includegraphics[width=\textwidth]{img/graph-1.png}
+		\caption{$v_{12}+v_{34}$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.14\textwidth}
+		\includegraphics[width=\textwidth]{img/graph-2.png}
+		\caption{$v_{14}+v_{24}+v_{34}$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.14\textwidth}
+		\includegraphics[width=\textwidth]{img/graph-3.png}
+		\caption{$\partial v_{124}+v_{34}$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
 \end{figure}
 
-\iffalse
-\begin{figure}[t]
-\centerline{\includegraphics[width=0.42\textwidth]{orbit-1.png}}
-\caption{Modulated bivector group on Riemann sphere S"∞+++"}
+\begin{figure}[ht]
+	\centering
+	%\caption{Doubly-periodic flow from independent bivectors:}
+	\begin{subfigure}[b]{0.3\textwidth}
+		\includegraphics[width=\textwidth]{img/torus.png}
+		\caption{Doubly periodic flow (independent)}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.15\textwidth}
+		\includegraphics[width=\textwidth]{img/helix.png}
+		\caption*{(a) Period translation}
+		%\label{fig:sample_figure}
+	\end{subfigure}
 \end{figure}
-\fi
 
-\begin{lstlisting}[language = Julia]
-skeleton(v123)
-betti(ans)
-subcomplex(v123)
-\end{lstlisting}
+\begin{figure}[ht]
+	\begin{subfigure}[b]{0.16\textwidth}
+		\includegraphics[width=\textwidth]{img/orbit-2.png}
+		%\caption{$x\oslash e^{\pi v_{12}/2}$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{0.28\textwidth}
+		\includegraphics[width=\textwidth]{img/orbit-4.png}
+		%\caption{$ x\oslash e^{\frac\pi2 v_{12}/2}$}
+		%\label{fig:sample_figure}
+	\end{subfigure}
+	\caption*{(b)$\sim$(c) $\downarrow(e^{tv_\infty(sin(3t)3v_1+cos(2t)7v_2-sin(5t)4v_3)/2}\obackslash\uparrow(v_1+v_2-v_3))$}
+\end{figure}
 

### 2019-10-31 src/Grassmann.jl

@@ -428,17 +428,15 @@ end
 ∂(ω::T) where T<:TensorAlgebra{V} where V = ω⋅V(∇)
 d(ω::T) where T<:TensorAlgebra{V} where V = V(∇)∧ω
 
-@pure ℙ(V) = ((i,o)=(hasinf(V),hasorigin(V));i+o==2 ? V : (i+o==0 ? S"∞∅"⊕V : V))
-
 function ↑(ω::T) where T<:TensorAlgebra{V} where V
-    PV = ℙ(V)
-    G = Λ(PV)
-    return if hasinf(PV) && hasorigin(PV)
+    !(hasinf(V)||hasorigin(V)) && (return ω)
+    G = Λ(V)
+    return if hasinf(V) && hasorigin(V)
         ((G.v∞/2)*ω^2+G.v∅)+ω
     else
         ω2 = ω^2
         iω2 = inv(ω2+1)
-        (hasinf(PV) ? G.v∞ : G.v∅)*(ω2-1)*iω2 + 2*iω2*ω
+        (hasinf(V) ? G.v∞ : G.v∅)*(ω2-1)*iω2 + 2*iω2*ω
     end
 end
 function ↑(ω,b)
@@ -453,12 +451,12 @@ function ↑(ω,p,m)
 end
 
 function ↓(ω::T) where T<:TensorAlgebra{V} where V
-    PV = ℙ(V)
-    G = Λ(PV)
-    return if hasinf(PV) && hasorigin(PV)
+    !(hasinf(V)||hasorigin(V)) && (return ω)
+    G = Λ(V)
+    return if hasinf(V) && hasorigin(V)
         inv(G.v∞∅)*(G.v∞∅∧ω)/(-ω⋅G.v∞)
     else
-        b = hasinf(PV) ? G.v∞ : G.v∅
+        b = hasinf(V) ? G.v∞ : G.v∅
         ((ω∧b)*b)/(1-b⋅ω)
     end
 end
@@ -494,8 +492,9 @@ function chain(t::S,::Val{T}=Val{true}()) where S<:TensorTerm{V} where {V,T}
 end
 path(t) = chain(t,Val{false}())
 
-𝒫(t::T) where T<:TensorAlgebra = skeleton(t,Val{false}())
-subcomplex(x::S,v=Val{true}()) where S<:TensorAlgebra = skeleton(absym(∂(x)),v)
[…]

### 2019-10-31 src/algebra.jl

@@ -526,7 +526,7 @@ export ⊘
 
 Sandwich product: ω⊘η = (~ω)⊖η⊖ω
 """
-⊘(x::TensorAlgebra{V},y::TensorAlgebra{V}) where V = inv(y) * x * involute(y)
+⊘(x::TensorAlgebra{V},y::TensorAlgebra{V}) where V = diffvars(V)≠0 ? (~y)*x*involute(y) : inv(y)*x*involute(y)
 ⊘(x::TensorAlgebra{V},y::TensorAlgebra{W}) where {V,W} = interop(⊘,x,y)
 
 """

### 2019-10-31 src/multivectors.jl

@@ -671,6 +671,8 @@ end
 #@pure supblade(N,S,B) = bladeindex(N,expandbits(N,S,B))
 #@pure supmulti(N,S,B) = basisindex(N,expandbits(N,S,B))
 
+@pure subvert(::SubManifold{M,V,S} where {M,V}) where S = S
+
 @pure function mixed(V::M,ibk::UInt) where M<:Manifold
     N,D,VC = ndims(V),diffvars(V),mixedmode(V)
     return if D≠0
@@ -687,10 +689,11 @@ end
     WC,VC = mixedmode(W),mixedmode(V)
     #if ((C1≠C2)&&(C1≥0)&&(C2≥0))
     #    return V0
+    B = typeof(V)<:SubManifold ? expandbits(ndims(W),subvert(V),bits(b)) : bits(b)
     if WC<0 && VC≥0
-        getbasis(W,mixed(V,bits(b)))
+        getbasis(W,mixed(V,B))
     elseif WC≥0 && VC≥0
-        getbasis(W,bits(b))
+        getbasis(W,B)
     else
         throw(error("arbitrary Manifold intersection not yet implemented."))
     end
@@ -717,10 +720,11 @@ for Chain ∈ MSC
             ib = indexbasis(N,G)
             for k ∈ 1:length(ib)
                 @inbounds if b[k] ≠ 0
+                    @inbounds B = typeof(V)<:SubManifold ? expandbits(M,subvert(V),ib[k]) : ib[k]
                     if WC<0 && VC≥0
-                        @inbounds setblade!(out,b[k],mixed(V,ib[k]),Dimension{M}())
+                        @inbounds setblade!(out,b[k],mixed(V,B),Dimension{M}())
                     elseif WC≥0 && VC≥0
-                        @inbounds setblade!(out,b[k],ib[k],Dimension{M}())
+                        @inbounds setblade!(out,b[k],B,Dimension{M}())
                     else
                         throw(error("arbitrary Manifold intersection not yet implemented."))
                     end
@@ -737,7 +741,7 @@ for Chain ∈ MSC
             for k ∈ 1:length(ib)
                 @inbounds if b[k] ≠ 0
                     @inbounds if count_ones(ib[k]&S) == G
-                        @inbounds setblade!(out,b[k],lowerbits(N,S,ib[k]),Dimension{M}())
+                        @inbounds setblade!(out,b[k],lowerbits(M,S,ib[k]),Dimension{M}())
                     end
[…]

### 2019-10-31 src/utilities.jl

@@ -244,7 +244,7 @@ const lowerbits_extra = Dict{UInt,Dict{UInt,UInt}}[]
     end
 end
 
-#=const expandbits_cache = Dict{UInt,Dict{UInt,UInt}}[]
+const expandbits_cache = Dict{UInt,Dict{UInt,UInt}}[]
 @pure expandbits_calc(N,S,B) = bit2int(indexbits(N,indices(S,N)[indices(B,N)]))
 @pure function expandbits(N,S,B)
     for k ∈ length(expandbits_cache)+1:N
@@ -253,6 +253,30 @@ end
     @inbounds !haskey(expandbits_cache[N],S) && push!(expandbits_cache[N],S=>Dict{UInt,UInt}())
     @inbounds !haskey(expandbits_cache[N][S],B) && push!(expandbits_cache[N][S],B=>expandbits_calc(N,S,B))
     @inbounds expandbits_cache[N][S][B]
+end
+
+#=const expandbits_cache = Vector{Vector{UInt}}[]
+const expandbits_extra = Dict{UInt,Dict{UInt,UInt}}[]
+@pure expandbits_calc(N,S,B,k=indices(S,N)) = bit2int(indexbits(N,k[indices(B,N)]))
+@pure function expandbits(N,S,B)
+    if N>cache_limit
+        n = N-cache_limit
+        for k ∈ length(expandbits_extra)+1:n
+            push!(expandbits_extra,Dict{UInt,Dict{UInt,UInt}}())
+        end
+        @inbounds !haskey(expandbits_extra[n],S) && push!(expandbits_extra[n],S=>Dict{UInt,UInt}())
+        @inbounds !haskey(expandbits_extra[n][S],B) && push!(expandbits_extra[n][S],B=>expandbits_calc(N,S,B))
+        @inbounds expandbits_extra[n][S][B]
+    else
+        for k ∈ length(expandbits_cache)+1:min(N,cache_limit)
+            push!(expandbits_cache,Vector{Int}[])
+        end
+        for s ∈ length(expandbits_cache[N])+1:S
+            k = indices(S,N)
+            push!(expandbits_cache[N],[expandbits_calc(N,s,d,k) for d ∈ UInt(0):UInt(1)<<(N+1)-1])
+        end
+        @inbounds expandbits_cache[N][S][B+1]
+    end
 end=#
 
 

### 2019-11-01 paper/paper.tex
revised Project.toml, Makie.jl links, and revised paper grammar

@@
 \begin{figure}[ht]
-%\centerline{\includegraphics[width=4cm]{grassmann.png}}
-\centerline{\includegraphics[width=4cm]{../docs/src/assets/logo.png}}
+\centerline{\includegraphics[width=4cm]{img/grassmann.png}}
+%\centerline{\includegraphics[width=4cm]{../docs/src/assets/logo.png}}
 \caption*{github.com/chakravala/Grassmann.jl}
@@
 	The kernelized operations are built up from composite sparse tensor products and Hodge duality, with high dimensional support for up to 62 indices using staged caching and precompilation.
-Code generation enables concise with highly extensible definitions.
+Code generation enables concise yet highly extensible definitions.
 	\textit{DirectSum.jl}
@@
 \begin{example}
-	[Vorticity of vector-field]
+	[Vorticity curl of vector-field]
 	$\star d(dx_1+dx_2+dx_3) = (∂_2 -∂_3)dx_1 + (∂_3 -∂_1)dx_2 + (∂_1 -∂_2)dx_3$.
@@
 \end{align*}
-That variation of complement satisfies $\lambda I = \omega\,\wedge\,!\omega$ instead.
+For that variation of complement, $||\omega||^2 I = \omega\,\wedge\,!\omega$ holds.
 \begin{example}%[\textit{using Leibniz $\bigoplus\,$Grassmann}]
@@
 \textbf{Acknowledgements}: Many thanks for discussions with Steven De Keninck, Utensil Song, Alexander Arsenovic, Hugo Hadfield, Karl Wessel; the helpful Julia community (e.g.
-Jameson Nash, Stefan Karpinski, Jeff Bezanson, Kristoffer Carlsson, Petr Krysl, Nathan Smith, etc); and thanks for support from my family.
+Jameson Nash, Stefan Karpinski, Jeff Bezanson, Kristoffer Carlsson, Petr Krysl, Nathan Smith, Hongying Li, etc); and thanks for support from my family.
 

### 2019-11-04 paper/paper.tex
created projective unsplitter norm and tidelift enterprise referral

@@
 \begin{proof}
-	$\partial\omega = \omega\cdot\nabla = \star(\star\omega\wedge\star^2\nabla) = (-1)^n(-1)^{nk}\star d\star\omega$.
+	$\partial\omega = \omega\cdot\nabla = \star\inv(\star\omega\wedge\star^2\nabla) = (-1)^n(-1)^{nk}\star d\star\omega$.
 
 	Then  substitute this into $\int_M \omega\wedge(-1)^{mk+m+1}\star\star d\star\eta = (-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}\int_M\omega\wedge d\star\eta$,
-	with identity $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and
+	apply the identity $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and
 	$ (-1)^k\int_M\omega\wedge d\star\eta = \int_M d(\omega\wedge\star\eta) - (-1)^{k-1}\omega\wedge d\star\eta = \int_M d\omega\wedge\star\eta$.
@@
 basis"2" # Euclidean
-streamplot(vectorfield(v1*exp(π*v12/2)),-1.5..1.5,-1.5..1.5)
+streamplot(vectorfield(exp(π*v12/2)),-1.5..1.5,-1.5..1.5)
 streamplot(vectorfield(exp((π/2)*v12/2)),-1.5..1.5,-1.5..1.5)
@@
 \begin{align*}
-	\mc H^{n-p}M &\cong \frac{\ker(d\Omega^{n-p}M)}{\im{d\Omega^{n-p-1}M}}, & \dim\mc H^pM &= \dim\frac{\ker(\partial\Omega^pM)}{\im{\partial\Omega^{p+1}M}}
+	\mc H^{n-p}M &\cong \frac{\ker(d\Omega^{n-p}M)}{\im{d\Omega^{n-p+1}M}}, & \dim\mc H^pM &= \dim\frac{\ker(\partial\Omega^pM)}{\im{\partial\Omega^{p+1}M}}
 \end{align*}
@@
 The figures are based on the product topology of two rotation bivectors.
-When the Euclidean $\mb R^4$ basis is combined with projective geometric algebra, resulting one parameter Lie groups can be visualized in the form of a torus in $\mb R^3$. 
+When the Euclidean $\mb R^4$ basis is combined with projective geometric algebra, resulting one parameter Lie groups can be visualized as a fibration of a torus in $\mb R^3$. 
 When the fourth $v_\infty$ basis direction is rotated into the Minkowski plane, the double rotation becomes a helix with translational single rotation.

### 2019-11-04 src/Grassmann.jl

@@ -3,9 +3,9 @@ module Grassmann
 #   This file is part of Grassmann.jl. It is licensed under the GPL license
 #   Grassmann Copyright (C) 2019 Michael Reed
 
-using Combinatorics, StaticArrays, Requires
+using Combinatorics, StaticArrays, SparseArrays
 using ComputedFieldTypes, AbstractLattices
-using DirectSum, AbstractTensors
+using DirectSum, AbstractTensors, Requires
 
 export vectorspace, ⊕, ℝ, @V_str, @S_str, @D_str, Signature,DiagonalForm,SubManifold, value
 import DirectSum: hasinf, hasorigin, mixedmode, dual, value, vectorspace, V0, ⊕, pre, vsn

### 2019-11-04 src/multivectors.jl

@@ -828,6 +828,61 @@ Base.copysign(x::Simplex{V,G,B,T},y::Simplex{V,G,B,T}) where {V,G,B,T} = Simplex
     return A
 end
 
+# Euclidean norm (unsplitter)
+
+unsplitstart(g) = 1|((UInt(1)<<(g-1)-1)<<2)
+unsplitend(g) = (UInt(1)<<g-1)<<2
+
+const unsplitter_cache = SparseMatrixCSC{Float64,Int64}[]
+@pure unsplitter_calc(n) = (n2=Int(n/2);sparse(1:n2,1:n2,1,n,n)+sparse(1:n2,(n2+1):n,-1/2,n,n)+sparse((n2+1):n,(n2+1):n,1/2,n,n)+sparse((n2+1):n,1:n2,1,n,n))
+@pure function unsplitter(n::Int)
+    n2 = Int(n/2)
+    for k ∈ length(unsplitter_cache)+1:n2
+        push!(unsplitter_cache,unsplitter_calc(2k))
+    end
+    @inbounds unsplitter_cache[n2]
+end
+@pure unsplitter(n,g) = unsplitter(bladeindex(n,unsplitend(g))-bladeindex(n,unsplitstart(g)))
+
+for implex ∈ (MSB...,Basis)
+    @eval begin
+        #norm(t::$implex) = norm(unsplitval(t))
+        function unsplitvalue(a::$implex{V,G}) where {V,G}
+            !(hasinf(V) && hasorigin(V)) && (return value(a))
+            #T = valuetype(a)
+            #$(insert_expr((:N,:t,:out),:mvec,:T,:(typeof((one(T)/(2one(T))))))...)
+            #out = copy(value(a,t))
+            return unsplitvalue(MChain(a))
+        end
+    end
+end
+
+for Chain ∈ MSC
+    @eval begin
+        #norm(t::$Chain) = norm(unsplitval(t))
+        function unsplitvalue(a::$Chain{T,V,G}) where {T,V,G}
+            !(hasinf(V) && hasorigin(V)) && (return value(a))
+            $(insert_expr((:N,:t,:out),:mvec,:T,:(typeof((one(T)/(2one(T))))))...)
+            out = copy(value(a,mvec(N,G,t)))
+            bi = bladeindex(N,unsplitstart(G)):bladeindex(N,unsplitend(G))-1
+            out[bi] = unsplitter(N,G)*out[bi]
+            return out
+        end
+    end
+end
+
+@eval begin
[…]

### 2019-11-14 src/algebra.jl
created hybrid generated function for MultiVector arithmetic

@@ -19,7 +19,6 @@ const ExprField = Union{Expr,Symbol}
 
 ## mutating operations
 
-
 const Sym = :DirectSum
 const SymField = Any
 
@@ -77,6 +76,66 @@ end
     end
 end
 
+function derive_pre(V,A,B,a,b,p)
+    if !(diffvars(V)≠0 && mixedmode(V)<0)
+        return Expr(:call,p,a,b)
+    else
+        return :(derive_post($V,$(Val{A}()),$(Val{B}()),a,b,$p))
+    end
+end
+
+function derive_post(V,::Val{A},::Val{B},v,x::Bool) where {A,B}
+    if !(diffvars(V)≠0 && mixedmode(V)<0)
+        return v
+    else
+        sa,sb = symmetricsplit(V,A),symmetricsplit(V,B)
+        ca,cb = count_ones(sa[2]),count_ones(sb[2])
+        return if (ca == cb == 0) || ((ca ≠ 0) && (cb ≠ 0))
+            v
+        else
+            prev = ca == 0 ? (x ? one(typeof(v)) : v) : (x ? v : one(typeof(v)))
+            for k ∈ DirectSum.indexsplit((ca==0 ? sa : sb)[1],ndims(V))
+                prev = derive(prev,getbasis(V,k))
+            end
+            prev
+        end
+    end
+end
+
+function derive_post(V,::Val{A},::Val{B},a,b,*) where {A,B}
+    if !(diffvars(V)≠0 && mixedmode(V)<0)
+        return a*b
+    else
+        sa,sb = symmetricsplit(V,A),symmetricsplit(V,B)
+        ca,cb = count_ones(sa[2]),count_ones(sb[2])
+        α,β = if (ca == cb == 0) || ((ca ≠ 0) && (cb ≠ 0))
+            a,b
+        else
+            prev = ca == 0 ? (a,b) : (b,a)
+            for k ∈ DirectSum.indexsplit((ca==0 ? sa : sb)[1],ndims(V))
+                prev = derive(prev[2],getbasis(V,k),prev[1],true)
+            end
+            #base = getbasis(V,0)
+            while typeof(prev[1]) <: TensorTerm
+                basi = basis(prev[1])
+                #base *= basi
+                inds = DirectSum.indexsplit(bits(basi),ndims(V))
+                prev = (value(prev[1]),prev[2])
+                for k ∈ inds
+                    prev = derive(prev[2],getbasis(V,k),prev[1],true)
[…]

### 2019-11-14 src/multivectors.jl

@@ -250,7 +250,6 @@ end
 MultiVector{T,V}(v::MArray{Tuple{E},S,1,E}) where S<:T where {T,V,E} = MultiVector{S,V,E}(v)
 MultiVector{T,V}(v::SArray{Tuple{E},S,1,E}) where S<:T where {T,V,E} = MultiVector{S,V,E}(v)
 
-
 function getindex(m::MultiVector{T,V},i::Int) where {T,V}
     N = ndims(V)
     0 <= i <= N || throw(BoundsError(m, i))

### 2019-11-14 src/algebra.jl
improved StaticArrays performance of MultiVector inbounds

@@ -1046,7 +1046,7 @@ function generate_products(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj
                 return MultiVector{t,V}(out)
             end
             @generated function $op(a::MultiVector{T,V},b::MultiVector{S,V}) where {V,T<:$Field,S<:$Field}
-                if ndims(V)>4
+                if ndims(V)>5
                     return quote
                         $(insert_expr((:N,:t,:out,:bs,:bn,:μ),$(QuoteNode(VEC)))...)
                         for g ∈ 1:N+1
@@ -1072,17 +1072,17 @@ function generate_products(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj
                     for g ∈ 1:N+1
                         Y = indexbasis(N,g-1)
                         @inbounds for i ∈ 1:bn[g]
-                            @inbounds val = :(b.v[$(bs[g]+i)])
+                            @inbounds val = :(@inbounds b.v[$(bs[g]+i)])
                             for G ∈ 1:N+1
                                 @inbounds R = bs[G]
                                 X = indexbasis(N,G-1)
                                 @inbounds for j ∈ 1:bn[G]
-                                    @inbounds $preproduct!(V,out,X[j],Y[i],derive_pre(V,X[j],Y[i],:(a.v[$(R+j)]),val,$(QuoteNode(MUL))))
+                                    @inbounds $preproduct!(V,out,X[j],Y[i],derive_pre(V,X[j],Y[i],:(@inbounds a.v[$(R+j)]),val,$(QuoteNode(MUL))))
                                 end
                             end
                         end
                     end
-                    return :(MultiVector{V}($(Expr(:vect,out...))))
+                    return :(MultiVector{V}($(Expr(:call,:SVector,out...))))
                 end
             end
         end

### 2019-11-14 src/multivectors.jl

@@ -245,9 +245,9 @@ end
 ## MultiVector{T,N}
 
 struct MultiVector{T,V,E} <: TensorMixed{T,V}
-    v::Union{MArray{Tuple{E},T,1,E},SArray{Tuple{E},T,1,E}}
+    v::SArray{Tuple{E},T,1,E}
 end
-MultiVector{T,V}(v::MArray{Tuple{E},S,1,E}) where S<:T where {T,V,E} = MultiVector{S,V,E}(v)
+MultiVector{T,V}(v::MArray{Tuple{E},S,1,E}) where S<:T where {T,V,E} = MultiVector{S,V,E}(SVector(v))
 MultiVector{T,V}(v::SArray{Tuple{E},S,1,E}) where S<:T where {T,V,E} = MultiVector{S,V,E}(v)
 
 function getindex(m::MultiVector{T,V},i::Int) where {T,V}

### 2019-11-14 src/algebra.jl
significant performance improvements for low-dimensional subalgebras

@@ -76,60 +76,60 @@ end
     end
 end
 
+function derive_pre(V,A,B,v,x)
+    if !(diffvars(V)≠0 && mixedmode(V)<0)
+        return v
+    else
+        return :(derive_post($V,$(Val{A}()),$(Val{B}()),$v,$x))
+    end
+end
+
 function derive_pre(V,A,B,a,b,p)
     if !(diffvars(V)≠0 && mixedmode(V)<0)
         return Expr(:call,p,a,b)
     else
-        return :(derive_post($V,$(Val{A}()),$(Val{B}()),a,b,$p))
+        return :(derive_post($V,$(Val{A}()),$(Val{B}()),$a,$b,$p))
     end
 end
 
 function derive_post(V,::Val{A},::Val{B},v,x::Bool) where {A,B}
-    if !(diffvars(V)≠0 && mixedmode(V)<0)
-        return v
+    sa,sb = symmetricsplit(V,A),symmetricsplit(V,B)
+    ca,cb = count_ones(sa[2]),count_ones(sb[2])
+    return if (ca == cb == 0) || ((ca ≠ 0) && (cb ≠ 0))
+        v
     else
-        sa,sb = symmetricsplit(V,A),symmetricsplit(V,B)
-        ca,cb = count_ones(sa[2]),count_ones(sb[2])
-        return if (ca == cb == 0) || ((ca ≠ 0) && (cb ≠ 0))
-            v
-        else
-            prev = ca == 0 ? (x ? one(typeof(v)) : v) : (x ? v : one(typeof(v)))
-            for k ∈ DirectSum.indexsplit((ca==0 ? sa : sb)[1],ndims(V))
-                prev = derive(prev,getbasis(V,k))
-            end
-            prev
+        prev = ca == 0 ? (x ? one(typeof(v)) : v) : (x ? v : one(typeof(v)))
+        for k ∈ DirectSum.indexsplit((ca==0 ? sa : sb)[1],ndims(V))
+            prev = derive(prev,getbasis(V,k))
         end
+        prev
     end
 end
 
 function derive_post(V,::Val{A},::Val{B},a,b,*) where {A,B}
-    if !(diffvars(V)≠0 && mixedmode(V)<0)
-        return a*b
+    sa,sb = symmetricsplit(V,A),symmetricsplit(V,B)
+    ca,cb = count_ones(sa[2]),count_ones(sb[2])
[…]

### 2019-11-14 src/forms.jl

@@ -174,7 +174,7 @@ for Chain ∈ MSC
             for i ∈ 1:N
                 i≠m && @inbounds setblade!(out,a.v[di[Q][i]]*val,one(Bits)<<(i-1),Dimension{N}())
             end
-            return $Chain{T,V,1}(out)
+            return SChain{T,V,1}(out)
         end
     end
     for implex ∈ MSB
@@ -214,12 +214,11 @@ for Chain ∈ MSC
                 for i ∈ 1:N
                     i≠m && @inbounds setblade!(out,a.v[di[Q][i]]*val,one(Bits)<<(i-1),Dimension{N}())
                 end
-                return $Chain{t,V,1}(out)
+                return SChain{t,V,1}(out)
             end
         end
     end
     for Other ∈ MSC
-        Final = ((Chain == MSC[1]) && (Other == MSC[1])) ? MSB[1] : MSB[2]
         @eval begin
             function (a::$Chain{T,V,1})(b::$Other{S,V,1}) where {V,T,S}
                 $(insert_expr((:N,:M,:t,:df))...)
@@ -227,7 +226,7 @@ for Chain ∈ MSC
                 for Q ∈ 1:M
                     @inbounds out += a.v[df[Q][1]]*(df[Q][2] ? -(b.v[Q]) : b.v[Q])
                 end
-                return $Final{V}(out::t,Basis{V}())
+                return Simplex{V}(out::t,Basis{V}())
             end
             function (a::$Chain{T,V,2})(b::$Other{S,V,1}) where {V,T,S}
                 C = mixedmode(V)
@@ -240,7 +239,7 @@ for Chain ∈ MSC
                         @inbounds i≠m && addblade!(out,a.v[di[Q][i]]*val,one(Bits)<<(i-1),Dimension{N}())
                     end
                 end
-                return $Chain{t,V,1}(out)
+                return SChain{t,V,1}(out)
             end
         end
     end
@@ -260,7 +259,7 @@ for Chain ∈ MSC
                     @inbounds b[j,i]≠0 && setblade!(out,b[j,i],x⊻(one(Bits)<<(M+j-1)),Dimension{N}())
                 end
             end
-            return $Chain{T,V,2}(out)
+            return SChain{T,V,2}(out)
         end
     end
 end

### 2019-11-14 src/multivectors.jl

@@ -511,6 +511,7 @@ valuetype(t::MultiGrade) = promote_type(valuetype.(terms(t))...)
 @pure order(m::Union{MSimplex,Simplex}) = order(basis(m))+order(value(m))
 @pure order(m) = 0
 @pure bits(m::T) where T<:TensorTerm = bits(basis(m))
+@pure bits(::Type{Basis{V,G,B}}) where {V,G,B} = B
 
 @pure isinf(e::Basis{V}) where V = hasinf(e) && count_ones(bits(e)) == 1
 @pure hasinf(e::Basis{V}) where V = hasinf(V) && isodd(bits(e))
@@ -557,7 +558,7 @@ function rank(t::T,d=gdims(t)) where T<:TensorAlgebra{V} where V
     for k ∈ 2:ndims(V)
         @inbounds out[k] = min(out[k],d[k+1])
     end
-    return out
+    return SVector(out)
 end
 
 function null(t::T) where T<:TensorAlgebra{V} where V
@@ -567,7 +568,7 @@ function null(t::T) where T<:TensorAlgebra{V} where V
     for k ∈ 1:ndims(V)
         @inbounds out[k] = d[k+1] - r[k]
     end
-    return out
+    return SVector(out)
 end
 
 function betti(t::T) where T<:TensorAlgebra{V} where V
@@ -577,7 +578,7 @@ function betti(t::T) where T<:TensorAlgebra{V} where V
     for k ∈ 1:ndims(V)
         @inbounds out[k] = d[k+1] - r[k] - r[k+1]
     end
-    return out
+    return SVector(out)
 end
 
 for A ∈ (:TensorTerm,MSC...), B ∈ (:TensorTerm,MSC...)
@@ -663,7 +664,7 @@ for M ∈ (:Signature,:DiagonalForm,:SubManifold)
     @eval begin
         @inline (V::$M)(s::UniformScaling{T}) where T = Simplex{V}(T<:Bool ? (s.λ ? one(Int) : -(one(Int))) : s.λ,getbasis(V,(one(T)<<(ndims(V)-diffvars(V)))-1))
         (W::$M)(b::Simplex) = Simplex{W}(value(b),W(basis(b)))
-        (W::$M)(b::MSimplex) = MSimplex{W}(value(b),W(basis(b)))
+        (W::$M)(b::MSimplex) = Simplex{W}(value(b),W(basis(b)))
     end
 end
 
@@ -729,10 +730,10 @@ for Chain ∈ MSC
                     end
[…]

### 2019-11-14 src/parity.jl

@@ -308,7 +308,7 @@ for (op,other) ∈ ((:angular,:radial),(:radial,:angular))
             for k ∈ $other(V,G)
                 @inbounds out[k]≠0 && (out[k] = zero(T))
             end
-            MChain{T,V,G}(out)
+            SChain{T,V,G}(out)
         end
     end
     @eval function $op(t::MultiVector{T,V}) where {T,V}

### 2019-11-14 test/issuestests.jl

@@ -74,7 +74,7 @@ end
 @testset "Issue #22: Error in MultiVector constructor for Chains" begin
     basis"++"
 
-    a = v1 + v2
+    a = MChain(v1 + v2)
     @test typeof(a) <: MChain
 
     @test MultiVector(a) == v1 + v2

### 2019-11-16 src/algebra.jl
improved generated code for complement operations

@@ -582,7 +582,7 @@ export ×
 
 Cross product: ω×η = ⋆(ω∧η)
 """
-cross(a::TensorAlgebra{V},b::TensorAlgebra{V}) where V = ⋆(a∧b)
+cross(t::T...) where T<:TensorAlgebra = ⋆(∧(t...))
 
 @pure function cross(a::Basis{V},b::Basis{V}) where V
     p,C,t,Z = crossprod(a,b)
@@ -717,20 +717,36 @@ function generate_products(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj
             end
             return false
         end
-        function adjoint(m::MultiVector{T,V}) where {T<:$Field,V}
-            if mixedmode(V)<0
-                $(insert_expr((:N,:M,:bs,:bn),VEC)...)
-                out = zeros($VEC(N,$TF))
-                for g ∈ 1:N+1
-                    ib = indexbasis(N,g-1)
-                    @inbounds for i ∈ 1:bn[g]
-                        @inbounds setmulti!(out,$CONJ(m.v[bs[g]+i]),dual(V,ib[i],M))
+        @generated function adjoint(m::MultiVector{T,V}) where {T<:$Field,V}
+            if ndims(V)<cache_limit
+                if mixedmode(V)<0
+                    $(insert_expr((:N,:M,:bs,:bn),:vec)...)
+                    out = zeros(svec(N,Any))
+                    for g ∈ 1:N+1
+                        ib = indexbasis(N,g-1)
+                        @inbounds for i ∈ 1:bn[g]
+                            @inbounds setmulti!_pre(out,:($$CONJ(m.v[$(bs[g]+i)])),dual(V,ib[i],M))
+                        end
                     end
+                else
+                    out = :(MultiVector{$(dual(V))}(SVector($$CONJ.(value(m)))))
                 end
-            else
-                out = $CONJ.(value(m))
-            end
-            MultiVector{$TF,dual(V)}(out)
+                return :(MultiVector{$(dual(V))}($(Expr(:call,:SVector,out...))))
+            else return quote
+                if mixedmode(V)<0
+                    $(insert_expr((:N,:M,:bs,:bn),$(QuoteNode(VEC)))...)
+                    out = zeros($$VEC(N,$$TF))
+                    for g ∈ 1:N+1
+                        ib = indexbasis(N,g-1)
+                        @inbounds for i ∈ 1:bn[g]
[…]

### 2019-11-16 src/parity.jl

@@ -24,6 +24,7 @@ for side ∈ (:left,:right)
     p = Symbol(:parity,side)
     pg = Symbol(p,:hodge)
     pn = Symbol(p,:null)
+    pnp = Symbol(pn,:pre)
     @eval begin
         @pure $p(V::Bits,B::Bits,N::Int) = $p(0,sum(indices(B,N)),count_ones(B),N)
         @pure $pg(V::Bits,B::Bits,N::Int) = $pg(count_ones(V&B),sum(indices(B,N)),count_ones(B),N)
@@ -32,6 +33,15 @@ for side ∈ (:left,:right)
             hi,ho = hasinf(V),hasorigin(V)
             if hi && ho && count_ones(B&UInt(3)) ==1
                 isodd(B) ? (2v) : (v/2)
+            else
+                v
+            end
+        end
+        @inline $pnp(V,B,v) = v
+        @inline function $pnp(V::Signature,B,v)
+            hi,ho = hasinf(V),hasorigin(V)
+            if hi && ho && count_ones(B&UInt(3)) ==1
+                isodd(B) ? Expr(:call,:*,2,v) : Expr(:call,:/,v,2)
             else
                 v
             end

### 2019-11-16 src/algebra.jl
significantly improved exp with generated MultiVector code

@@ -672,6 +672,45 @@ export ⟂, ∥
 
 ### Product Algebra Constructor
 
+@eval function generate_loop_multivector(V,term,b,MUL,product!,preproduct!,d=nothing)
+    if ndims(V)<cache_limit/2
+        $(insert_expr((:N,:t,:out,:bs,:bn),:svec)...)
+        for g ∈ 1:N+1
+            Y = indexbasis(N,g-1)
+            @inbounds for i ∈ 1:bn[g]
+                @inbounds val = isnothing(d) ? :($b[$(bs[g]+i)]) : :($b[$(bs[g]+i)]/$d)
+                for G ∈ 1:N+1
+                    @inbounds R = bs[G]
+                    X = indexbasis(N,G-1)
+                    @inbounds for j ∈ 1:bn[G]
+                        @inbounds preproduct!(V,out,X[j],Y[i],derive_pre(V,X[j],Y[i],:($term[$(R+j)]),val,MUL))
+                    end
+                end
+            end
+        end
+        (:N,:t,:out), :(out .= $(Expr(:call,:SVector,out...)))
+    else
+        (:N,:t,:out,:bs,:bn,:μ), quote
+            for g ∈ 1:N+1
+                Y = indexbasis(N,g-1)
+                @inbounds for i ∈ 1:bn[g]
+                    @inbounds val = $(isnothing(d) ? :($b[bs[g]+i]) : :($b[bs[g]+i]/$d))
+                    val≠0 && for G ∈ 1:N+1
+                        @inbounds R = bs[G]
+                        X = indexbasis(N,G-1)
+                        @inbounds for j ∈ 1:bn[G]
+                            if @inbounds $product!(V,out,X[j],Y[i],derive_mul(V,X[j],Y[i],$term[R+j],val,$MUL))&μ
+                                $(insert_expr((:out,);mv=:out)...)
+                                @inbounds $product!(V,out,X[j],Y[i],derive_mul(V,X[j],Y[i],$term[R+j],val,$MUL))
+                            end
+                        end
+                    end
+                end
+            end
+        end
+    end
+end
+
 function generate_products(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj,PAR=false)
     if Field == Grassmann.Field
         generate_mutators(:(MArray{Tuple{M},T,1,M}),Number,Expr,:-,:*)
[…]

### 2019-11-16 src/composite.jl

@@ -24,41 +24,32 @@ function Base.expm1(t::T) where T<:TensorAlgebra{V} where V
     return S
 end
 
-@eval function Base.expm1(b::MultiVector{T,V}) where {T,V}
-    B = value(b)
-    sb,nb = scalar(b),norm(B)
-    sb ≈ nb && (return Simplex{V}(expm1(sb)))
-    $(insert_expr((:N,:t,:out,:bs,:bn),:mvec,:T,Float64)...)
-    S = zeros(mvec(N,t))
-    term = zeros(mvec(N,t))
-    S .= B
-    out .= value(b^2)/2
-    norms = MVector(nb,norm(out),norm(term))
-    k::Int = 3
-    @inbounds while (norms[2]<norms[1] || norms[2]>1) && k ≤ 10000
-        S += out
-        ns = norm(S)
-        @inbounds ns ≈ norms[3] && break
-        term .= out
-        out .= 0
-        # term *= b/k
-        for g ∈ 1:N+1
-            Y = indexbasis(N,g-1)
-            @inbounds for i ∈ 1:bn[g]
-                @inbounds val = B[bs[g]+i]/k
-                val≠0 && for G ∈ 1:N+1
-                    @inbounds R = bs[G]
-                    X = indexbasis(N,G-1)
-                    @inbounds for j ∈ 1:bn[G]
-                        @inbounds geomaddmulti!(V,out,X[j],Y[i],*(term[R+j],val))
-                    end
-                end
-            end
+@eval @generated function Base.expm1(b::MultiVector{T,V}) where {T,V}
+    loop = generate_loop_multivector(V,:term,:B,:*,:geomaddmulti!,geomaddmulti!_pre,:k)
+    return quote
+        B = value(b)
+        sb,nb = scalar(b),norm(B)
+        sb ≈ nb && (return Simplex{V}(expm1(sb)))
+        $(insert_expr(loop[1],:mvec,:T,Float64)...)
+        S = zeros(mvec(N,t))
+        term = zeros(mvec(N,t))
+        S .= B
+        out .= value(b^2)/2
+        norms = MVector(nb,norm(out),norm(term))
+        k::Int = 3
+        @inbounds while (norms[2]<norms[1] || norms[2]>1) && k ≤ 10000
+            S += out
+            ns = norm(S)
+            @inbounds ns ≈ norms[3] && break
+            term .= out
+            out .= 0
+            # term *= b/k 
[…]

### 2020-05-12 src/Grassmann.jl
Make up/downarrow operators type-stable

@@ -123,7 +123,7 @@ function ↑(ω::T) where T<:TensorAlgebra
     !(hasinf(V)||hasorigin(V)) && (return ω)
     G = Λ(V)
     return if hasinf(V) && hasorigin(V)
-        ((G.v∞/2)*ω^2+G.v∅)+ω
+        ((G.v∞*(one(valuetype(ω))/2))*ω^2+G.v∅)+ω
     else
         ω2 = ω^2
         iω2 = inv(ω2+1)
@@ -146,7 +146,7 @@ function ↓(ω::T) where T<:TensorAlgebra
     !(hasinf(V)||hasorigin(V)) && (return ω)
     G = Λ(V)
     return if hasinf(V) && hasorigin(V)
-        inv(G.v∞∅)*(G.v∞∅∧ω)/(-ω⋅G.v∞)
+        inv(one(valuetype(ω))*G.v∞∅)*(G.v∞∅∧ω)/(-ω⋅G.v∞)
     else
         b = hasinf(V) ? G.v∞ : G.v∅
         ((ω∧b)*b)/(1-b⋅ω)

### 2020-05-13 paper/paper.tex
created hybrid generated function for MultiVector arithmetic
revised JuliaCon paper terminology

@@
 \begin{figure}[ht]
-\centerline{\includegraphics[width=4cm]{img/grassmann.png}}
-%\centerline{\includegraphics[width=4cm]{../docs/src/assets/logo.png}}
+%\centerline{\includegraphics[width=4cm]{img/grassmann.png}}
+\centerline{\includegraphics[width=4cm]{../docs/src/assets/logo.png}}
 \caption*{github.com/chakravala/Grassmann.jl}
@@
 \begin{definition}[Vector bundle of submanifolds]
-	Let $M = T^\mu V\in\text{Vect}_{\mb K}$ be a \verb`VectorBundle<:Manifold` of rank $n$,
+	Let $M = T^\mu V\in\text{Vect}_{\mb K}$ be a \verb`TensorBundle<:Manifold` of rank $n$,
 	\begin{align*}
@@
 	\end{align*}
-	The type \verb+VectorBundle{n,+$\mb P$\verb+,g,+$\nu,\mu$\verb+}+ uses \textit{byte-encoded} data available at pre-compilation, where
+	The type \verb+TensorBundle{n,+$\mb P$\verb+,g,+$\nu,\mu$\verb+}+ uses \textit{byte-encoded} data available at pre-compilation, where
 	$\mb P$ specifies the basis for up and down projection,
@@
 
-The metric signature of the \verb+Basis{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the \verb+Basis{V,1}+ element of the corresponding index squares to \verb`+1` or \verb`-1`.
-For example, \verb`S"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
+The metric signature of the \verb+SubManifold{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the element of the corresponding index squares to \verb`+1` or \verb`-1`.
+For example, \verb`S"+++"` constructs a positive definite 3-dimensional \verb`TensorBundle`.
 It is also possible to specify an arbitrary \verb`DiagonalForm` having numerical values for the basis with degenracy \verb`D"1,1,1,0"`, although the $\pm$ format has a more compact representation.
@@
 The \verb`AbstractTensors` package is intended for universal interoperability of the abstract \verb`TensorAlgebra` type system.
-All \verb`TensorAlgebra{V}` subtypes have type parameter \verb`V`, used to store a \verb`VectorBundle` value obtained from \textit{DirectSum.jl}.
-By itself, this package does not impose any specifications or structure on the \verb`TensorAlgebra{V}` subtypes and elements, aside from requiring $V$ to be a \verb`VectorBundle`.
-Hence all tensor types share a common underlying \verb`VectorBundle` structure.
+All \verb`TensorAlgebra{V}` subtypes have type parameter \verb`V`, used to store a \verb`TensorBundle` value obtained from \textit{DirectSum.jl}.
+By itself, this package does not impose any specifications or structure on the \verb`TensorAlgebra{V}` subtypes and elements, aside from requiring $V$ to be a \verb`Manifold`.
+Hence all tensor types share a common underlying \verb`Manifold` structure.
 The macro \verb`@basis V` declares a local basis in Julia.
@@
 \begin{definition}
-	Let $V\in\text{Vect}_{\mb k}$ be a \verb`VectorBundle` with dual space $V'$ and the basis elements $w_k:V\ra\mb K$, then for all $x\in V,c\in\mb K$ the properties $(w_i+w_j)(x) = w_i(x)+w_j(x)$ and $(cw_k)(x) = cw_k(x)$ hold.
+	Let $V\in\text{Vect}_{\mb k}$ be a \verb`TensorBundle` with dual space $V'$ and the basis elements $w_k:V\ra\mb K$, then for all $x\in V,c\in\mb K$ the properties $(w_i+w_j)(x) = w_i(x)+w_j(x)$ and $(cw_k)(x) = cw_k(x)$ hold.
 	An element of a mixed-symmetry \verb`TensorAlgebra{V}` is a multilinear mapping that is formally constructed by taking the tensor products of linear and multilinear maps,
@@
 \begin{definition}[Mixed-symmetry basis]
-	Combining the linear basis generating elements with each other using the multilinear tensor product yields a graded (decomposable) tensor \verb`Basis` $\langle w_{p_1}\otimes\dots\otimes w_{p_k}\rangle_k$, where \verb`grade` $k$ is determined by the number of $w_i$ basis elements in its tensor product decomposition.
+	Combining the linear basis generating elements with each other using the multilinear tensor product yields a graded (decomposable) \verb`SubManifold` $\langle w_{p_1}\otimes\dots\otimes w_{p_k}\rangle_k$, where \verb`rank` $k$ is determined by the number of $w_i$ basis elements in its tensor product decomposition.
 	The algebra partitions into symmetric and anti-symmetric tensor equivalence classes.
@@
 
-The Grassmann \verb`Basis` elements $v_k\in\Lambda_1V$ and $w^k\in\Lambda^1V$ are linearly independent vector and covector elements of $V$, while the Leibniz \verb`Operator` elements $\partial_k\in L_1V$ are partial tangent derivations and $\epsilon_k(x)\in L^1V$ are dependent functions of the \verb`tangent` manifold.
+The Grassmann basis elements $v_k\in\Lambda_1V$ and $w^k\in\Lambda^1V$ are linearly independent vector and covector elements of $V$, while the Leibniz \verb`Operator` elements $\partial_k\in L_1V$ are partial tangent derivations and $\epsilon_k(x)\in L^1V$ are dependent functions of the \verb`tangent` manifold.
 Higher \verb`grade` elements of $\Lambda V$ correspond to \verb`SubManifold` spaces, while higher \verb`order` function elements of $LV$ become homogenous polynomials and Taylor series.
@@
 \begin{remark}
-	The product symbol $\ominus$ will be used to denote explicitly usage of the geometric algebraic product, altough the standard number product \verb`*` notation could also be used.
+	The product symbol $\ominus$ will be used to denote explicitly usage of the geometric algebraic product, although the standard number product \verb`*` notation could also be used.
 	The $\ominus$ choice helps emphasize that the geometric algebraic product is characterized by symmetric differencing of anti-symmetric indices.
@@
 	Observe that $\ast$ and $\ast'$ could both be exchanged in \verb`abs`, \verb`abs2`, and \verb`norm`; however, these are different products.
-	The \textit{scalar product} $\circledast$ is the scalar part, so $\eta\circledast\omega = \gen{\eta\ast\omega}$.
+	The \textit{scalar product} $\circledast$ is the \verb`scalar` part, so $\eta\circledast\omega = \gen{\eta\ast\omega}$.
 	In general $\sqrt\omega = e^{(\log\omega)/2}$ is valid for invertible $\omega$.
@@
 A universal unit volume element can be specified in terms of \verb`LinearAlgebra.UniformScaling`, which is independent of $V$ and has its interpretation only instantiated by the context of the \verb`TensorAlgebra{V}` element being operated on.
-Universal interoperability of \verb`LinearAlgebra.UniformScaling` as the pseudoscalar element which takes on the \verb`VectorBundle` form of any other \verb`TensorAlgebra` element is handled globally.
+Universal interoperability of \verb`LinearAlgebra.UniformScaling` as the pseudoscalar element which takes on the \verb`TensorBundle` form of any other \verb`TensorAlgebra` element is handled globally.
 This enables the usage of \verb`I` from \verb`LinearAlgebra` as a universal pseudoscalar element defined at every point $x$ of a \verb`Manifold`, which is mathematically denoted by $I=I(x)$ and specified by the $g(x)$ bilinear tensor field of $TM$.
@@
 \begin{remark}
-	While $\star\omega$ is \verb`complementright` of $\omega$, the \verb`complementleft` would be $I\ast'\omega$.
-The $\star$ symbol was added to the Julia language as unary operator for ease of use with \verb`Grassmann` on Julia's v1.2 release.
+	While $\star\omega$ is \verb`complementright` of $\omega$, the \verb`complementleft` would be $I\ast'\omega$ and $!\omega$ denotes the non-metric variant the complement.
+The $\star$ symbol was added to the Julia language as unary operator on Julia's v1.2 release.
 \end{remark}
@@
 	\end{align*}
-	Elements $\omega$ are \textit{harmonic} if $\nabla\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, such that $\mc H^p M = \setc{\nabla\omega = 0}{\omega\in \Omega^pM}$.
+	Elements $\omega$ are \textit{harmonic} if $\nabla\omega = 0$ and both \textit{closed} $d\omega=0$ and \textit{coclosed} $\delta\omega=0$, such that $\mc H^p M = \setc{\nabla\omega = 0}{\omega\in \Omega^pM}$.
 	Hodge \cite{ivancevic}:

### 2020-05-27 paper/paper.tex
fixed #51 fixed #68 fixed #69

@@
 $v_\infty^2 =0$, $v_\emptyset^2 =0$,
-$v_\infty \cdot v_\emptyset = 1$,  and $v_{\infty\emptyset}^2 = 1$ with
+$v_\infty \cdot v_\emptyset = -1$,  and $v_{\infty\emptyset}^2 = 1$ with
 Minkowski plane $v_{\infty\emptyset}$ having the Hestenes-Dirac-Clifford product properties

### 2020-05-27 src/algebra.jl

@@ -352,6 +352,8 @@ Exterior product as defined by the anti-symmetric quotient Λ≡⊗/~
 
 export ∧, ∨, ⊗
 
+@inline ∧(t) = t
+
 @pure function ∧(a::SubManifold{V},b::SubManifold{V}) where V
     ba,bb = bits(a),bits(b)
     A,B,Q,Z = symmetricmask(V,ba,bb)
@@ -378,7 +380,7 @@ end
 #∧(a::SubManifold{V},b::MultiGrade{V}) where V = MultiGrade{V}(b.v,a*basis(b))
 #∧(a::MultiGrade{V},b::MultiGrade{V}) where V = MultiGrade{V}(a.v*b.v,basis(a)*basis(b))
 
-⊗(a::TensorAlgebra{V},b::TensorAlgebra{V}) where V = a∧b
+⊗(a::A,b::B) where {A<:TensorAlgebra,B<:TensorAlgebra} = a∧b
 
 ## regressive product: (L = grade(a) + grade(b); (-1)^(L*(L-ndims(V)))*⋆(⋆(a)∧⋆(b)))
 
@@ -804,6 +806,8 @@ for (op,eop) ∈ ((:+,:(+=)),(:-,:(-=)))
     end
 end
 
+const FieldsBig = (Fields...,BigFloat,BigInt,Complex{BigFloat},Complex{BigInt},Rational{BigInt})
+
 function generate_sums(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj,PAR=false)
     if Field == Grassmann.Field
         generate_mutators(:(MArray{Tuple{M},T,1,M}),Number,Expr,SUB,MUL)
@@ -811,7 +815,7 @@ function generate_sums(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj,PAR
         generate_mutators(:(SizedArray{Tuple{M},T,1,1}),Field,set_val,SUB,MUL)
     end
     PAR && (DirectSum.extend_field(eval(Field)); global parsym = (parsym...,eval(Field)))
-    TF = Field ∉ Fields ? :Any : :T
+    TF = Field ∉ FieldsBig ? :Any : :T
     EF = Field ≠ Any ? Field : ExprField
     Field ∉ Fields && @eval begin
         Base.:*(a::F,b::SubManifold{V}) where {F<:$EF,V} = Simplex{V}(a,b)

### 2020-05-27 src/products.jl

@@ -46,7 +46,7 @@ end
 insert_t(x) = Expr(:block,:(t=promote_type(valuetype(a),valuetype(b))),x)
 
 function generate_products(Field=Field,VEC=:mvec,MUL=:*,ADD=:+,SUB=:-,CONJ=:conj,PAR=false)
-    TF = Field ∉ Fields ? :Any : :T
+    TF = Field ∉ FieldsBig ? :Any : :T
     EF = Field ≠ Any ? Field : ExprField
     generate_sums(Field,VEC,MUL,ADD,SUB,CONJ,PAR)
     @eval begin
